### 2017-01-24 Paper/MSRChallenge2017.tex
Adding the templates for the paper

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt, conference]{IEEEtran}
% Add the compsocconf option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

\usepackage{booktabs}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\usepackage[usenames,dvipsnames]{color}
\newcommand{\todo}[1]
  {{\scriptsize \textbf{\color{red} {#1}}}}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired

\title{Predicting commit success from developer's profile}
%Or some better name, Zack can probably think of a better one, he is good with names

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{Authors hidden for the purposes of double blind review}
\IEEEauthorblockA{\\
\\
\\}

%\author{\IEEEauthorblockN{Authors Name/s per 1st Affiliation (Author)}
%\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
%line 2: name of organization, acronyms acceptable\\
%line 3: City, Country\\
%line 4: Email: name@xyz.com}
%\and
%\IEEEauthorblockN{Authors Name/s per 2nd Affiliation (Author)}
%\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
%line 2: name of organization, acronyms acceptable\\
%line 3: City, Country\\
%line 4: Email: name@xyz.com}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
The abstract goes here. DO NOT USE SPECIAL CHARACTERS, SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.

\end{abstract}

\begin{IEEEkeywords}
component; formatting; style; styling;

\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
\todo{Introduction goes here}
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Type style and Fonts}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here. this is more of the conclusion

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...
more thanks here

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2017-02-13 Paper/MSRChallenge2017.tex
First page of the paper

@@
 
-\title{Predicting commit success from developer's profile}
+\title{Predicting job success from developer's profile}
 %Or some better name, Zack can probably think of a better one, he is good with names
@@
 \begin{abstract}
-The abstract goes here. DO NOT USE SPECIAL CHARACTERS, SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.
-
+Abstract goes here
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component; formatting; style; styling;
+social networks; predicting success;
 
@@
 \section{Introduction}
-% no \IEEEPARstart
-\todo{Introduction goes here}
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
+Social networks have gained a lot attention in the last several years, and because of this we now have a wide variety of measurable social attributes that we did not have in the past.
 
-\subsection{Subsection Heading Here}
-Subsection text here.
+\section{Research Design}
+We present the research design of this study
+following the Goal-Question-Metric (GQM) approach descibed by Basili et al. \cite{Basili84}
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+\subsection{Goal}
+The goal of this study is to have a deeper understanding of the relationship between the several different properties that are gathered in a developer's online profile, and the likelihood of a commit performed by that developer to be considered a successful commit depending on these attributes.
 
-\section{Type style and Fonts}
+\subsection{Question}
+
+\begin{enumerate}
+\item Given a model built from the technical data related a corpus of commits, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power?
+\item Which attributes (in developer's data, commit data, and both together) are the most decisive in order to know if a commit will be successful or not?
+\item Does (country of origin/gender/stars/num of followers/num following/activity rate) have a significant impact in the likelihood of commit success?
+
+\end{enumerate}
+
+\subsection{Metric}
+
+\section{Building and Augmenting dataset with user profile data}
+For this section our goal is to build a dataset based on the attributes that are intrinsic for the commit complexity and therefore for its probability of leading to a successful Travis CI job.
+To do this we extracted the attributes from the original dataset provided~\cite{msr17challenge} which work as a proxy for the complexity of the commit being pushed.
+\begin{itemize}
+\item tr\_original\_commit
+\item gh\_build\_started\_at 
+\item git\_diff\_src\_churn 
+\item gh\_diff\_files\_added 
+\item gh\_diff\_files\_deleted 
+\item gh\_diff\_files\_modified 
+\item gh\_diff\_tests\_added 
+\item gh\_diff\_tests\_deleted 
+\item gh\_diff\_src\_files 
+\item gh\_sloc 
+\item tr\_status 
+\end{itemize}
+
+Once we had these attributes, we removed repeated rows and we gathered the social attributes for each of these rows.
+
+To do this, we extracted from the original file provided~\cite{msr17challenge} the commit hash and the project name.
+We removed the repeated rows and created a script to gather the social data of the developer who pushed that commit.
+First we concatenated the two attributes before mentioned in the following way:
+\newline \newline
+\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
+\newline \newline
+We created a script that takes this string and navigates through the html representation of the website described above, and looks for the \textit{username} of the developer in the Github platform.
+If it is able to find one, we then create another string following the pattern:
+\newline \newline
+\textit{https://github.com/\textbf{UserName}}
+\newline \newline
+We then navigate through the html representation of the developer's profile website (described above) and look for the following attributes:
+\begin{itemize}
+\item repositories
+\item stars
+\item followers
+\item following
+\item collabProjects
+\end{itemize}
+
+To this dataset, we also added from the dataset provided~\cite{msr17challenge} the attribute gh\_by\_core\_team\_member which we considered to have also social weight.
+
+After performing this last data mining task, we created two different datasets.
+One of them contains technical data that is seen as a proxy for the complexity of the changes being performed in the commit.
+We also created a second dataset which consists of the data mentioned in the first dataset, plus the set of social attributes related to the developer who pushed the commit.
+
+The dataset provided by the MSR Challenge~\cite{msr17challenge} is very diverse and consists of commits that date from very far back, and the social data we are gathering is recent data, gathered in January 2017.
+The researchers of this project acknowledge this discrepancy and in an effort to mitigate this threat to validity, we filter the commits analyzed by looking only at the commits pushed in the last 3 years of the dataset (2014,2015,2016), with the intuition that the social data gathered by this study will have a closer relationship to the social data if it were to be gathered in these years, than if we would compare it to years further back.
+
+\section{Multiple linear regression}
+How we used the ML
+
+\section{Evaluation}
+Maybe a 10 fold cross validation?
+
+\section{Results}
+Results
+
+\section{Discussion}
+Discussion
 
@@
 
-The authors would like to thank...
-more thanks here
+The acknowledgments will be added for the camera ready version.
 
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
+%\begin{thebibliography}{1}
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%\end{thebibliography}
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
+%\bibliographystyle{abbrv}
+\bibliography{MSRChallenge2017}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
 

### 2017-02-15 Paper/MSRChallenge2017.tex
added intro and some related work

@@
 %
-%\usepackage{cite}
+\usepackage{cite}
 % cite.sty was written by Donald Arseneau
@@
 \begin{IEEEkeywords}
-social networks; predicting success;
+social attributes; Travis CI; Github; social networks; predicting integration success; social coding
 
@@
 \section{Introduction}
-Social networks have gained a lot attention in the last several years, and because of this we now have a wide variety of measurable social attributes that we did not have in the past.
+Social interactions and attributes play a key role in software quality output from development teams~\cite{nagappan08,bettenburgh10}, these aspects have become more and more important and platforms that support software development processes provide every time a broader spectrum of measurements for social characteristics.
+Because of this we now have a wide variety of measurable social attributes that can be studied and analyzed to understand their correlation and impact with different success measures.
+This study aims to acknowledge the predictive power of some of these attributes when it comes to the quality of the commits developers write and its success when integrating into the project build through Travis CI.
+
+\textbf{Related work:}
+Similar studies have shown the relationship between different attributes and different measures of success: pull request acceptance~\cite{gousios14, gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
+Tsay et al~\cite{tsay14icse} performed a very relevant study where they determine that the social connection between the developer who is asking the pull request and the integrators is a key factor torwards acceptance of a pull request.
+Unlike this previous study, in our study we look at a broader aspect of social aspects and how this attributes towards the success in Travis CI jobs.
+Gousios et al~\cite{gousios14} study the relationship between the area of the source code being modified by the developer requesting the changes to be pulled and the acceptance rate of these changes is highly correlated.
+Also existence of tests and overall code quality~\cite{gousios15} are attributes that have a strong relationship with the acceptance rate of a pull request.
+Bettenburgh et al~\cite{bettenburgh10} discuss the impact of social interactions with post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different project characteristics (programming language, project age, etc.) affect commit success when integrated to the automatic build process...............
+Unlike the before mentioned, our study focuses on independent social attributes, and not interactions between developers, or technical properties of the project.
 
 \section{Research Design}
-We present the research design of this study
-following the Goal-Question-Metric (GQM) approach descibed by Basili et al. \cite{Basili84}
+We present the approach taken to guide this study by
+following the Goal-Question-Metric (GQM) methodology descibed by Basili et al~\cite{Basili84}.
 
 \subsection{Goal}
-The goal of this study is to have a deeper understanding of the relationship between the several different properties that are gathered in a developer's online profile, and the likelihood of a commit performed by that developer to be considered a successful commit depending on these attributes.
+The goal of this study is to have a deeper understanding of the relationship between the several different social properties that are gathered in a developer's online profile, and the likelihood of a commit performed by that developer to be considered a successfully integrated into its corresponding project according to Travis CI depending on the social attributes of the developer.
 
@@
 \begin{enumerate}
-\item Given a model built from the technical data related a corpus of commits, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power?
-\item Which attributes (in developer's data, commit data, and both together) are the most decisive in order to know if a commit will be successful or not?
-\item Does (country of origin/gender/stars/num of followers/num following/activity rate) have a significant impact in the likelihood of commit success?
+\item What is the relationship, if any, between attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the travis jobs this commit triggers?
+\item Given a dataset described before, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power of a linear regression model created from this data?
+\item Which attributes (in social data, technical data, and both together) are the most decisive in order to know if a commit will be successful or not?
+\item Does any of the social attributes have a significant impact in the likelihood of commit success?
 
@@
 \subsection{Metric}
+We created a linear regression model based on two different sets of data.
+Merely technical data related to technical aspects of the complexity of the commit, and a superset of this before-mentioned data and social data gathered from the developer who pushed the commit.
+We evaluate the predictive power of these two models with 10 fold cross validation and we analyze which of them is able to predict with higher accuracy the success of unseen commits.
 
@@
 
-%\bibliographystyle{abbrv}
+\bibliographystyle{plain}
 \bibliography{MSRChallenge2017}  % sigproc.bib is the name of the Bibliography in this case

### 2017-02-15 Paper/MSRChallenge2017.tex
added some approach

@@
 \begin{enumerate}
-\item What is the relationship, if any, between attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the travis jobs this commit triggers?
-\item Given a dataset described before, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power of a linear regression model created from this data?
+\item What is the relationship, if any, between attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the Travis jobs this commit triggers?
+\item Given the dataset described before, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power of a linear regression model created from this dataset?
 \item Which attributes (in social data, technical data, and both together) are the most decisive in order to know if a commit will be successful or not?
-\item Does any of the social attributes have a significant impact in the likelihood of commit success?
+\item Does any of the social attributes have a significant impact in the likelihood of commit integration success?
 
@@
 \newline \newline
-We created a script that takes this string and navigates through the html representation of the website described above, and looks for the \textit{username} of the developer in the Github platform.
+We created a script that constructs this string and navigates through the html representation of the website described above, and looks for the \textit{username} of the developer in the Github platform.
 If it is able to find one, we then create another string following the pattern:
@@
 \newline \newline
-We then navigate through the html representation of the developer's profile website (described above) and look for the following attributes:
+We then navigate through the html representation of the developer's profile website (described above) and gather the following attributes:
 \begin{itemize}
-\item repositories
-\item stars
-\item followers
-\item following
-\item collabProjects
+\item Repositories
+\item Stars
+\item Followers
+\item Following
+\item ContribProjects
 \end{itemize}
 
-To this dataset, we also added from the dataset provided~\cite{msr17challenge} the attribute gh\_by\_core\_team\_member which we considered to have also social weight.
+Repositories alludes to the repositories the developer has access to.
+This includes where the developer is the repository owner,where the developer is a collaborator, and repositories that the developer can access through an organization membership.\footnote{https://developer.github.com/v3/repos/} Stars show the projects the developer has stared, where starring translates to showing appreciation to the repository and creating a bookmark for later access.\footnote{https://help.github.com/articles/about-stars/} Followers and Following detail the number of developers that are following and being followed by the developer in question.
+Finally, the last attribute studies is the number of contributions made by the developer in the last year.
+To this dataset, we also added from the original dataset provided~\cite{msr17challenge} the attribute gh\_by\_core\_team\_member which we considered to have also social weight, which describes if the developer pushing the commit is a core member of the project the commit is being pushed to.
 
@@
 
-\section{Multiple linear regression}
-How we used the ML
-
 \section{Evaluation}
-Maybe a 10 fold cross validation?
+Logistic Regression and Decision trees.
 

### 2017-02-16 Paper/MSRChallenge2017.tex
Close to the first draft

@@
 
-\title{Predicting job success from developer's profile}
+\title{Analyzing the impact of social attributes on the success of commit integration}
 %Or some better name, Zack can probably think of a better one, he is good with names
@@
 Social interactions and attributes play a key role in software quality output from development teams~\cite{nagappan08,bettenburgh10}, these aspects have become more and more important and platforms that support software development processes provide every time a broader spectrum of measurements for social characteristics.
-Because of this we now have a wide variety of measurable social attributes that can be studied and analyzed to understand their correlation and impact with different success measures.
-This study aims to acknowledge the predictive power of some of these attributes when it comes to the quality of the commits developers write and its success when integrating into the project build through Travis CI.
+Because of this we now have a wide variety of measurable social attributes that can be studied and analyzed to understand their correlation and impact on different success measures.
+
+This study aims to acknowledge the impact of some of these attributes when it comes to the quality of the commits developers write and its success when integrating into the project build through Travis CI.
+The knowledge obtained by analyzing how much impact social characteristics have on the success of a commit integration will help developers further understand what social attributes are better proxies for experience and coding excellence; and it will also help code integrators and core team members to know how to prioritize pull requests coming from different developers, which of them may have a higher probability of integration success based not only on the technical difficulty of the integration, but also on social factors that determine the expertise of the developer in their integration practices.
 
@@
 Also existence of tests and overall code quality~\cite{gousios15} are attributes that have a strong relationship with the acceptance rate of a pull request.
-Bettenburgh et al~\cite{bettenburgh10} discuss the impact of social interactions with post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different project characteristics (programming language, project age, etc.) affect commit success when integrated to the automatic build process...............
-Unlike the before mentioned, our study focuses on independent social attributes, and not interactions between developers, or technical properties of the project.
+Bettenburgh et al~\cite{bettenburgh10} discuss the impact of social interactions with post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different project characteristics (programming language, project age, etc.) affect commit success when integrated to the automatic build process.
+Yu et al~\cite{yu16} analyze the impact of CI usage in Github and its correlation with software quality.
+Unlike the before mentioned, our study focuses on independent social attributes and how these relate to the success of the integration of a commit pushed by the developer being described by these social attributes.
+%, and not interactions between developers, or technical properties of the project.
 
@@
 
-\begin{enumerate}
-\item What is the relationship, if any, between attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the Travis jobs this commit triggers?
-\item Given the dataset described before, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power of a linear regression model created from this dataset?
-\item Which attributes (in social data, technical data, and both together) are the most decisive in order to know if a commit will be successful or not?
-\item Does any of the social attributes have a significant impact in the likelihood of commit integration success?
-
-\end{enumerate}
+Previous studies have identified a relationship between technical and social factors and pull request acceptance.
+In the interest of understanding if these relationship will hold with a different success measure such as commit integration success, and in order to establish a baseline to compare to, we deliver our first research question:
+\newline \newline
+\textbf{What is the relationship, if any, between technical attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the Travis jobs this commit triggers?}
+\newline \newline
+Assuming the previous studies hold to this different success measure, and there is a relationship between technical attributes and commit integration success, we are afterwards interested in knowing if adding social attributes to this predictability model will increase the probability of the model asserting correctly future instances by knowing not only technical data about the commit being pushed but also social attributes of the developer pushing the changes:
+\newline \newline
+\textbf{Given the dataset described before, are the social attributes gathered from the Github profiles of developers who pushed those commits, able to increase the predictive power of a model created from the technical dataset?}
+\newline \newline
+We are also interested in knowing what attributes, either from the technical background, the social background, and both combined, are the best proxies for knowing what will be the success of the commit integration:
+\newline \newline
+\textbf{Which attributes (in social data, technical data, and both together) are the most decisive in order to know if a commit will be successful or not?}
+\newline \newline
+Finally, we would like to know if/which social attributes have a significant impact in success of commit integration to a project: \todo{I'm not sure what's the difference between this RQ and the last one}
+\newline \newline
+\textbf{Does any of the social attributes have a significant impact in the likelihood of commit integration success?}
+\newline \newline
 
@@
 
-\section{Building and Augmenting dataset with user profile data}
+\section{Building and Augmenting dataset with social attributes} \label{approach}
 For this section our goal is to build a dataset based on the attributes that are intrinsic for the commit complexity and therefore for its probability of leading to a successful Travis CI job.
@@
 \begin{itemize}
-\item tr\_original\_commit
-\item gh\_build\_started\_at 
+%\item tr\_original\_commit
+%\item gh\_build\_started\_at 
 \item git\_diff\_src\_churn 
@@
 \item gh\_sloc 
-\item tr\_status 
+%\item tr\_status 
 \end{itemize}
@@
 \section{Evaluation}
-Logistic Regression and Decision trees.
+To evaluate the predictive power we can gain from analyzing the corpus provided~\cite{msr17challenge}, we have created a logistic regression model from both the datasets described in Section \ref{approach}.
+A logistic regression model is one where the dependent variable is categorial~\cite{freedman09}.
+Since in this study we are interested only in the cases where the commit was successfully integrated against any other possible state (errored, failed, canceled, started), we have divided our corpus into only two possible states, successful and notSuccessful, as to have a binary dependent variable.
+
+A binary logistic model is a mechanism used to calculate the probability of characterizing a binary dependent variable based on one or more independent variables~\cite{walker67,cox58}.
+In our study, the binary dependent variable would become the final status of the Travis CI jobs triggered by the commit pushed by the developer, and the independent variables are both the technical attributes (files added, files deleted, source churn, etc) and the social attributes (stars, followers, repositories, etc.) used to predict the the class value.
+
+We also evaluate our dataset by using decision trees, a predictive model which branches the different possible class values (represented as the leaves) depending on the attributes used to predict the class value (represented as the branches).
+In classification trees as the one being used in this study, each attribute represents a branch (with some exceptions due to pruning) and depending on the decisions taken while traversing the tree, the class value will be determined when one of the decisions leads to a leaf of the tree, therefore a class value will be encountered and a prediction can be made.
 
 \section{Results}
-Results
+Results \todo{maybe this section can be merged with the prior one}
 
@@
 
+\section{Threats to validity}
+
+\textbf{Internal}
+
+\textbf{External}
+
+\textbf{Structural}
+
 % use section* for acknowledgement

### 2017-02-16 Paper/MSRChallenge2017.tex
Wrapping lines so they are not absolutely humongous

@@
 \section{Introduction}
-Social interactions and attributes play a key role in software quality output from development teams~\cite{nagappan08,bettenburgh10}, these aspects have become more and more important and platforms that support software development processes provide every time a broader spectrum of measurements for social characteristics.
-Because of this we now have a wide variety of measurable social attributes that can be studied and analyzed to understand their correlation and impact on different success measures.
+Social interactions and attributes play a key role in software quality output 
+from development teams~\cite{nagappan08,bettenburgh10}, these aspects have 
+become more and more important and platforms that support software development 
+processes provide every time a broader spectrum of measurements for social 
+characteristics. Because of this we now have a wide variety of measurable social 
+attributes that can be studied and analyzed to understand their correlation and 
+impact on different success measures.
 
-This study aims to acknowledge the impact of some of these attributes when it comes to the quality of the commits developers write and its success when integrating into the project build through Travis CI.
-The knowledge obtained by analyzing how much impact social characteristics have on the success of a commit integration will help developers further understand what social attributes are better proxies for experience and coding excellence; and it will also help code integrators and core team members to know how to prioritize pull requests coming from different developers, which of them may have a higher probability of integration success based not only on the technical difficulty of the integration, but also on social factors that determine the expertise of the developer in their integration practices.
+This study aims to acknowledge the impact of some of these attributes when it 
+comes to the quality of the commits developers write and its success when 
+integrating into the project build through Travis CI. The knowledge obtained by 
+analyzing how much impact social characteristics have on the success of a commit 
+integration will help developers further understand what social attributes are 
+better proxies for experience and coding excellence; and it will also help code 
+integrators and core team members to know how to prioritize pull requests coming 
+from different developers, which of them may have a higher probability of 
+integration success based not only on the technical difficulty of the 
+integration, but also on social factors that determine the expertise of the 
+developer in their integration practices.
 
 \textbf{Related work:}
-Similar studies have shown the relationship between different attributes and different measures of success: pull request acceptance~\cite{gousios14, gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
-Tsay et al~\cite{tsay14icse} performed a very relevant study where they determine that the social connection between the developer who is asking the pull request and the integrators is a key factor torwards acceptance of a pull request.
-Unlike this previous study, in our study we look at a broader aspect of social aspects and how this attributes towards the success in Travis CI jobs.
-Gousios et al~\cite{gousios14} study the relationship between the area of the source code being modified by the developer requesting the changes to be pulled and the acceptance rate of these changes is highly correlated.
-Also existence of tests and overall code quality~\cite{gousios15} are attributes that have a strong relationship with the acceptance rate of a pull request.
-Bettenburgh et al~\cite{bettenburgh10} discuss the impact of social interactions with post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different project characteristics (programming language, project age, etc.) affect commit success when integrated to the automatic build process.
-Yu et al~\cite{yu16} analyze the impact of CI usage in Github and its correlation with software quality.
-Unlike the before mentioned, our study focuses on independent social attributes and how these relate to the success of the integration of a commit pushed by the developer being described by these social attributes.
-%, and not interactions between developers, or technical properties of the project.
+Similar studies have shown the relationship between different attributes and 
+different measures of success: pull request acceptance~\cite{gousios14, 
+gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
+Tsay et al~\cite{tsay14icse} performed a very relevant study where they 
+determine that the social connection between the developer who is asking the 
+pull request and the integrators is a key factor torwards acceptance of a pull 
+request. Unlike this previous study, in our study we look at a broader aspect of 
+social aspects and how this attributes towards the success in Travis CI jobs. 
+Gousios et al~\cite{gousios14} study the relationship between the area of the 
+source code being modified by the developer requesting the changes to be pulled 
+and the acceptance rate of these changes is highly correlated. Also existence of 
+tests and overall code quality~\cite{gousios15} are attributes that have a 
+strong relationship with the acceptance rate of a pull request. Bettenburgh et 
+al~\cite{bettenburgh10} discuss the impact of social interactions with 
+post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different 
+project characteristics (programming language, project age, etc.) affect commit 
+success when integrated to the automatic build process. Yu et al~\cite{yu16} 
+analyze the impact of CI usage in Github and its correlation with software 
+quality. Unlike the before mentioned, our study focuses on independent social 
+attributes and how these relate to the success of the integration of a commit 
+pushed by the developer being described by these social attributes. %, and not 
+interactions between developers, or technical properties of the project.
 
@@
 We present the approach taken to guide this study by
-following the Goal-Question-Metric (GQM) methodology descibed by Basili et al~\cite{Basili84}.
+following the Goal-Question-Metric (GQM) methodology descibed by Basili et 
+al~\cite{Basili84}.
 
 \subsection{Goal}
-The goal of this study is to have a deeper understanding of the relationship between the several different social properties that are gathered in a developer's online profile, and the likelihood of a commit performed by that developer to be considered a successfully integrated into its corresponding project according to Travis CI depending on the social attributes of the developer.
+The goal of this study is to have a deeper understanding of the relationship 
+between the several different social properties that are gathered in a 
+developer's online profile, and the likelihood of a commit performed by that 
+developer to be considered a successfully integrated into its corresponding 
+project according to Travis CI depending on the social attributes of the 
+developer.
 
@@
 
-Previous studies have identified a relationship between technical and social factors and pull request acceptance.
-In the interest of understanding if these relationship will hold with a different success measure such as commit integration success, and in order to establish a baseline to compare to, we deliver our first research question:
+Previous studies have identified a relationship between technical and social 
+factors and pull request acceptance. In the interest of understanding if these 
+relationship will hold with a different success measure such as commit 
+integration success, and in order to establish a baseline to compare to, we 
+deliver our first research question:
 \newline \newline
-\textbf{What is the relationship, if any, between technical attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the Travis jobs this commit triggers?}
+\textbf{What is the relationship, if any, between technical attributes that 
+describe the complexity of a commit (such as files added, tests added, lines of 
+code, etc) and the final status of the Travis jobs this commit triggers?}
 \newline \newline
-Assuming the previous studies hold to this different success measure, and there is a relationship between technical attributes and commit integration success, we are afterwards interested in knowing if adding social attributes to this predictability model will increase the probability of the model asserting correctly future instances by knowing not only technical data about the commit being pushed but also social attributes of the developer pushing the changes:
+Assuming the previous studies hold to this different success measure, and there 
+is a relationship between technical attributes and commit integration success, 
+we are afterwards interested in knowing if adding social attributes to this 
+predictability model will increase the probability of the model asserting 
+correctly future instances by knowing not only technical data about the commit 
+being pushed but also social attributes of the developer pushing the changes:
 \newline \newline
-\textbf{Given the dataset described before, are the social attributes gathered from the Github profiles of developers who pushed those commits, able to increase the predictive power of a model created from the technical dataset?}
+\textbf{Given the dataset described before, are the social attributes gathered 
+from the Github profiles of developers who pushed those commits, able to 
+increase the predictive power of a model created from the technical dataset?}
 \newline \newline
-We are also interested in knowing what attributes, either from the technical background, the social background, and both combined, are the best proxies for knowing what will be the success of the commit integration:
+We are also interested in knowing what attributes, either from the technical 
+background, the social background, and both combined, are the best proxies for 
+knowing what will be the success of the commit integration:
 \newline \newline
-\textbf{Which attributes (in social data, technical data, and both together) are the most decisive in order to know if a commit will be successful or not?}
+\textbf{Which attributes (in social data, technical data, and both together) are 
+the most decisive in order to know if a commit will be successful or not?}
 \newline \newline
-Finally, we would like to know if/which social attributes have a significant impact in success of commit integration to a project: \todo{I'm not sure what's the difference between this RQ and the last one}
+Finally, we would like to know if/which social attributes have a significant 
+impact in success of commit integration to a project: \todo{I'm not sure what's 
+the difference between this RQ and the last one}
 \newline \newline
-\textbf{Does any of the social attributes have a significant impact in the likelihood of commit integration success?}
+\textbf{Does any of the social attributes have a significant impact in the 
+likelihood of commit integration success?}
 \newline \newline
@@
 \subsection{Metric}
-We created a linear regression model based on two different sets of data.
-Merely technical data related to technical aspects of the complexity of the commit, and a superset of this before-mentioned data and social data gathered from the developer who pushed the commit.
-We evaluate the predictive power of these two models with 10 fold cross validation and we analyze which of them is able to predict with higher accuracy the success of unseen commits.
+We created a linear regression model based on two different sets of data. Merely 
+technical data related to technical aspects of the complexity of the commit, and 
+a superset of this before-mentioned data and social data gathered from the 
+developer who pushed the commit. We evaluate the predictive power of these two 
+models with 10 fold cross validation and we analyze which of them is able to 
+predict with higher accuracy the success of unseen commits.
 
-\section{Building and Augmenting dataset with social attributes} \label{approach}
-For this section our goal is to build a dataset based on the attributes that are intrinsic for the commit complexity and therefore for its probability of leading to a successful Travis CI job.
-To do this we extracted the attributes from the original dataset provided~\cite{msr17challenge} which work as a proxy for the complexity of the commit being pushed.
+\section{Building and Augmenting dataset with social attributes} 
+\label{approach}
+For this section our goal is to build a dataset based on the attributes that are 
+intrinsic for the commit complexity and therefore for its probability of leading 
+to a successful Travis CI job.
+To do this we extracted the attributes from the original dataset 
+provided~\cite{msr17challenge} which work as a proxy for the complexity of the 
+commit being pushed.
 \begin{itemize}
@@
 
-Once we had these attributes, we removed repeated rows and we gathered the social attributes for each of these rows.
+Once we had these attributes, we removed repeated rows and we gathered the 
+social attributes for each of these rows.
 
-To do this, we extracted from the original file provided~\cite{msr17challenge} the commit hash and the project name.
-We removed the repeated rows and created a script to gather the social data of the developer who pushed that commit.
+To do this, we extracted from the original file provided~\cite{msr17challenge} 
+the commit hash and the project name. We removed the repeated rows and created a 
+script to gather the social data of the developer who pushed that commit.
 First we concatenated the two attributes before mentioned in the following way:
@@
 \newline \newline
-We created a script that constructs this string and navigates through the html representation of the website described above, and looks for the \textit{username} of the developer in the Github platform.
-If it is able to find one, we then create another string following the pattern:
+We created a script that constructs this string and navigates through the html 
+representation of the website described above, and looks for the 
+\textit{username} of the developer in the Github platform. If it is able to find 
+one, we then create another string following the pattern:
 \newline \newline
@@
 \newline \newline
-We then navigate through the html representation of the developer's profile website (described above) and gather the following attributes:
+We then navigate through the html representation of the developer's profile 
+website (described above) and gather the following attributes:
 \begin{itemize}
@@
 
-Repositories alludes to the repositories the developer has access to.
-This includes where the developer is the repository owner,where the developer is a collaborator, and repositories that the developer can access through an organization membership.\footnote{https://developer.github.com/v3/repos/} Stars show the projects the developer has stared, where starring translates to showing appreciation to the repository and creating a bookmark for later access.\footnote{https://help.github.com/articles/about-stars/} Followers and Following detail the number of developers that are following and being followed by the developer in question.
-Finally, the last attribute studies is the number of contributions made by the developer in the last year.
-To this dataset, we also added from the original dataset provided~\cite{msr17challenge} the attribute gh\_by\_core\_team\_member which we considered to have also social weight, which describes if the developer pushing the commit is a core member of the project the commit is being pushed to.
+Repositories alludes to the repositories the developer has access to. This 
+includes where the developer is the repository owner,where the developer is a 
+collaborator, and repositories that the developer can access through an 
+organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
+show the projects the developer has stared, where starring translates to showing 
+appreciation to the repository and creating a bookmark for later 
+access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
+Following detail the number of developers that are following and being followed 
+by the developer in question. Finally, the last attribute studies is the number 
+of contributions made by the developer in the last year. To this dataset, we 
+also added from the original dataset provided~\cite{msr17challenge} the 
+attribute gh\_by\_core\_team\_member which we considered to have also social 
+weight, which describes if the developer pushing the commit is a core member of 
+the project the commit is being pushed to.
 
 After performing this last data mining task, we created two different datasets. 
-One of them contains technical data that is seen as a proxy for the complexity of the changes being performed in the commit.
-We also created a second dataset which consists of the data mentioned in the first dataset, plus the set of social attributes related to the developer who pushed the commit.
+One of them contains technical data that is seen as a proxy for the complexity 
+of the changes being performed in the commit. We also created a second dataset 
+which consists of the data mentioned in the first dataset, plus the set of 
+social attributes related to the developer who pushed the commit.
 
-The dataset provided by the MSR Challenge~\cite{msr17challenge} is very diverse and consists of commits that date from very far back, and the social data we are gathering is recent data, gathered in January 2017.
-The researchers of this project acknowledge this discrepancy and in an effort to mitigate this threat to validity, we filter the commits analyzed by looking only at the commits pushed in the last 3 years of the dataset (2014,2015,2016), with the intuition that the social data gathered by this study will have a closer relationship to the social data if it were to be gathered in these years, than if we would compare it to years further back.
+The dataset provided by the MSR Challenge~\cite{msr17challenge} is very diverse 
+and consists of commits that date from very far back, and the social data we are 
+gathering is recent data, gathered in January 2017. The researchers of this 
+project acknowledge this discrepancy and in an effort to mitigate this threat to 
+validity, we filter the commits analyzed by looking only at the commits pushed 
+in the last 3 years of the dataset (2014,2015,2016), with the intuition that the 
+social data gathered by this study will have a closer relationship to the social 
+data if it were to be gathered in these years, than if we would compare it to 
+years further back.
 
 \section{Evaluation}
-To evaluate the predictive power we can gain from analyzing the corpus provided~\cite{msr17challenge}, we have created a logistic regression model from both the datasets described in Section \ref{approach}.
-A logistic regression model is one where the dependent variable is categorial~\cite{freedman09}.
-Since in this study we are interested only in the cases where the commit was successfully integrated against any other possible state (errored, failed, canceled, started), we have divided our corpus into only two possible states, successful and notSuccessful, as to have a binary dependent variable.
+To evaluate the predictive power we can gain from analyzing the corpus 
+provided~\cite{msr17challenge}, we have created a logistic regression model from 
+both the datasets described in Section \ref{approach}. A logistic regression 
+model is one where the dependent variable is categorial~\cite{freedman09}. Since 
+in this study we are interested only in the cases where the commit was 
+successfully integrated against any other possible state (errored, failed, 
+canceled, started), we have divided our corpus into only two possible states, 
+successful and notSuccessful, as to have a binary dependent variable.
 
-A binary logistic model is a mechanism used to calculate the probability of characterizing a binary dependent variable based on one or more independent variables~\cite{walker67,cox58}.
-In our study, the binary dependent variable would become the final status of the Travis CI jobs triggered by the commit pushed by the developer, and the independent variables are both the technical attributes (files added, files deleted, source churn, etc) and the social attributes (stars, followers, repositories, etc.) used to predict the the class value.
+A binary logistic model is a mechanism used to calculate the probability of 
+characterizing a binary dependent variable based on one or more independent 
+variables~\cite{walker67,cox58}. In our study, the binary dependent variable 
+would become the final status of the Travis CI jobs triggered by the commit 
+pushed by the developer, and the independent variables are both the technical 
+attributes (files added, files deleted, source churn, etc) and the social 
+attributes (stars, followers, repositories, etc.) used to predict the the class 
+value.
 
-We also evaluate our dataset by using decision trees, a predictive model which branches the different possible class values (represented as the leaves) depending on the attributes used to predict the class value (represented as the branches).
-In classification trees as the one being used in this study, each attribute represents a branch (with some exceptions due to pruning) and depending on the decisions taken while traversing the tree, the class value will be determined when one of the decisions leads to a leaf of the tree, therefore a class value will be encountered and a prediction can be made.
+We also evaluate our dataset by using decision trees, a predictive model which 
+branches the different possible class values (represented as the leaves) 
+depending on the attributes used to predict the class value (represented as the 
+branches). In classification trees as the one being used in this study, each 
+attribute represents a branch (with some exceptions due to pruning) and 
+depending on the decisions taken while traversing the tree, the class value will 
+be determined when one of the decisions leads to a leaf of the tree, therefore a 
+class value will be encountered and a prediction can be made.
 

### 2017-02-17 Paper/MSRChallenge2017.tex

@@
 
+Similar studies in recent years have analyzed the relationship between social 
+and technical factors using different measures of success~\cite{tsay14icse,tsay14fse}. 
 This study aims to acknowledge the impact of some of these attributes when it 
 comes to the quality of the commits developers write and its success when 
-integrating into the project build through Travis CI. The knowledge obtained by 
+integrating into the project build through Travis CI.
+
+The knowledge obtained by 
 analyzing how much impact social characteristics have on the success of a commit 
@@
 factors and pull request acceptance. In the interest of understanding if these 
-relationship will hold with a different success measure such as commit 
-integration success, and in order to establish a baseline to compare to, we 
-deliver our first research question:
-\newline \newline
-\textbf{What is the relationship, if any, between technical attributes that 
-describe the complexity of a commit (such as files added, tests added, lines of 
-code, etc) and the final status of the Travis jobs this commit triggers?}
-\newline \newline
-Assuming the previous studies hold to this different success measure, and there 
-is a relationship between technical attributes and commit integration success, 
-we are afterwards interested in knowing if adding social attributes to this 
+relationship hold with a different success measure such as commit 
+integration success, and in order to establish a baseline to compare to, we have created a dataset with technical attributes to be able to analyze the predictiveness of these attributes and its relationship with commit integration success.
+This way, we are able to create a model
+
+We are afterwards interested in knowing if adding social attributes to this 
 predictability model will increase the probability of the model asserting 
 correctly future instances by knowing not only technical data about the commit 
-being pushed but also social attributes of the developer pushing the changes:
+being pushed but also social attributes of the developer pushing the changes. Therefore our main research question is presented as follows:
 \newline \newline
-\textbf{Given the dataset described before, are the social attributes gathered 
-from the Github profiles of developers who pushed those commits, able to 
-increase the predictive power of a model created from the technical dataset?}
+\textbf{Are the social attributes gathered 
+from the Github profiles of developers who push commits, able to 
+increase the predictive power of a model created from technical attributes of the pushed commits?}
 \newline \newline
-We are also interested in knowing what attributes, either from the technical 
+Concerning the results of this research question we can also derive parallel important information. For example, we are also interested in knowing what attributes, either from the technical 
 background, the social background, and both combined, are the best proxies for 
-knowing what will be the success of the commit integration:
-\newline \newline
-\textbf{Which attributes (in social data, technical data, and both together) are 
-the most decisive in order to know if a commit will be successful or not?}
-\newline \newline
-Finally, we would like to know if/which social attributes have a significant 
-impact in success of commit integration to a project: \todo{I'm not sure what's 
-the difference between this RQ and the last one}
-\newline \newline
-\textbf{Does any of the social attributes have a significant impact in the 
-likelihood of commit integration success?}
-\newline \newline
+knowing what will be the success of the commit integration, helping both developers and integrators to find ways to help them check the success likeliness of a commit based on metadata of the commit.
 

### 2017-02-17 genderComputer/genderComputer.py
trying to merge

@@ -1,694 +1,0 @@
-# This Python file uses the following encoding: utf-8
-
-"""Copyright 2012-2013
-Eindhoven University of Technology
-Bogdan Vasilescu
-
-This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU Lesser General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-GNU Lesser General Public License for more details.
-
-You should have received a copy of the GNU Lesser General Public License
-along with this program.  If not, see <http://www.gnu.org/licenses/>."""
-
-import os
-import re
-from dictUtils import MyDict
-from unicodeMagic import UnicodeReader
-from unidecode import unidecode
-from nameUtils import only_greek_chars, only_cyrillic_chars
-from nameUtils import leet2eng, inverseNameParts, extractFirstName
-from filters import normaliseCountryName
-
-
-
-def simplifiedGender(gender):
-	if gender is not None:
-		if gender == 'mostly male':
-			return 'male'
-		elif gender == 'mostly female':
-			return 'female'
-		# elif gender == 'unisex':
-		# return ''
-		else:
-			return gender # male, female, unisex
-	return None
-
-def formatOutput(gender, simplified=True):
-	if simplified:
-		return simplifiedGender(gender)
-	else:
-		return gender
-
-
-'''Load the male and female name lists for <country>'''
-def loadData(country, dataPath, hasHeader=True):
-	def loadGenderList(gender, country, dataPath, hasHeader):
-		fd = open(os.path.join(dataPath, '%s%sUTF8.csv' % (country, gender)), 'rb')
-		reader = UnicodeReader(fd)
-		names = {}
-		if hasHeader:
-			unused_header = reader.next()
-		'''Load names as-is, but lower cased'''
-		for row in reader:
-			name = row[0].lower()
-			try:
[…]

### 2017-02-17 Paper/MSRChallenge2017.tex
some threats to validity and table

@@
 attributes and how these relate to the success of the integration of a commit 
-pushed by the developer being described by these social attributes. %, and not 
-interactions between developers, or technical properties of the project.
+pushed by the developer being described by these social attributes.
+%, and not 
+%interactions between developers, or technical properties of the project.
+
+\todo{Contributions}
 
@@
 
+\todo{Explain downsampling}
+
 \section{Evaluation}
+\todo{I guess we have to remove the logisitic regression section here if we are not going to present those results. Depending on what Bogdan and Claire think.}
 To evaluate the predictive power we can gain from analyzing the corpus 
@@
 \section{Results}
-Results \todo{maybe this section can be merged with the prior one}
+Results \todo{maybe this section can be merged with the prior one} Table \ref{resultsTable}
+
+\begin{table*}[ht]
+\centering
+\begin{tabular}{l||r|r||r|r}
+  & \multicolumn{2}{|c||}{Original number of instances}  & \multicolumn{2}{|c}{Downsampled} \\
+\hline
+  & Technical & Technical and Social & Technical & Technical and Social \\
+\hline
+\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\
+
+\textbf{Incorrectly Classified Instances}&  22.99\% & 18.90\% & 35.90\% & 23.91\%\\
+
+\textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\
+
+\textbf{Mean absolute error}& 0.34 &  0.28 & 0.43 & 0.32\\
+
+\textbf{Relative absolute error}& 88.64\% & 72.42\%  & 85.35\% & 63.07\%\\
+\hline
+\textbf{Increase when adding social attributes}& \multicolumn{2}{|c||}{4.09\%}  & \multicolumn{2}{|c}{11.99\%}\\
+
+\hline
+\end{tabular}
+\\
+\center
+  \caption{ Second and third columns: Comparison of performance when running 10 fold cross validation of two decision trees.
+The first column after the first double bar uses only technical attributes to predict the Travis Job status, the second column augments the dataset with social attributes.
+Fourth and fifth columns: The same intuition as the previous two, with the difference that the dataset was downsampled to provide the same number of successful and unsuccessful instances }
+  \label{resultsTable}
+\end{table*}
 
@@
 
+\section{Threats to validity}
+
+\noindent\textbf{Internal validity:}
+The internal validity threats deal with possible errors in our implementation and experiments.
+The researchers in this study used the dataset provided by the MSRChallenge~\cite{msr17challenge} to gain useful information regarding the behavior of developers when pushing commits and how well these commits integrate successfully with the project.
+The authors have used Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for usage of machine learning algorithms to analyze our datasets.
+We are aware that, as every human written tool, Weka is prone to contain errors and/or bugs; nonetheless, Weka is a broadly used, open source tool that is subject to high quality standards and a vast user and developer base which makes it more likely to be a high quality code and to have less bugs than lesser used tools.
+
+The scripts we have created to adapt and extract the datasets we needed, and the scripts to obtain the developer social data are publicly available to facilitate the transparency and quality of the process.\footnote{https://goo.gl/CqTX44}
+
+\noindent\textbf{External validity:} 
+External validity threats deal with the generalizability of our findings. 
+To tackle the concern that the results of this study might not generalize to other studies outside of the studied cases, we have used a broad and rich dataset~\cite{msr17challenge} in our analysis.
+
+\noindent\textbf{Construct validity:}
+Regarding the suitability of our evaluation metrics,
+
 \section{Conclusion}
@@
 % conference papers do not normally have an appendix
-
-\section{Threats to validity}
-
-\textbf{Internal}
-
-\textbf{External}
-
-\textbf{Structural}
 

### 2017-02-17 Paper/MSRChallenge2017.tex
rewrote part of the evaluation section

@@
 \item Following
-\item ContribProjects
+\item Contributions 
 \end{itemize}
@@
 Following detail the number of developers that are following and being followed 
-by the developer in question. Finally, the last attribute studies is the number 
+by the developer in question. Finally, the last attribute studied is the number 
 of contributions made by the developer in the last year. To this dataset, we 
@@
 \todo{I guess we have to remove the logisitic regression section here if we are not going to present those results. Depending on what Bogdan and Claire think.}
-To evaluate the predictive power we can gain from analyzing the corpus 
-provided~\cite{msr17challenge}, we have created a logistic regression model from 
-both the datasets described in Section \ref{approach}. A logistic regression 
-model is one where the dependent variable is categorial~\cite{freedman09}. Since 
-in this study we are interested only in the cases where the commit was 
-successfully integrated against any other possible state (errored, failed, 
-canceled, started), we have divided our corpus into only two possible states, 
-successful and notSuccessful, as to have a binary dependent variable.
+\todo{consider moving this data preprocessing step to the previous section}
+To explore how much social aspects contributed to the build success, we first
+converted the build statuses to successful (passed) and not successful (errored,
+failed, canceled, and started).  We then created a decision tree classifier
+using the technical data to establish how influential the technical data is on 
+build success.  We then added the social data to the technical data and used
+that to create a new decision tree classifier.  The decision trees were
+evaluated using ten fold cross validation.
 
-A binary logistic model is a mechanism used to calculate the probability of 
-characterizing a binary dependent variable based on one or more independent 
-variables~\cite{walker67,cox58}. In our study, the binary dependent variable 
-would become the final status of the Travis CI jobs triggered by the commit 
-pushed by the developer, and the independent variables are both the technical 
-attributes (files added, files deleted, source churn, etc) and the social 
-attributes (stars, followers, repositories, etc.) used to predict the the class 
-value.
-
+\todo{this paragraph is now out of place.  Decide where to move it.}
 We also evaluate our dataset by using decision trees, a predictive model which 

### 2017-02-17 Paper/MSRChallenge2017.tex
removed result line

@@
 \begin{abstract}
-Abstract goes here
+\todo{Abstract goes here}
 \end{abstract}
@@
 
-The dataset provided by the MSR Challenge~\cite{msr17challenge} is very diverse 
-and consists of commits that date from very far back, and the social data we are 
+The dataset used in this study~\cite{msr17challenge} is very diverse 
+and consists of commits that date from far back, and the social data we are 
 gathering is recent data, gathered in January 2017. The researchers of this 
@@
 
-\todo{Explain downsampling}
+We constructed a decision tree with the dataset before mentioned, and we noticed that at this point the training data was unbalanced in a ratio close to 3:1 regarding successful and unsuccessful instances accordingly.
+To mitigate the risk of this being a skewing factor for the training process of the decision tree, we sampled randomly the successful instances to get an equal distribution of
+successful and unsuccessful instances to train the decision tree. We present the results of both of these datasets in the following section.
 
@@
 \section{Results}
-Results \todo{maybe this section can be merged with the prior one} Table \ref{resultsTable}
 
@@
 \section{Discussion}
-Discussion
+In this study we have analyzed how considering social data is beneficial to be able to predict if a commit will be successfully integrated into a project or not.
+We have analyzed different technical complexity measures that work as a proxy for the complexity of the task being commited, such as number of files added, size of the project, size of the commit, etc.
+It is worth noticing that these are not the only measures that can be used as a proxy for technical complexity of a commit.
+The same intuition applies to the social attributes we gathered.
+These are not the only proxies for experience a developer may have, but we are making use of a suitable feature Github provides, which are the social attributes being measured in this study.
+
+This study is consistent with previous studies~\cite{Yu15,tsay14icse,tsay14fse} that show the importance of considering social traits  when dealing with a merely social process such as the software development process.
 
@@
 \noindent\textbf{Internal validity:}
-The internal validity threats deal with possible errors in our implementation and experiments.
-The researchers in this study used the dataset provided by the MSRChallenge~\cite{msr17challenge} to gain useful information regarding the behavior of developers when pushing commits and how well these commits integrate successfully with the project.
-The authors have used Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for usage of machine learning algorithms to analyze our datasets.
-We are aware that, as every human written tool, Weka is prone to contain errors and/or bugs; nonetheless, Weka is a broadly used, open source tool that is subject to high quality standards and a vast user and developer base which makes it more likely to be a high quality code and to have less bugs than lesser used tools.
+The internal validity threats deal with possible errors in our implementation 
+and experiments.
+The researchers in this study used the dataset provided by the 
+MSRChallenge~\cite{msr17challenge} to gain useful information regarding the 
+behavior of developers when pushing commits and how well these commits integrate 
+successfully with the project. The authors have used 
+Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for 
+usage of machine learning algorithms to analyze our datasets. We are aware that, 
+as every human written tool, Weka is prone to contain errors and/or bugs; 
+nonetheless, Weka is a broadly used, open source tool that is subject to high 
+quality standards and a vast user and developer base which makes it more likely 
+to be a high quality code and to have less bugs than lesser used tools.
 
-The scripts we have created to adapt and extract the datasets we needed, and the scripts to obtain the developer social data are publicly available to facilitate the transparency and quality of the process.\footnote{https://goo.gl/CqTX44}
+The scripts we have created to adapt and extract the datasets we needed, and the 
+scripts to obtain the developer social data are publicly available to facilitate 
+the transparency and quality of the process.\footnote{https://goo.gl/CqTX44}
 
@@
 External validity threats deal with the generalizability of our findings. 
-To tackle the concern that the results of this study might not generalize to other studies outside of the studied cases, we have used a broad and rich dataset~\cite{msr17challenge} in our analysis.
+To tackle the concern that the results of this study might not generalize to 
+other instances outside of the studied cases, we have used a broad and rich 
+dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
+projects used in this dataset have also been filtered to be popular (having more 
+than 10 watches on Github), and to have a history of using the continuous 
+integration tool Travis CI for more than 50 builds. All these features help to 
+build the notion that since we are building our analysis on top of a vast 
+dataset comprehending a wide diversity of projects, the threat of this analysis 
+not generalizing to other projects is mitigated.
 
 \noindent\textbf{Construct validity:}
-Regarding the suitability of our evaluation metrics,
+Regarding the suitability of our evaluation metrics, the authors understand that 
+Travis job success is not the only way to analyze the success of a commit, and 
+that for different reasons the job may not be successful even if the code 
+commited does not have flaws (a flacky test case for example). Since continuous 
+integration is a best known practice in industry and the use of this methodology 
+spreads out into the open source community, we consider that cases of misuse of 
+CI such that it will lead to failing travis jobs when they should have actually 
+be successful are minimum, specially since having a solid build is one of the 
+main purposes of the methodology, and taking into account that the projects in 
+out dataset are projects with a history of using continuous integration and 
+having a certain level of popularity, this threat is minimized. We therefore 
+consider Travis job success to be a proxy 
+for success when integrating a commit into a larger project.
 
 \section{Conclusion}
-The conclusion goes here. this is more of the conclusion
+In this study we have analyzed the probability of Travis job success as being predicted by two different categories of attributes: Technical and Social data.
+We gathered the attributes that describe complexity of each commit being pushed and have created a decision tree that predicts if a future pushed commit will be successfully integrated into its corresponding build or not.
+Afterwards, we have gathered social attributes from the developers who pushed each of these commits
+and we have augmented our dataset with these attributes to understand whether adding social information about the developer would help the decision tree predict with higher accuracy future 
+instances.
+
+Our results show that adding social data to the construction of the decision tree increases the probability this correctly predicting future commit's success in integrating into their corresponding projects by a margin of 4.09\% to 11.99\%, depending on the ratio of successful vs unsuccessful instances are used to train the desicion tree.
+\todo{maybe add here some other answers to smaller deduced RQ's}
 

### 2017-02-17 Paper/MSRChallenge2017.tex
discussion and downsampling

@@
 \item Following
-\item Contributions 
+\item ContribProjects
 \end{itemize}
@@
 Following detail the number of developers that are following and being followed 
-by the developer in question. Finally, the last attribute studied is the number 
+by the developer in question. Finally, the last attribute studies is the number 
 of contributions made by the developer in the last year. To this dataset, we 
@@
 \todo{I guess we have to remove the logisitic regression section here if we are not going to present those results. Depending on what Bogdan and Claire think.}
-\todo{consider moving this data preprocessing step to the previous section}
-To explore how much social aspects contributed to the build success, we first
-converted the build statuses to successful (passed) and not successful (errored,
-failed, canceled, and started).  We then created a decision tree classifier
-using the technical data to establish how influential the technical data is on 
-build success.  We then added the social data to the technical data and used
-that to create a new decision tree classifier.  The decision trees were
-evaluated using ten fold cross validation.
+To evaluate the predictive power we can gain from analyzing the corpus 
+provided~\cite{msr17challenge}, we have created a logistic regression model from 
+both the datasets described in Section \ref{approach}. A logistic regression 
+model is one where the dependent variable is categorial~\cite{freedman09}. Since 
+in this study we are interested only in the cases where the commit was 
+successfully integrated against any other possible state (errored, failed, 
+canceled, started), we have divided our corpus into only two possible states, 
+successful and notSuccessful, as to have a binary dependent variable.
 
-\todo{this paragraph is now out of place.  Decide where to move it.}
+A binary logistic model is a mechanism used to calculate the probability of 
+characterizing a binary dependent variable based on one or more independent 
+variables~\cite{walker67,cox58}. In our study, the binary dependent variable 
+would become the final status of the Travis CI jobs triggered by the commit 
+pushed by the developer, and the independent variables are both the technical 
+attributes (files added, files deleted, source churn, etc) and the social 
+attributes (stars, followers, repositories, etc.) used to predict the the class 
+value.
+
 We also evaluate our dataset by using decision trees, a predictive model which 
@@
 \section{Results}
+Results \todo{maybe this section can be merged with the prior one} Table \ref{resultsTable}
 

### 2017-02-17 Paper/MSRChallenge2017.tex
added the results

--- 2017-02-17 Paper/MSRChallenge2017.tex
@@
 
+\subsection{Success Classification}
 \begin{table*}[ht]
@@
 \end{table*}
+
+Table~\ref{resultsTable} shows the results of running the data sets through the
+default Weka J48 decision tree algorithm. 
+In the original data set, 74.43\% of the builds were successful, the rest were not
+successful.  This means that a classifier which guesses successful every time
+would produce a classification rate of 74.43\%. The decision tree built from
+only the technical indicators has a correct classification rate of 77.01\%, so
+the technical attributes only increased the prediction accuracy by about 3\%.
+Adding the social data increased the classifier's accuracy from 77.01\% to
+81.10\%, about a 4\% increase.
+
+On the downsampled data, the decision tree created from the technical attributes
+had a classification accuracy of 64.10\%, when predicting a successful build in
+all instances would produce 50.00\% accuracy.  After including the social data
+in the data set, the classifier correctly predicted 76.09\% of the data set,
+about a 12\% improvement from only the technical data.
+
+The same
+
+\subsection{Build success by core team member}
+
+For the build success investigation, we classified the build success rate for
+core team members and non-core team members.  We found that core team members
+triggered of 89.39\% of the builds in the data set and 75.58\% of those builds
+passed.  Non-core team members triggered 10.61\% of the builds in the data set
+and 64.70\% of the builds passed.
 

### 2017-02-17 Paper/MSRChallenge2017.tex
added the results

@@
 \begin{abstract}
-\todo{Abstract goes here}
+One important aspect of developing open source software is deciding which
+commits to include in the main branch of a project.  
+Recent research has started to explore how the open source community manages
+this question and found that both technical and social factors are factors in 
+the success of project contributions on GitHub.  
+This investigation defined a successful project contribution as a project
+contribution that gets
+accepted to the project.  However, with the continuous integration, we can
+explore this question a step further.  We can better estimate the success of a
+contribution by investigating if the contribution passed the project's
+test cases.  We performed an initial investigation into the technical and
+social factors involved in a commit that successfully passes the integration
+tests. Specifically, we investigated if social factors (such as being a
+core member of the development team, having a large number of followers,
+or contributing a large number of commits) improve predictions of build
+success.  We have found that while social factors cause an noticeable increase
+in predictive power (12\%), further investigation into these factors are
+required.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-social attributes; Travis CI; Github; social networks; predicting integration success; social coding
-
+Social Attributes; Travis CI; Github; Social Networks; Predicting Integration 
+Success; Social Coding
 \end{IEEEkeywords}

### 2017-02-18 Paper/MSRChallenge2017.tex
rewrote the introduction

@@
 \section{Introduction}
-Social interactions and attributes play a key role in software quality output 
-from development teams~\cite{nagappan08,bettenburgh10}, these aspects have 
-become more and more important and platforms that support software development 
-processes provide every time a broader spectrum of measurements for social 
-characteristics. Because of this we now have a wide variety of measurable social 
-attributes that can be studied and analyzed to understand their correlation and 
-impact on different success measures.
+For managers of an open source project, it is important to ensure that the
+project consists of high quality contributions.  The decision to include code in
+a project has been described as a meritocracy, where only the code is a factor
+in the decision~\cite{Scacchi07}.  However, to better understand successful 
+project contributions, we must analyze factors which are common to all commits.
 
-Similar studies in recent years have analyzed the relationship between social 
-and technical factors using different measures of success~\cite{tsay14icse,tsay14fse}. 
-This study aims to acknowledge the impact of some of these attributes when it 
-comes to the quality of the commits developers write and its success when 
-integrating into the project build through Travis CI.
+Over the years, the open source
+community has developed various techniques to vet project contributions, such as pull
+requests which must be approved by a core team member~\cite{gousios14}. One such
+technique is continuous integration. Continuous integration automatically checks
+the contribution against the project's test cases, to notify the development
+team if the change caused a test case failure~\cite{Meyer14}.  When a change
+passes one of these vetting techniques, it shows that the project developers
+have confidence in the changes.
+
+In past studies, both technical factors and social factors have been found to be
+important when when predicting pull request success~\cite{tsay14icse,tsay14fse}.
+Yet, these factors may not be as important during continuous integration.
+Specifically, we want to investigate if social factors, which can be used a
+proxy for experience, are important when predicting build success when grouped
+with technical data, used as a proxy for commit complexity.
 

### 2017-02-18 Paper/MSRChallenge2017.tex
minor revisions to related work and research design

@@
 analyze the impact of CI usage in Github and its correlation with software 
-quality. Unlike the before mentioned, our study focuses on independent social 
+quality. Unlike the works previously listed, our study focuses on independent social 
 attributes and how these relate to the success of the integration of a commit 
 pushed by the developer being described by these social attributes.
-%, and not 
-%interactions between developers, or technical properties of the project.
 
-\todo{Contributions}
+Our study shows that social factors are an important aspect of build success but
+these factors alone do not fully predict if a build will succeed.  We also show
+that core team members are more likely to achieve build success than non-core
+team members.
 
@@
 The goal of this study is to have a deeper understanding of the relationship 
-between the several different social properties that are gathered in a 
-developer's online profile, and the likelihood of a commit performed by that 
-developer to be considered a successfully integrated into its corresponding 
-project according to Travis CI depending on the social attributes of the 
-developer.
+between the several different social properties that that estimate the
+developer's experience, and the likelihood of a developer's commit
+to be considered a successfully integrated in the project. We define successful
+integration as passing the continuous integration build tests in the project.
 

### 2017-02-18 Paper/MSRChallenge2017.tex
rewrote the question subsection

@@
 \usepackage{booktabs}
+\usepackage{verbatim}
 \newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
@@
 Previous studies have identified a relationship between technical and social 
-factors and pull request acceptance. In the interest of understanding if these 
-relationship hold with a different success measure such as commit 
-integration success, and in order to establish a baseline to compare to, we have created a dataset with technical attributes to be able to analyze the predictiveness of these attributes and its relationship with commit integration success.
+factors and pull request acceptance. We are interested in understanding if
+social factors, that proxy experience, can be used to predict a
+a different success measure: continuous integration success.
+
+Therefore our main research question is presented as follows:
+\newline \newline
+\textbf{Do social attributes, gathered 
+from the Github profiles of developers,
+allow for more accurate predictions than only using technical data?}
+\newline \newline
+
+Depending on the results of this question, we can further explore which
+attributes are most important for predicting build integration success.
+
+\begin{comment}
+we have created a dataset with technical attributes to be able to analyze the predictiveness of these attributes and its relationship with commit integration success.
 This way, we are able to create a model
-
 We are afterwards interested in knowing if adding social attributes to this 
@@
 correctly future instances by knowing not only technical data about the commit 
-being pushed but also social attributes of the developer pushing the changes. Therefore our main research question is presented as follows:
-\newline \newline
-\textbf{Are the social attributes gathered 
-from the Github profiles of developers who push commits, able to 
-increase the predictive power of a model created from technical attributes of the pushed commits?}
-\newline \newline
-Concerning the results of this research question we can also derive parallel important information. For example, we are also interested in knowing what attributes, either from the technical 
-background, the social background, and both combined, are the best proxies for 
-knowing what will be the success of the commit integration, helping both developers and integrators to find ways to help them check the success likeliness of a commit based on metadata of the commit.
+being pushed but also social attributes of the developer pushing the changes.
+\end{comment}
 

### 2017-02-18 Paper/MSRChallenge2017.tex
editted the results

@@
 
-\section{Building and Augmenting dataset with social attributes} 
+\section{Building Dataset}
 \label{approach}
-For this section our goal is to build a dataset based on the attributes that are 
-intrinsic for the commit complexity and therefore for its probability of leading 
-to a successful Travis CI job.
-To do this we extracted the attributes from the original dataset 
-provided~\cite{msr17challenge} which work as a proxy for the complexity of the 
-commit being pushed.
+To investigate our research questions, we built a dataset based on the 
+attributes that consisted of both technical and social factors.  We collected
+the technical factors from the provided data set~\cite{msr17challenge}.
+We extracted only the attributes in the data set that proxy the commit's
+complexity and the build status.
 \begin{itemize}
@@
 \item gh\_sloc 
-%\item tr\_status 
+\item tr\_status 
 \end{itemize}
 
-Once we had these attributes, we removed repeated rows and we gathered the 
-social attributes for each of these rows.
+Once we had these attributes, we removed repeated rows \todo{Why did we have to
+remove repeated rows?}
 
-To do this, we extracted from the original file provided~\cite{msr17challenge} 
-the commit hash and the project name. We removed the repeated rows and created a 
-script to gather the social data of the developer who pushed that commit.
-First we concatenated the two attributes before mentioned in the following way:
+To collect the social data, we created a web crawler to extract the social data
+from developer's profiles.
+We used the commit hash and the project name in the original data
+set~\cite{msr17challenge} to locate the webpage of the commit using the syntax
+below. 
 \newline \newline
@@
 \newline \newline
-We created a script that constructs this string and navigates through the html 
-representation of the website described above, and looks for the 
-\textit{username} of the developer in the Github platform. If it is able to find 
-one, we then create another string following the pattern:
+Then, we scraped the commit author's
+\textit{username} from the page. If the scrapper was able to find username, the
+scraper went to the user's profile information using the syntax below.
 \newline \newline
@@
 \newline \newline
-We then navigate through the html representation of the developer's profile 
-website (described above) and gather the following attributes:
+The scrapper then extracted the following items from the user's profile.
 \begin{itemize}
@@
 
-Repositories alludes to the repositories the developer has access to. This 
+Repositories represents the repositories the developer has access to. This 
 includes where the developer is the repository owner,where the developer is a 
@@
 organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
-show the projects the developer has stared, where starring translates to showing 
-appreciation to the repository and creating a bookmark for later 
+represents a count of the projects the developer has stared. Starring  a project
+means to showing approval of the repository and creating a bookmark for later 
 access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
@@
 by the developer in question. Finally, the last attribute studied is the number 
-of contributions made by the developer in the last year. To this dataset, we 
-also added from the original dataset provided~\cite{msr17challenge} the 
-attribute gh\_by\_core\_team\_member which we considered to have also social 
-weight, which describes if the developer pushing the commit is a core member of 
-the project the commit is being pushed to.
+of contributions made by the developer in the last year.
 
-After performing this last data mining task, we created two different datasets. 
-One of them contains technical data that is seen as a proxy for the complexity 
-of the changes being performed in the commit. We also created a second dataset 
-which consists of the data mentioned in the first dataset, plus the set of 
-social attributes related to the developer who pushed the commit.
+We also added one item from the original data set to the social factors:
+gh\_by\_core\_team\_member.
+This factor indicates if the developer making a contribution is a core member 
+of that project.
+
+We used this data to create two data sets.  One with only the technical
+factors and the build status, and another with both the technical and social
+factors along with the build status.
 
@@
 gathering is recent data, gathered in January 2017. The researchers of this 
-project acknowledge this discrepancy and in an effort to mitigate this threat to 
-validity, we filter the commits analyzed by looking only at the commits pushed 
-in the last 3 years of the dataset (2014,2015,2016), with the intuition that the 
-social data gathered by this study will have a closer relationship to the social 
-data if it were to be gathered in these years, than if we would compare it to 
-years further back.
+project acknowledge this discrepancy and in an effort to mitigate the threat of
+using future result to predict previous events,
+we removed the commits in the dataset that were not performed within the last
+three years of the data set's release (2014,2015,2016).  While this is not
+perfect, we believe that these numbers are unlikely to have changed
+significantly in the last three years.
 
-We constructed a decision tree with the dataset before mentioned, and we noticed that at this point the training data was unbalanced in a ratio close to 3:1 regarding successful and unsuccessful instances accordingly.
-To mitigate the risk of this being a skewing factor for the training process of the decision tree, we sampled randomly the successful instances to get an equal distribution of
-successful and unsuccessful instances to train the decision tree. We present the results of both of these datasets in the following section.
+After building the data set, we converted the various Travis build statuses to
+successful (passed in the data set) or not successful (errored, failed, canceled
+and started in the data set).  This still left a big discrepancy in the two
+categories, with about a 3:1 successful to not successful ratio. To avoid having
+this discrepancy alter our results, we created a separate data set where the
+successful builds were randomly selected until the number of successful builds
+equaled the number of not successful builds (downsampled).  We used both the
+downsampled and non-downsampled data sets in our results.
 
 \section{Evaluation}
-\todo{I guess we have to remove the logisitic regression section here if we are not going to present those results. Depending on what Bogdan and Claire think.}
-\todo{consider moving this data preprocessing step to the previous section}
-To explore how much social aspects contributed to the build success, we first
-converted the build statuses to successful (passed) and not successful (errored,
-failed, canceled, and started).  We then created a decision tree classifier
-using the technical data to establish how influential the technical data is on 
-build success.  We then added the social data to the technical data and used
-that to create a new decision tree classifier.  The decision trees were
-evaluated using ten fold cross validation.
 
-\todo{this paragraph is now out of place.  Decide where to move it.}
-We also evaluate our dataset by using decision trees, a predictive model which 
-branches the different possible class values (represented as the leaves) 
-depending on the attributes used to predict the class value (represented as the 
-branches). In classification trees as the one being used in this study, each 
-attribute represents a branch (with some exceptions due to pruning) and 
-depending on the decisions taken while traversing the tree, the class value will 
-be determined when one of the decisions leads to a leaf of the tree, therefore a 
-class value will be encountered and a prediction can be made.
+We evaluated the predictive power of the social factors using a decision
+tree.\todo{citation needed}
+Decision trees are a predictive model which uses binary decisions on the
+attributes to predict a final class.  The predicted class is represented as the
+leaves, while the attribute decisions used in the prediction cause the
+different branches.
+In this study, we used the J48 Weka decision tree \todo{citation needed} with default settings. The 
+decision trees were evaluated using ten fold cross validation with the data in
+each data set.
 
@@
 
-Table~\ref{resultsTable} shows the results of running the data sets through the
-default Weka J48 decision tree algorithm. 
 In the original data set, 74.43\% of the builds were successful, the rest were not
 successful.  This means that a classifier which guesses successful every time
-would produce a classification rate of 74.43\%. The decision tree built from
-only the technical indicators has a correct classification rate of 77.01\%, so
-the technical attributes only increased the prediction accuracy by about 3\%.
+would produce a classification rate of 74.43\% if ran on the full data set.
+
+Table~\ref{resultsTable} shows the results of running the two data sets through the
+default Weka J48 decision tree algorithm.The decision tree built from
+only the technical indicators has a correct classification rate of 77.01\% which
+means the technical attributes only increased the prediction accuracy by about 3\%.
 Adding the social data increased the classifier's accuracy from 77.01\% to
@@
 about a 12\% improvement from only the technical data.
-
-The same
 
@@
 \section{Discussion}
-In this study we have analyzed how considering social data is beneficial to be able to predict if a commit will be successfully integrated into a project or not.
-We have analyzed different technical complexity measures that work as a proxy for the complexity of the task being commited, such as number of files added, size of the project, size of the commit, etc.
-It is worth noticing that these are not the only measures that can be used as a proxy for technical complexity of a commit.
-The same intuition applies to the social attributes we gathered.
-These are not the only proxies for experience a developer may have, but we are making use of a suitable feature Github provides, which are the social attributes being measured in this study.
+We have found that social attributes which proxy experience produce a small but
+noticeable increase in predicting build success.  While the increase was very
+small with the full data set, there was a greater increase in prediction
+accuracy after performing downsampling.  These results show that experience is
+important to predicting build commit success but a strong predictor.
 
-This study is consistent with previous studies~\cite{Yu15,tsay14icse,tsay14fse} that show the importance of considering social traits  when dealing with a merely social process such as the software development process.
+The build success by core team member results show that core team members are
+more likely to have the build integration pass than non-core team members.  This
+result provides evidence that non-core team member commit are not throughly
+scrutinized, although further studied will be required to draw definite
+conclusions.
 
@@
 \section{Threats to validity}
+This study contains various threats to validity.
 
 \noindent\textbf{Internal validity:}
-The internal validity threats deal with possible errors in our implementation 
-and experiments.
 The researchers in this study used the dataset provided by the 

### 2017-02-18 Paper/MSRChallenge2017.tex
rewrote the threats to validity and the conclusion

@@
 \noindent\textbf{Internal validity:}
-The researchers in this study used the dataset provided by the 
-MSRChallenge~\cite{msr17challenge} to gain useful information regarding the 
-behavior of developers when pushing commits and how well these commits integrate 
-successfully with the project. The authors have used 
-Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for 
-usage of machine learning algorithms to analyze our datasets. We are aware that, 
-as every human written tool, Weka is prone to contain errors and/or bugs; 
-nonetheless, Weka is a broadly used, open source tool that is subject to high 
-quality standards and a vast user and developer base which makes it more likely 
-to be a high quality code and to have less bugs than lesser used tools.
+One source of internal validity concern is the time mismatch between the
+technical and social data.  We restricted the commits to only the commits in the
+last three years of the data set to reduce this concern.
+There is also a chance that scripts we used to create the data sets contain an
+error.  For full transparency, we've released the scripts used to collect the
+data set at (This will be added after the anonymous review).
 
-The scripts we have created to adapt and extract the datasets we needed, and the 
-scripts to obtain the developer social data are publicly available to facilitate 
-the transparency and quality of the process.\footnote{https://goo.gl/CqTX44}
+%footnote{https://goo.gl/CqTX44}
 
 \noindent\textbf{External validity:} 
-External validity threats deal with the generalizability of our findings. 
-To tackle the concern that the results of this study might not generalize to 
-other instances outside of the studied cases, we have used a broad and rich 
-dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
-projects used in this dataset have also been filtered to be popular (having more 
-than 10 watches on Github), and to have a history of using the continuous 
-integration tool Travis CI for more than 50 builds. All these features help to 
-build the notion that since we are building our analysis on top of a vast 
-dataset comprehending a wide diversity of projects, the threat of this analysis 
-not generalizing to other projects is mitigated.
+While we have used a data set with high quality standards~\cite{msr17challenge},
+these results may not generalized to non-open source projects.
 
 \noindent\textbf{Construct validity:}
-Regarding the suitability of our evaluation metrics, the authors understand that 
-Travis job success is not the only way to analyze the success of a commit, and 
-that for different reasons the job may not be successful even if the code 
-commited does not have flaws (a flacky test case for example). Since continuous 
-integration is a best known practice in industry and the use of this methodology 
-spreads out into the open source community, we consider that cases of misuse of 
-CI such that it will lead to failing travis jobs when they should have actually 
-be successful are minimum, specially since having a solid build is one of the 
-main purposes of the methodology, and taking into account that the projects in 
-out dataset are projects with a history of using continuous integration and 
-having a certain level of popularity, this threat is minimized. We therefore 
-consider Travis job success to be a proxy 
-for success when integrating a commit into a larger project.
+While we believe the build status is a good metric for contribution success,
+there is the chance that a problem in the projects's test cases, and no the
+contribution itself, led to the build failure.
 
 \section{Conclusion}
-In this study we have analyzed the probability of Travis job success as being predicted by two different categories of attributes: Technical and Social data.
-We gathered the attributes that describe complexity of each commit being pushed and have created a decision tree that predicts if a future pushed commit will be successfully integrated into its corresponding build or not.
-Afterwards, we have gathered social attributes from the developers who pushed each of these commits
-and we have augmented our dataset with these attributes to understand whether adding social information about the developer would help the decision tree predict with higher accuracy future 
-instances.
-
-Our results show that adding social data to the construction of the decision tree increases the probability this correctly predicting future commit's success in integrating into their corresponding projects by a margin of 4.09\% to 11.99\%, depending on the ratio of successful vs unsuccessful instances are used to train the desicion tree.
-\todo{maybe add here some other answers to smaller deduced RQ's}
+In this study we have analyzed the ability to use social factors to predict
+build integration success.
+Our results show that adding social data, which proxies experience, provides a
+small increases in prediction accuracy.  This leads us to conclude that while
+experience is important, it is not the only factor in build success.
+We have also found that non-core contributors cause not successful builds more
+than core contributors.  This leads us to believe that non-core contributions
+are not inspected as closely as they should be.
 

### 2017-02-18 Paper/MSRChallenge2017.tex
added decision tree citations

@@
 We evaluated the predictive power of the social factors using a decision
-tree.\todo{citation needed}
+tree~\cite{Quinlan86}.
 Decision trees are a predictive model which uses binary decisions on the
@@
 different branches.
-In this study, we used the J48 Weka decision tree \todo{citation needed} with default settings. The 
-decision trees were evaluated using ten fold cross validation with the data in
-each data set.
+In this study, we used the Weka~\cite{Weka} J48~\cite{Quinlan1993} decision tree
+with default settings. The decision trees were evaluated using ten fold cross 
+validation with the data in each data set.
 
@@
 
+\subsection{Follower effect on build success}
+
+We also investigated if developers with followers were more likely to have a
+successful build integration, since have followers may be seen as vouching for
+the developer's abilities.  We specifically investigated if a developer with 
+followers was more likely to pass the build.  We found that only 0.87\% of the
+contributions in the data set was performed by developers with zero 
+followers (excluding the developers in which we were not able to extract profile
+information for). We found that 99.13\% of the contributions were performed by
+developers with at least one or more followers.
+We found that developers with 0 followers had a successful build commit 68.49\%
+of the time.  Developers with one or more followers were successful 74.78\% of
+the time.
+
+We also investigated developers with a large number of followers (1000 or more
+followers).  We found that 6.94\% of the contributions in the data set were
+performed by developers with 1000 or more followers.  We found that these
+contributions had a 78.61\% success rate.
+
 \section{Discussion}
@@
 conclusions.
+
+The follower results indicate that developers with more followers are more
+likely to pass the build, although followers are not a perfect indicator.
+Developers with over 1000 followers had more than a 10\% increase compared to
+developers with no followers.  This shows that high-quality developers are more
+likely to have a large number of followers.
 
@@
 
-\noindent\textbf{Internal validity:}
+\noindent\textbf{Internal validity:}\\
 One source of internal validity concern is the time mismatch between the
@@
 
-\noindent\textbf{External validity:} 
+\noindent\textbf{External validity:} \\
 While we have used a data set with high quality standards~\cite{msr17challenge},
@@
 
-\noindent\textbf{Construct validity:}
+\noindent\textbf{Construct validity:}\\
 While we believe the build status is a good metric for contribution success,
-there is the chance that a problem in the projects's test cases, and no the
-contribution itself, led to the build failure.
+there is the chance that a problem in the project's test cases, and not the
+contribution itself, led to the build failure.  There are also other possible
+technical and social factors which were not explored in this study.  Future
+research will be required to determine if those factors are important.
 
@@
 than core contributors.  This leads us to believe that non-core contributions
-are not inspected as closely as they should be.
+are not inspected as closely as they should be.  We have also found that having
+a follower, and especially a large follower base, can be an indicator of build
+integration success.
 

### 2017-02-18 Paper/MSRChallenge2017.tex
added a needed citation

@@
 successful builds were randomly selected until the number of successful builds
-equaled the number of not successful builds (downsampled).  We used both the
+equaled the number of not successful builds (downsampled\todo{citation needed}).  We used both the
 downsampled and non-downsampled data sets in our results.

### 2017-02-18 Paper/MSRChallenge2017.tex
minor change
forgot to update the introduction

@@
 that core team members are more likely to achieve build success than non-core
-team members.
+team members and having followers increases the likelihood passing the
+continuous integration build.
 
@@
 Developers with over 1000 followers had more than a 10\% increase compared to
-developers with no followers.  This shows that high-quality developers are more
+developers with no followers.  This shows that higher quality developers are more
 likely to have a large number of followers.

### 2017-02-18 Paper/MSRChallenge2017.tex
removed repeat word

@@
 factors and pull request acceptance. We are interested in understanding if
-social factors, that proxy experience, can be used to predict a
+social factors, that proxy experience, can be used to predict
 a different success measure: continuous integration success.

### 2017-02-18 Paper/MSRChallenge2017.tex
minor revisions

@@
 
-To collect the social data, we created a web crawler to extract the social data
+To collect the social data, we created a web scrapper to extract the social data
 from developer's profiles.
 We used the commit hash and the project name in the original data
-set~\cite{msr17challenge} to locate the webpage of the commit using the syntax
+set~\cite{msr17challenge} to locate the web page of the commit using the syntax
 below. 

### 2017-02-18 Paper/MSRChallenge2017.tex
adjusted the todos

@@
 request. Unlike this previous study, in our study we look at a broader aspect of 
-social aspects and how this attributes towards the success in Travis CI jobs. 
+social aspects and how this attributes towards the success in Travis
+CI\todo{citation needed for Travis CI} jobs. 
 Gousios et al~\cite{gousios14} study the relationship between the area of the 
@@
 successful builds were randomly selected until the number of successful builds
-equaled the number of not successful builds (downsampled\todo{citation needed}).  We used both the
+equaled the number of not successful builds (downsampled\todo{citation needed
+for down sampling}).  We used both the
 downsampled and non-downsampled data sets in our results.

### 2017-02-18 Paper/MSRChallenge2017.tex
after Mau's pass

--- 2017-02-18 Paper/MSRChallenge2017.tex
@@
 \begin{abstract}
-One important aspect of developing open source software is deciding which
-commits to include in the main branch of a project.  
-Recent research has started to explore how the open source community manages
-this question and found that both technical and social factors are factors in 
+Software quality is an important and desirable aspect of the software 
+development process overall, especially with the increasing participation of a very
+diverse pool of developers, the number of commits and pull requests keeps increasing 
+and the mechanisms available to identify which developers are pushing high 
+quality commits and pull requests is scarce.
+Recent research has explored how the open source community manages
+this question finding that both technical and social factors are factors in 
 the success of project contributions on GitHub.  
@@
 contribution that gets
-accepted to the project.  However, with the continuous integration, we can
+accepted to the project. However, with continuous integration, we can
 explore this question a step further.  We can better estimate the success of a
-contribution by investigating if the contribution passed the project's
-test cases.  We performed an initial investigation into the technical and
+contribution by investigating if the contribution passed all the quality standards set 
+by the repository owners.  We performed an initial investigation into the technical and
 social factors involved in a commit that successfully passes the integration
@@
 or contributing a large number of commits) improve predictions of build
-success.  We have found that while social factors cause an noticeable increase
+success.  We have found that while social factors cause a noticeable increase
 in predictive power (12\%), further investigation into these factors are
@@
 in the decision~\cite{Scacchi07}.  However, to better understand successful 
-project contributions, we must analyze factors which are common to all commits.
+project contributions, we must take into consideration and analyze 
+different social attributes from the developers creating the commits,
+which can be great predictors for the success of a contribution.
 
@@
 community has developed various techniques to vet project contributions, such as pull
-requests which must be approved by a core team member~\cite{gousios14}. One such
-technique is continuous integration. Continuous integration automatically checks
+requests which must be approved by a core team member~\cite{gousios14}. 
+These kinds of mechanisms benefit in substancial part by knowing into which 
+aspects to look for as predictors of the quality of the contribution being made.
+
+In this study we analyze a large set of technical and social attributes 
+and how these can be used to
+add certainty to the probability of a contribution being successful or not. 
+Our corpus is based on the entries of a large number of open source projects
+using continuous integration. Continuous integration automatically checks
 the contribution against the project's test cases, to notify the development
-team if the change caused a test case failure~\cite{Meyer14}.  When a change
-passes one of these vetting techniques, it shows that the project developers
-have confidence in the changes.
+team if the change caused a test case failure~\cite{Meyer14}. The
+projects using continuous integration provide quality standard barriers such as
+test cases which will cause the build to break if the commit does not perform
+accordingly to the standards. When a change
+passes these vetting techniques, it shows that the project developers
+have confidence in the changes, therefore, allowing us to analyze the success
+of the contributions made by passing the quality standards created by the 
+core developers of each project.
 
 In past studies, both technical factors and social factors have been found to be
-important when when predicting pull request success~\cite{tsay14icse,tsay14fse}.
-Yet, these factors may not be as important during continuous integration.
-Specifically, we want to investigate if social factors, which can be used a
-proxy for experience, are important when predicting build success when grouped
-with technical data, used as a proxy for commit complexity.
+important when predicting pull request success~\cite{tsay14icse,tsay14fse}.
+In this study we are interested in analyzing the quality of a contribution 
+at a lower granulairity level, commit level. We will analyze this in the 
+context of continuous integration, using some of the social attributes provided
+by Github as a proxy for the developer's experience level and familiarity with
+the process, and their importance when grouped with technical attributes of the commit as 
+confounds for the complexity of the commit being pushed.
 
@@
 request. Unlike this previous study, in our study we look at a broader aspect of 
-social aspects and how this attributes towards the success in Travis CI jobs. 
+social aspects and how this attributes towards the success in Travis
+CI jobs.\footnote{https://docs.travis-ci.com/user/customizing-the-build} 
 Gousios et al~\cite{gousios14} study the relationship between the area of the 
@@
 Our study shows that social factors are an important aspect of build success but
-these factors alone do not fully predict if a build will succeed.  We also show
+these factors alone do not fully predict if a contribution will be successfully integrated into the project. We also show
 that core team members are more likely to achieve build success than non-core
@@
 The goal of this study is to have a deeper understanding of the relationship 
-between the several different social properties that that estimate the
+between the several different social properties that estimate the
 developer's experience, and the likelihood of a developer's commit
-to be considered a successfully integrated in the project. We define successful
+to be considered successfully integrated in the project. We define successful
 integration as passing the continuous integration build tests in the project.
@@
 factors and pull request acceptance. We are interested in understanding if
-social factors, that proxy experience, can be used to predict
-a different success measure: continuous integration success.
+social factors, used as a proxy for experience, can be used to predict
+a different success measure: commit integration success, therefore giving
+developers and integrators another tool to be able to identify the quality
+of a contribution performed by a particular developer.
 
@@
 \subsection{Metric}
-We created a linear regression model based on two different sets of data. Merely 
+We created a decision tree based on two different sets of data. Merely 
 technical data related to technical aspects of the complexity of the commit, and 
@@
 \label{approach}
-To investigate our research questions, we built a dataset based on the 
-attributes that consisted of both technical and social factors.  We collected
-the technical factors from the provided data set~\cite{msr17challenge}.
+To investigate our research questions, we built a data set based on the 
+attributes that consisted of both technical and social factors. For the technical factors, we collected
+these from the data set provided by the MSR Challenge~\cite{msr17challenge}.
 We extracted only the attributes in the data set that proxy the commit's
-complexity and the build status.
+complexity and the build status as listed below:
 \begin{itemize}
@@
 
-Once we had these attributes, we removed repeated rows \todo{Why did we have to
-remove repeated rows?}
-
-To collect the social data, we created a web scrapper to extract the social data
-from developer's profiles.
-We used the commit hash and the project name in the original data
-set~\cite{msr17challenge} to locate the web page of the commit using the syntax
-below. 
-\newline \newline
-\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
-\newline \newline
-Then, we scraped the commit author's
-\textit{username} from the page. If the scrapper was able to find username, the
-scraper went to the user's profile information using the syntax below.
-\newline \newline
-\textit{https://github.com/\textbf{UserName}}
-\newline \newline
-The scrapper then extracted the following items from the user's profile.
-\begin{itemize}
-\item Repositories
-\item Stars
-\item Followers
-\item Following
-\item Contributions 
-\end{itemize}
-
-Repositories represents the repositories the developer has access to. This 
-includes where the developer is the repository owner,where the developer is a 
-collaborator, and repositories that the developer can access through an 
-organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
-represents a count of the projects the developer has stared. Starring  a project
-means to showing approval of the repository and creating a bookmark for later 
-access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
-Following detail the number of developers that are following and being followed 
-by the developer in question. Finally, the last attribute studied is the number 
-of contributions made by the developer in the last year.
-
-We also added one item from the original data set to the social factors:
-gh\_by\_core\_team\_member.
-This factor indicates if the developer making a contribution is a core member 
-of that project.
-
-We used this data to create two data sets.  One with only the technical
-factors and the build status, and another with both the technical and social
-factors along with the build status.
-
-The dataset used in this study~\cite{msr17challenge} is very diverse 
-and consists of commits that date from far back, and the social data we are 
-gathering is recent data, gathered in January 2017. The researchers of this 
-project acknowledge this discrepancy and in an effort to mitigate the threat of
-using future result to predict previous events,
-we removed the commits in the dataset that were not performed within the last
-three years of the data set's release (2014,2015,2016).  While this is not
-perfect, we believe that these numbers are unlikely to have changed
-significantly in the last three years.
-
-After building the data set, we converted the various Travis build statuses to
-successful (passed in the data set) or not successful (errored, failed, canceled
-and started in the data set).  This still left a big discrepancy in the two
-categories, with about a 3:1 successful to not successful ratio. To avoid having
-this discrepancy alter our results, we created a separate data set where the
-successful builds were randomly selected until the number of successful builds
-equaled the number of not successful builds (downsampled\todo{citation needed}).  We used both the
-downsampled and non-downsampled data sets in our results.
-
-\section{Evaluation}
-
-We evaluated the predictive power of the social factors using a decision
-tree~\cite{Quinlan86}.
-Decision trees are a predictive model which uses binary decisions on the
-attributes to predict a final class.  The predicted class is represented as the
-leaves, while the attribute decisions used in the prediction cause the
-different branches.
-In this study, we used the Weka~\cite{Weka} J48~\cite{Quinlan1993} decision tree
-with default settings. The decision trees were evaluated using ten fold cross 
-validation with the data in each data set.
-
-\section{Results}
-
-\subsection{Success Classification}
 \begin{table*}[ht]
@@
   \caption{ Second and third columns: Comparison of performance when running 10 fold cross validation of two decision trees.
-The first column after the first double bar uses only technical attributes to predict the Travis Job status, the second column augments the dataset with social attributes.
-Fourth and fifth columns: The same intuition as the previous two, with the difference that the dataset was downsampled to provide the same number of successful and unsuccessful instances }
+The first column after the first double bar uses only technical attributes to predict the Travis Job status, the second column augments the data set with social attributes.
+Fourth and fifth columns: The same intuition as the previous two, with the difference that the data set was downsampled to provide the same number of successful and unsuccessful instances }
   \label{resultsTable}
 \end{table*}
+
+As a result of extracting just these particular technical attributes, the new data set is conformed by a  big number of repeated rows, which would slow down the process of collecting the social data for each of these rows, therefore, at this point we removed the repeated rows and continued to collect the social attributes from the developers who pushed the commits.
+
+To collect the social data, we created a web scrapper to extract the social data
+from developer's profiles.
+We used the commit hash and the project name in the original data
+set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page of the commit using the syntax
+below. 
+\newline \newline
+\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
+\newline \newline
+
+Then, we scraped the commit author's
+\textit{username} from the page. If the scrapper was able to find username, the
+scraper went to the user's profile information using the syntax below.
+\newline \newline
+\textit{https://github.com/\textbf{UserName}}
+\newline \newline
+The scrapper then extracted the following items from the user's profile.
+\begin{itemize}
+\item Repositories
+\item Stars
+\item Followers
+\item Following
+\item Contributions in the last year
+\end{itemize}
+
+Repositories represents the repositories the developer has access to. This 
+includes where the developer is the repository owner,where the developer is a 
+collaborator, and repositories that the developer can access through an 
+organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
+represents a count of the projects the developer has stared. Starring  a project
+means to showing approval of the repository and creating a bookmark for later 
+access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
+Following detail the number of developers that are following and being followed 
+by the developer in question. Finally, the last attribute studied is the number 
+of contributions made by the developer in the last year.
+
+We also added one item from the original data set to the social factors:
+gh\_by\_core\_team\_member.
+This factor indicates if the developer making a contribution is a core member 
+of that project.
+
+We used this data to create two data sets.  One with only the technical
+factors and the build status, and another with both the technical and social
+factors along with the build status.
+
+The data set used in this study~\cite{msr17challenge} is very diverse 
+and consists of commits that date from far back, and the social data we are 
+gathering is recent data, gathered in January 2017. The researchers of this 
+project acknowledge this discrepancy and in an effort to mitigate the threat of
+using future result to predict previous events,
+we removed the commits in the data set that were not performed within the last
+three years of the data set's release (2014,2015,2016).  While this is not
+perfect, we believe that these numbers are unlikely to have changed
+significantly in the last three years.
+
+After building the data set, we converted the various Travis build statuses to
+successful (passed in the data set) or not successful (errored, failed, canceled
+and started in the data set).  This still left a big discrepancy in the two
+categories, with about a 3:1 successful to not successful ratio. To avoid having
+this discrepancy alter our results, we created a separate data set where the
+successful builds were randomly selected until the number of successful builds
+equaled the number of not successful builds (downsampling process).  We used both the
+downsampled and non-downsampled data sets in our results.
+
+\section{Evaluation}
+
+We evaluated the predictive power of the social factors using a decision
+tree~\cite{Quinlan86}.
+Decision trees are a predictive model which uses binary decisions on the
+attributes to predict a final class.  The predicted class is represented as the
+leaves, while the attribute decisions used in the prediction cause the
+different branches.
+In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
+with default settings. The decision trees were evaluated using ten fold cross 
+validation with the data in each data set.
+
+\section{Results}
+
+\subsection{Success Classification}
 
@@
 Table~\ref{resultsTable} shows the results of running the two data sets through the
-default Weka J48 decision tree algorithm.The decision tree built from
+default Weka J48 decision tree algorithm. The decision tree built from
 only the technical indicators has a correct classification rate of 77.01\% which
@@
 \section{Discussion}
-We have found that social attributes which proxy experience produce a small but
-noticeable increase in predicting build success.  While the increase was very
-small with the full data set, there was a greater increase in prediction
-accuracy after performing downsampling.  These results show that experience is
-important to predicting build commit success but a strong predictor.
+We have found that social attributes which proxy experience produce a 
+noticeable increase in predicting build success.  While the increase was noticeable 
+with the full data set, there was a much greater increase in prediction
+accuracy after performing downsampling. These results show that social factors
+as the ones studied in this paper are important predictors when
+evaluating the predictive power of build commit success.
 
@@
 more likely to have the build integration pass than non-core team members.  This
-result provides evidence that non-core team member commit are not throughly
+result provides evidence that non-core team member commit are not thoroughly
 scrutinized, although further studied will be required to draw definite
@@
 \section{Threats to validity}
-This study contains various threats to validity.
+\noindent\textbf{Internal validity:}\\
+The researchers in this study used the dataset provided by the 
+ MSRChallenge~\cite{msr17challenge} to gain useful information regarding the 
+ behavior of developers when pushing commits and how well these commits integrate 
+ successfully with the project. The authors have used 
+ Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for 
+ usage of machine learning algorithms to analyze our datasets. We are aware that, 
+ as every human written tool, Weka is prone to contain errors and/or bugs; 
+ nonetheless, Weka is a broadly used, open source tool that is subject to high 
+ quality standards and a vast user and developer base which makes it more likely 
+ to be a high quality code and to have less bugs than lesser used tools.
 
-\noindent\textbf{Internal validity:}\\
-One source of internal validity concern is the time mismatch between the
-technical and social data.  We restricted the commits to only the commits in the
-last three years of the data set to reduce this concern.
-There is also a chance that scripts we used to create the data sets contain an
-error.  For full transparency, we've released the scripts used to collect the
-data set at (This will be added after the anonymous review).
-
-%footnote{https://goo.gl/CqTX44}
+ The scripts we have created to adapt and extract the datasets we needed, and the 
+ scripts to obtain the developer social data are publicly available to facilitate 
+ the transparency and quality of the process(Will be made available after double blind review).%\footnote{https://goo.gl/CqTX44}
 
 \noindent\textbf{External validity:} \\
-While we have used a data set with high quality standards~\cite{msr17challenge},
-these results may not generalized to non-open source projects.
+ To tackle the concern that the results of this study might not generalize to 
+ other instances outside of the studied cases, we have used a broad and rich 
+ dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
+ projects used in this dataset have also been filtered to be popular (having more 
+ than 10 watches on Github), and to have a history of using the continuous 
+ integration tool Travis CI for more than 50 builds. All these features help to 
+ build the notion that since we are building our analysis on top of a vast 
+ dataset comprehending a wide diversity of projects, the threat of this analysis 
+ not generalizing to other projects is mitigated.
 
 \noindent\textbf{Construct validity:}\\
-While we believe the build status is a good metric for contribution success,
-there is the chance that a problem in the project's test cases, and not the
-contribution itself, led to the build failure.  There are also other possible
-technical and social factors which were not explored in this study.  Future
-research will be required to determine if those factors are important.
+The authors understand that 
+ Travis job success is not the only way to analyze the success of a commit, and 
+ that for different reasons the job may not be successful even if the code 
+ commited does not have flaws (a flacky test case for example). Since continuous 
+ integration is a best known practice in industry and the use of this methodology 
+ spreads out into the open source community, we consider that cases of misuse of 
+ CI such that it will lead to failing travis jobs when they should have actually 
+ be successful are minimum, specially since having a solid build is one of the 
+ main purposes of the methodology, and taking into account that the projects in 
+ out dataset are projects with a history of using continuous integration and 
+ having a certain level of popularity, this threat is minimized. We therefore 
+ consider Travis job success to be a proxy 
+ for success when integrating a commit into a larger project.
 
 \section{Conclusion}
-In this study we have analyzed the ability to use social factors to predict
-build integration success.
-Our results show that adding social data, which proxies experience, provides a
-small increases in prediction accuracy.  This leads us to conclude that while
-experience is important, it is not the only factor in build success.
+In this study we have analyzed the probability of Travis job success as being predicted by two different categories of attributes: Technical and Social data.
+We gathered the attributes that describe complexity of each commit being pushed and have created a decision tree that predicts if a future pushed commit will be successfully integrated into its corresponding build or not.
+Afterwards, we have gathered social attributes from the developers who pushed each of these commits
+and we have augmented our dataset with these attributes to understand whether adding social information about the developer would help the decision tree predict with higher accuracy future 
+instances.
+
+Our results show that adding social data to the construction of the decision tree increases the probability this correctly predicting future commit's success in integrating into their corresponding projects by a margin of 4.09\% to 11.99\%, depending on the ratio of successful vs unsuccessful instances are used to train the desicion tree.
+
 We have also found that non-core contributors cause not successful builds more

### 2017-02-19 Paper/MSRChallenge2017.tex

@@
   {{\scriptsize \textbf{\color{red} {#1}}}}
+\newcommand{\clg}[1]
+  {{\scriptsize \textbf{\color{blue} {CLG says: #1}}}}
 
@@
 \section{Introduction}
+\clg{detail nitpick: ``et al.'' has a paragraph after the al. (and not the et).
+  This is something I write about in the blog post you all claim to have read.
+  Please fix it throughout.}
+
 For managers of an open source project, it is important to ensure that the
@@
 \section{Research Design}
+
 We present the approach taken to guide this study by
@@
 
-\subsection{Goal}
-The goal of this study is to have a deeper understanding of the relationship 
+\paragraph{Goal}
+The goal of this study is to identify and understand relationships 
 between the several different social properties that estimate the
@@
 integration as passing the continuous integration build tests in the project.
+\clg{I might recommend a paragraph at the top of this section defining at a high
+  level the key terms, like ``technical elements'' versus ``social factors.''
+  You do concretize them in the next section, but conceptually here they're a
+  little bit UBD.}
 
-\subsection{Question}
-
+\paragraph{Question}
 Previous studies have identified a relationship between technical and social 
@@
 
-\subsection{Metric}
+\paragraph{Metric}
+\clg{I think I need a little bit more detail here, at multiple levels (like, why
+  a decision tree? among other questions.}
 We created a decision tree based on two different sets of data. Merely 
@@
 \label{approach}
+
+\clg{Perhaps it makes sense to break this down into subsections?}
+
 To investigate our research questions, we built a data set based on the 
@@
 We extracted only the attributes in the data set that proxy the commit's
-complexity and the build status as listed below:
+complexity and the build status as listed below:\clg{The listed terms don't mean
+  anything on their own; they're clearly grabbed from code.  Please rename them
+  to something descriptive (in English) and give a quick definition of each.
+  Even better is if you give some insight as to why they might be meaningful in
+  your theory (or not).}
 \begin{itemize}
@@
 \end{itemize}
+
+As a result of extracting just these particular technical attributes, the new
+data set is conformed by a  big number of repeated rows, which would slow down
+the process of collecting the social data for each of these rows, therefore, at
+this point we removed the repeated rows and continued to collect the social
+attributes from the developers who pushed the commits.\clg{I'm afraid this
+  sentence/paragraph isn't parsing for me.  Please rephrase, clarify, expand,
+  and add precision.  Also break into multiple sentences, because it's really
+  really long, which doesn't help.  To start, I think the word ``conformed'' is
+  not what you mean.}
+
+To collect the social data, we created a web scraper to extract the social data
+from developer's profiles.
+We used the commit hash and the project name in the original data
+set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
+of the commit, leveraging \textit{github.com}'s URL standard for projects and
+commit hashes.
+%  using the syntax
+% below. 
+% \newline \newline
+% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
+% \newline \newline
+
+We scraped the commit author's
+\textit{username} from a commit page. If the scrapper\clg{you mean ``scraper''
+  not ``scrapper''; I fixed it once but you should fix it everywhere else.} was able to find username, the
+scraper went to the user's profile information
+(\textit{https://github.com/\textbf{UserName}}).
+
+The scrapper then extracted the following items from the user's
+profile.\clg{slightly better than the above for technical factors because you do
+  define them in the text below but I think integrating into the itemized list
+  would be better.  Also, what does each of these mean?}
+\begin{itemize}
+\item Repositories
+\item Stars
+\item Followers
+\item Following
+\item Contributions in the last year
+\end{itemize}
+
+Repositories represents the repositories the developer has access to. This 
+includes where the developer is the repository owner,where the developer is a 
+collaborator, and repositories that the developer can access through an 
+organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
+represents a count of the projects the developer has stared. Starring  a project
+means to showing approval of the repository and creating a bookmark for later 
+access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
+Following detail the number of developers that are following and being followed 
+by the developer in question. Finally, the last attribute studied is the number 
+of contributions made by the developer in the last year.
+
+We also added one item from the original\clg{...what?} data set to the social factors:
+gh\_by\_core\_team\_member.
+This factor indicates if the developer making a contribution is a core member 
+of that project.
+
+We used this data to create two data sets.  One with only the technical
+factors and the build status, and another with both the technical and social
+factors along with the build status.\clg{This is not a complete
+  sentence.}\clg{also: why do you build two data sets?}
+
+The data set used in this study~\cite{msr17challenge} is very diverse 
+and consists of commits that date from far back. The social data we 
+gather is recent, gathered in January 2017. In an effort to mitigate the threat of
+using future result to predict previous events,
+we removed the commits in the data set that were not performed within the last
+three years of the data set's release (2014,2015,2016).  While this is not
+perfect, we believe that these numbers are unlikely to have changed
+significantly in the last three years.\clg{...did you spot check?}
+
+After building the data set, we converted the\clg{which?} various Travis build statuses to
+successful (passed in the\clg{which?} data set) or not successful (errored, failed, canceled
+and started in the data set).  This still left a big discrepancy in the two
+categories, with about a 3:1 successful to not successful ratio.\clg{I think I'm
+  having ah ard time here because it's not clear which dataset we're referring
+  to, but I don't understand the previous sentence, and thus don't understand
+  the next sentence.} To avoid having
+this discrepancy alter our results, we created a separate data set where the
+successful builds were randomly selected until the number of successful builds
+equaled the number of not successful builds (downsampling process).\clg{How?}  We used both the
+downsampled and non-downsampled data sets in our results.\clg{Why?}
+
+\section{Evaluation}
 
@@
 \center
-  \caption{ Second and third columns: Comparison of performance when running 10 fold cross validation of two decision trees.
-The first column after the first double bar uses only technical attributes to predict the Travis Job status, the second column augments the data set with social attributes.
-Fourth and fifth columns: The same intuition as the previous two, with the difference that the data set was downsampled to provide the same number of successful and unsuccessful instances }
-  \label{resultsTable}
+  \caption{ Second and third columns: Comparison of performance when running 10
+    fold cross validation\clg{We've discussed this phrasing surrounding 10-fold cross
+      validation.  Please fix.  What is the metric here?  How do I interpret
+      these numbers?} of two decision trees. The first column after
+    the first double bar uses only technical attributes to predict the Travis
+    Job status, the second column augments the data set with social
+    attributes. Fourth and fifth columns: \clg{this sentence is not a
+      sentence/is a bit awkward.} The same intuition as the previous
+    two, with the difference that the data set was downsampled to provide the
+    same number of successful and unsuccessful instances.\clg{...and what is the
+    takeaway from this table?} \clg{Small thing: labels should be inside the
+    caption otherwise the numbers sometimes get confused.  It's a stupid latex thing.}  \label{resultsTable}} 
 \end{table*}
-
-As a result of extracting just these particular technical attributes, the new data set is conformed by a  big number of repeated rows, which would slow down the process of collecting the social data for each of these rows, therefore, at this point we removed the repeated rows and continued to collect the social attributes from the developers who pushed the commits.
-
-To collect the social data, we created a web scrapper to extract the social data
-from developer's profiles.
-We used the commit hash and the project name in the original data
-set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page of the commit using the syntax
-below. 
-\newline \newline
-\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
-\newline \newline
-
-Then, we scraped the commit author's
-\textit{username} from the page. If the scrapper was able to find username, the
-scraper went to the user's profile information using the syntax below.
-\newline \newline
-\textit{https://github.com/\textbf{UserName}}
-\newline \newline
-The scrapper then extracted the following items from the user's profile.
-\begin{itemize}
-\item Repositories
-\item Stars
-\item Followers
-\item Following
-\item Contributions in the last year
-\end{itemize}
-
-Repositories represents the repositories the developer has access to. This 
-includes where the developer is the repository owner,where the developer is a 
-collaborator, and repositories that the developer can access through an 
-organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
-represents a count of the projects the developer has stared. Starring  a project
-means to showing approval of the repository and creating a bookmark for later 
-access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
-Following detail the number of developers that are following and being followed 
-by the developer in question. Finally, the last attribute studied is the number 
-of contributions made by the developer in the last year.
-
-We also added one item from the original data set to the social factors:
-gh\_by\_core\_team\_member.
-This factor indicates if the developer making a contribution is a core member 
-of that project.
-
-We used this data to create two data sets.  One with only the technical
-factors and the build status, and another with both the technical and social
-factors along with the build status.
-
-The data set used in this study~\cite{msr17challenge} is very diverse 
-and consists of commits that date from far back, and the social data we are 
-gathering is recent data, gathered in January 2017. The researchers of this 
-project acknowledge this discrepancy and in an effort to mitigate the threat of
-using future result to predict previous events,
-we removed the commits in the data set that were not performed within the last
-three years of the data set's release (2014,2015,2016).  While this is not
-perfect, we believe that these numbers are unlikely to have changed
-significantly in the last three years.
-
-After building the data set, we converted the various Travis build statuses to
-successful (passed in the data set) or not successful (errored, failed, canceled
-and started in the data set).  This still left a big discrepancy in the two
-categories, with about a 3:1 successful to not successful ratio. To avoid having
-this discrepancy alter our results, we created a separate data set where the
-successful builds were randomly selected until the number of successful builds
-equaled the number of not successful builds (downsampling process).  We used both the
-downsampled and non-downsampled data sets in our results.
-
-\section{Evaluation}
 
@@
 
-\section{Results}
+\clg{I killed the separation between ``evaluation'' and ``results'' because I
+  don't know why it existed in the first place.}
+\clg{I also wouldn't mind an enumeration of research questions; the stuff in
+  design (section 2) is high level and it's not obvious where you're going to go
+  at this juncture.}
 
@@
 successful.  This means that a classifier which guesses successful every time
-would produce a classification rate of 74.43\% if ran on the full data set.
+would produce a classification rate of 74.43\% if ran on the full data
+set. \clg{This sentence migth be better place above, when you first discuss subsampling.}
 
@@
 Adding the social data increased the classifier's accuracy from 77.01\% to
-81.10\%, about a 4\% increase.
+81.10\%, about a 4\% increase.\clg{It's not clear from this text that you're
+  talking about the unsampled data.}
 
@@
 
+\clg{...upshot? Also: there are various numbers in the Table that aren't
+  discussed or explained either in the caption or in these results, like, what's
+  a Kappa statistic, and what do we learn from them?}
+
 \subsection{Build success by core team member}
 
-For the build success investigation, we classified the build success rate for
+For the build success investigation,\clg{Is this a different investigation than
+  the previous subsection?}  we classified the build success rate for
 core team members and non-core team members.  We found that core team members
 triggered of 89.39\% of the builds in the data set and 75.58\% of those builds
-passed.  Non-core team members triggered 10.61\% of the builds in the data set
+passed.  Non-core team members triggered 10.61\% of the builds in the\clg{which?} data set
 and 64.70\% of the builds passed.
+
+\clg{upshot?}
 
@@
 
-\section{Discussion}
-We have found that social attributes which proxy experience produce a 
+\clg{upshot?}
+
+\subsection{Discussion}
+
+Overall, we have found that social attributes which proxy experience produce a 
 noticeable increase in predicting build success.  While the increase was noticeable 
@@
 accuracy after performing downsampling. These results show that social factors
-as the ones studied in this paper are important predictors when
+as the ones studied in this paper are important\clg{...maybe a strong word?} predictors when
 evaluating the predictive power of build commit success.
@@
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
+\clg{connection back to theory?}
 
 \section{Threats to validity}
-\noindent\textbf{Internal validity:}\\
+
+\paragraph{Internal validity:}
 The researchers in this study used the dataset provided by the 
@@
 
-\noindent\textbf{External validity:} \\
+\paragraph{External validity:} 
  To tackle the concern that the results of this study might not generalize to 
@@
 
-\noindent\textbf{Construct validity:}\\
-The authors understand that 
+\paragraph{Construct validity:}
  Travis job success is not the only way to analyze the success of a commit, and 
@@
 
+\clg{per my email: fix the bibliography. Now.}
+
 \bibliographystyle{plain}

### 2017-02-19 Paper/MSRChallenge2017.tex
Addressed most of Claire's todo's

@@
 \section{Introduction}
-\clg{detail nitpick: ``et al.'' has a paragraph after the al. (and not the et).
-  This is something I write about in the blog post you all claim to have read.
-  Please fix it throughout.}
-
 For managers of an open source project, it is important to ensure that the
@@
 gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
-Tsay et al~\cite{tsay14icse} performed a very relevant study where they 
+Tsay et al.~\cite{tsay14icse} performed a very relevant study where they 
 determine that the social connection between the developer who is asking the 
@@
 CI jobs.\footnote{https://docs.travis-ci.com/user/customizing-the-build} 
-Gousios et al~\cite{gousios14} study the relationship between the area of the 
+Gousios et al.~\cite{gousios14} study the relationship between the area of the 
 source code being modified by the developer requesting the changes to be pulled 
@@
 al~\cite{bettenburgh10} discuss the impact of social interactions with 
-post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different 
+post-release defects, Vasilescu et al.~\cite{vasilescu14} explored how different 
 project characteristics (programming language, project age, etc.) affect commit 
-success when integrated to the automatic build process. Yu et al~\cite{yu16} 
+success when integrated to the automatic build process. Yu et al.~\cite{yu16} 
 analyze the impact of CI usage in Github and its correlation with software 
@@
 \paragraph{Goal}
-The goal of this study is to identify and understand relationships 
+The goal of this study is to identify and understand the relationship 
 between the several different social properties that estimate the
-developer's experience, and the likelihood of a developer's commit
+developer's experience such as contributions in the last year, repositories participated, stars, etc., technical properties, such as files added and modified, and the likelihood of a developer's commit
 to be considered successfully integrated in the project. We define successful
 integration as passing the continuous integration build tests in the project.
-\clg{I might recommend a paragraph at the top of this section defining at a high
-  level the key terms, like ``technical elements'' versus ``social factors.''
-  You do concretize them in the next section, but conceptually here they're a
-  little bit UBD.}
 
@@
 Therefore our main research question is presented as follows:
-\newline \newline
+
 \textbf{Do social attributes, gathered 
@@
 allow for more accurate predictions than only using technical data?}
-\newline \newline
 
@@
 
-\clg{Perhaps it makes sense to break this down into subsections?}
+To investigate our research questions, we built a data set based on the 
+attributes that consisted of both technical and social factors.
 
-To investigate our research questions, we built a data set based on the 
-attributes that consisted of both technical and social factors. For the technical factors, we collected
+\textbf{Technical Factors:} For the technical factors, we collected
 these from the data set provided by the MSR Challenge~\cite{msr17challenge}.
 We extracted only the attributes in the data set that proxy the commit's
-complexity and the build status as listed below:\clg{The listed terms don't mean
-  anything on their own; they're clearly grabbed from code.  Please rename them
-  to something descriptive (in English) and give a quick definition of each.
-  Even better is if you give some insight as to why they might be meaningful in
-  your theory (or not).}
-\begin{itemize}
+complexity such as the size of the changes being performed as listed below:\begin{itemize}
 %\item tr\_original\_commit
 %\item gh\_build\_started\_at 
-\item git\_diff\_src\_churn 
-\item gh\_diff\_files\_added 
-\item gh\_diff\_files\_deleted 
-\item gh\_diff\_files\_modified 
-\item gh\_diff\_tests\_added 
-\item gh\_diff\_tests\_deleted 
-\item gh\_diff\_src\_files 
-\item gh\_sloc 
-\item tr\_status 
+\item Source churn: How many lines of code were changed by the new commit in this build.
+\item Files added: How many files were added by this commit.
+\item Files deleted: How many files were deleted by this commit.
+\item Files modified: How many files were modified by this commit.
+\item Tests added: How many tests were added by this commit.
+\item Tests deleted: How many tests were deleted by this commit.
+\item Source files: Number of files in the new commits. 
+\item Source loc: Number of executable source lines of code, in the entire repository.
+\item Travis status: Status of the travis build.
 \end{itemize}
 
-As a result of extracting just these particular technical attributes, the new
-data set is conformed by a  big number of repeated rows, which would slow down
-the process of collecting the social data for each of these rows, therefore, at
-this point we removed the repeated rows and continued to collect the social
-attributes from the developers who pushed the commits.\clg{I'm afraid this
-  sentence/paragraph isn't parsing for me.  Please rephrase, clarify, expand,
-  and add precision.  Also break into multiple sentences, because it's really
-  really long, which doesn't help.  To start, I think the word ``conformed'' is
-  not what you mean.}
-
-To collect the social data, we created a web scraper to extract the social data
+\textbf{Social Factors:} To collect the social data, we created a web scraper to extract the social data
 from developer's profiles.
@@
 We scraped the commit author's
-\textit{username} from a commit page. If the scrapper\clg{you mean ``scraper''
-  not ``scrapper''; I fixed it once but you should fix it everywhere else.} was able to find username, the
+\textit{username} from a commit page. If the scraper was able to find username, the
 scraper went to the user's profile information
@@
 
-The scrapper then extracted the following items from the user's
-profile.\clg{slightly better than the above for technical factors because you do
-  define them in the text below but I think integrating into the itemized list
-  would be better.  Also, what does each of these mean?}
+The scraper then extracted the following items from the user's
+profile.
+
 \begin{itemize}
-\item Repositories
-\item Stars
-\item Followers
-\item Following
-\item Contributions in the last year
+\item Repositories: the repositories the developer has access to. This 
+includes where the developer is the repository owner,where the developer is a 
+collaborator, and repositories that the developer can access through an 
+organization membership.\footnote{https://developer.github.com/v3/repos/}
+\item Stars: a count of the projects the developer has stared. Starring  a project
+means to showing approval of the repository and creating a bookmark for later 
+access.\footnote{https://help.github.com/articles/about-stars/}
+\item Followers: number of developers that that are following the author. 
+\item Following: number of developers that that are being followed by the author.
+\item Contributions in the last year: Number of contributions made by the author in the last year.
 \end{itemize}
 
-Repositories represents the repositories the developer has access to. This 
-includes where the developer is the repository owner,where the developer is a 
-collaborator, and repositories that the developer can access through an 
-organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
-represents a count of the projects the developer has stared. Starring  a project
-means to showing approval of the repository and creating a bookmark for later 
-access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
-Following detail the number of developers that are following and being followed 
-by the developer in question. Finally, the last attribute studied is the number 
-of contributions made by the developer in the last year.
-
-We also added one item from the original\clg{...what?} data set to the social factors:
+We also added one item from the original data set provided by the MSR Challenge to the social factors:
 gh\_by\_core\_team\_member.
@@
 
-We used this data to create two data sets.  One with only the technical
+\textbf{Comparing two data sets:} We used the social data gathered to create two data sets: one with only the technical
 factors and the build status, and another with both the technical and social
-factors along with the build status.\clg{This is not a complete
-  sentence.}\clg{also: why do you build two data sets?}
+factors, this is to be able to compare how well can the job status be predicted by just technical data, and adding social data.
 
@@
 perfect, we believe that these numbers are unlikely to have changed
-significantly in the last three years.\clg{...did you spot check?}
+significantly in the last three years.\clg{...did you spot check? RESPONSE: Spot check that they did belong to those years? Yeah}
 
-After building the data set, we converted the\clg{which?} various Travis build statuses to
-successful (passed in the\clg{which?} data set) or not successful (errored, failed, canceled
-and started in the data set).  This still left a big discrepancy in the two
-categories, with about a 3:1 successful to not successful ratio.\clg{I think I'm
-  having ah ard time here because it's not clear which dataset we're referring
-  to, but I don't understand the previous sentence, and thus don't understand
-  the next sentence.} To avoid having
-this discrepancy alter our results, we created a separate data set where the
+Since we are interested in the success of the job status of each row, we converted the Travis build statuses to just two possible values,
+successful (passed in the original provided data set) and not successful (errored, failed, canceled
+and started in the original data set). At this point we had a 3:1 successful to not successful ratio in the rows of the data sets.
+
+In the non-downsampled data set, 74.43\% of the builds were successful, the rest were not
+successful.  This means that a classifier which guesses successful every time
+would produce a classification rate of 74.43\% if ran on the full data
+set.
+
+To avoid this and have a 1:1 ratio successful to not successful, we created a separate data set where the
 successful builds were randomly selected until the number of successful builds
 equaled the number of not successful builds (downsampling process).\clg{How?}  We used both the
-downsampled and non-downsampled data sets in our results.\clg{Why?}
+downsampled and non-downsampled data sets in our results to show the difference of the behavior of the decision tree when it is trained with a equal ratio than when it is trained with a non equal ratio.
 
@@
 \begin{tabular}{l||r|r||r|r}
-  & \multicolumn{2}{|c||}{Original number of instances}  & \multicolumn{2}{|c}{Downsampled} \\
+  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
 \hline
@@
 
-\textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\
+%\textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\
 
-\textbf{Mean absolute error}& 0.34 &  0.28 & 0.43 & 0.32\\
+%\textbf{Mean absolute error}& 0.34 &  0.28 & 0.43 & 0.32\\
 
-\textbf{Relative absolute error}& 88.64\% & 72.42\%  & 85.35\% & 63.07\%\\
+%\textbf{Relative absolute error}& 88.64\% & 72.42\%  & 85.35\% & 63.07\%\\
 \hline
@@
 \center
-  \caption{ Second and third columns: Comparison of performance when running 10
-    fold cross validation\clg{We've discussed this phrasing surrounding 10-fold cross
-      validation.  Please fix.  What is the metric here?  How do I interpret
-      these numbers?} of two decision trees. The first column after
-    the first double bar uses only technical attributes to predict the Travis
-    Job status, the second column augments the data set with social
-    attributes. Fourth and fifth columns: \clg{this sentence is not a
-      sentence/is a bit awkward.} The same intuition as the previous
-    two, with the difference that the data set was downsampled to provide the
-    same number of successful and unsuccessful instances.\clg{...and what is the
-    takeaway from this table?} \clg{Small thing: labels should be inside the
-    caption otherwise the numbers sometimes get confused.  It's a stupid latex thing.}  \label{resultsTable}} 
+  \caption{Comparison of predictive power by running 10
+    fold cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column).
+The higher the percentages represent the higher number of instances we are able to correctly predict.
+\label{resultsTable}}
 \end{table*}
@@
 validation with the data in each data set.
-
-\clg{I killed the separation between ``evaluation'' and ``results'' because I
-  don't know why it existed in the first place.}
-\clg{I also wouldn't mind an enumeration of research questions; the stuff in
-  design (section 2) is high level and it's not obvious where you're going to go
-  at this juncture.}
+To give an answer to main research question: ``Do social attributes, gathered 
+from the Github profiles of developers,
+allow for more accurate predictions than only using technical data?", we present the following results:
 
@@
 
-In the original data set, 74.43\% of the builds were successful, the rest were not
-successful.  This means that a classifier which guesses successful every time
-would produce a classification rate of 74.43\% if ran on the full data
-set. \clg{This sentence migth be better place above, when you first discuss subsampling.}
-
 Table~\ref{resultsTable} shows the results of running the two data sets through the
-default Weka J48 decision tree algorithm. The decision tree built from
+default Weka J48 decision tree algorithm, first without downsampling. The decision tree built from
 only the technical indicators has a correct classification rate of 77.01\% which
@@
 Adding the social data increased the classifier's accuracy from 77.01\% to
-81.10\%, about a 4\% increase.\clg{It's not clear from this text that you're
-  talking about the unsampled data.}
+81.10\%, a 4.09\% increase.
 
@@
 in the data set, the classifier correctly predicted 76.09\% of the data set,
-about a 12\% improvement from only the technical data.
-
-\clg{...upshot? Also: there are various numbers in the Table that aren't
-  discussed or explained either in the caption or in these results, like, what's
-  a Kappa statistic, and what do we learn from them?}
+about a 12\% improvement from only the technical data
 
@@
 accuracy after performing downsampling. These results show that social factors
-as the ones studied in this paper are important\clg{...maybe a strong word?} predictors when
+as the ones studied in this paper are significant predictors when
 evaluating the predictive power of build commit success.
@@
 
-\paragraph{Internal validity:}
+\paragraph{Internal validity}
 The researchers in this study used the dataset provided by the 
@@
 
-\paragraph{External validity:} 
+\paragraph{External validity} 
  To tackle the concern that the results of this study might not generalize to 
@@
 
-\paragraph{Construct validity:}
+\paragraph{Construct validity}
  Travis job success is not the only way to analyze the success of a commit, and 
@@
 
-\clg{per my email: fix the bibliography. Now.}
-
 \bibliographystyle{plain}

### 2017-02-19 Paper/MSRChallenge2017.tex
addressed the other comments

@@
 We present the approach taken to guide this study by
-following the Goal-Question-Metric (GQM) methodology descibed by Basili et 
-al~\cite{Basili84}.
+following the Goal-Question-Metric (GQM) methodology described by Basili et 
+al.~\cite{Basili84}.
 
@@
 between the several different social properties that estimate the
-developer's experience such as contributions in the last year, repositories participated, stars, etc., technical properties, such as files added and modified, and the likelihood of a developer's commit
+developer's experience such as contributions in the last year, repositories 
+participated, stars, etc., technical properties, such as files added and 
+modified, and the likelihood of a developer's commit
 to be considered successfully integrated in the project. We define successful
@@
 \begin{comment}
-we have created a dataset with technical attributes to be able to analyze the predictiveness of these attributes and its relationship with commit integration success.
-This way, we are able to create a model
+we have created a dataset with technical attributes to be able to analyze the 
+predictive power of these attributes and its relationship with commit integration 
+success. This way, we are able to create a model
 We are afterwards interested in knowing if adding social attributes to this 
@@
 \paragraph{Metric}
-\clg{I think I need a little bit more detail here, at multiple levels (like, why
-  a decision tree? among other questions.}
-We created a decision tree based on two different sets of data. Merely 
-technical data related to technical aspects of the complexity of the commit, and 
-a superset of this before-mentioned data and social data gathered from the 
-developer who pushed the commit. We evaluate the predictive power of these two 
-models with 10 fold cross validation and we analyze which of them is able to 
-predict with higher accuracy the success of unseen commits.
+Because decision trees are well tested and easy to interpret, we used a decision
+tree classifier to create models which predict build integration success. 
+The first model was generated with only
+the technical factors, that provide insight on the complexity of the commit, 
+to understand how well technical factors predicted build
+success.  We then added the social factors to the technical factors to determine
+the influence of additional social factors on predicting build success.
+We evaluate the predictive power of these two 
+models with 10-fold cross validation and determine the effects of adding social
+factors when predicting build integration success.
 
@@
 
-We also added one item from the original data set provided by the MSR Challenge to the social factors:
+We also added one item from the MSR Challenge data set to the social factors:
 gh\_by\_core\_team\_member.
@@
 
-\textbf{Comparing two data sets:} We used the social data gathered to create two data sets: one with only the technical
+\textbf{Comparing two data sets:} We used the social data gathered to create two data 
+sets: one with only the technical
 factors and the build status, and another with both the technical and social
-factors, this is to be able to compare how well can the job status be predicted by just technical data, and adding social data.
+factors, this is to be able to compare how well can the job status be predicted 
+by just technical data, and adding social data.
 
@@
 perfect, we believe that these numbers are unlikely to have changed
-significantly in the last three years.\clg{...did you spot check? RESPONSE: Spot check that they did belong to those years? Yeah}
+significantly in the last three years.\clg{...did you spot check? Mau's Response: Spot
+check that they did belong to those years? Yeah. Zack's Response: assuming you
+are asking a different question of if the values changed in the last three
+years, than no, we did not check because we weren't sure how.  What should we
+say here?}
 
-Since we are interested in the success of the job status of each row, we converted the Travis build statuses to just two possible values,
-successful (passed in the original provided data set) and not successful (errored, failed, canceled
-and started in the original data set). At this point we had a 3:1 successful to not successful ratio in the rows of the data sets.
+Since we are interested in the success of the job status of each row, we 
+converted the Travis build statuses to just two possible values,
+successful (passed in the original provided data set) and not successful 
+(errored, failed, canceled
+and started in the original data set). At this point we had a 3:1 successful to 
+not successful ratio in the rows of the data sets.
 
@@
 
-To avoid this and have a 1:1 ratio successful to not successful, we created a separate data set where the
-successful builds were randomly selected until the number of successful builds
-equaled the number of not successful builds (downsampling process).\clg{How?}  We used both the
-downsampled and non-downsampled data sets in our results to show the difference of the behavior of the decision tree when it is trained with a equal ratio than when it is trained with a non equal ratio.
+To avoid this and have a 1:1 ratio successful to not successful, we created a 
+separate data set where the
+successful builds were a random sub-sample of successful builds were selected
+such that the number of successful builds equaled the number of failing builds,
+known as downsampling.  We used 
+both the downsampled and non-downsampled data sets in our results to show the 
+difference of the behavior of the decision tree when it is trained with a equal 
+ratio than when it is trained with a non equal ratio.
 
@@
 \center
-  \caption{Comparison of predictive power by running 10
-    fold cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column).
+  \caption{Comparison of predictive power by running 10-fold
+    cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column).
 The higher the percentages represent the higher number of instances we are able to correctly predict.
@@
 In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
-with default settings. The decision trees were evaluated using ten fold cross 
+with default settings. The decision trees were evaluated using 10-fold cross 
 validation with the data in each data set.
@@
 from the Github profiles of developers,
-allow for more accurate predictions than only using technical data?", we present the following results:
+allow for more accurate predictions than only using technical data?", we 
+present the following results:
 
@@
 Table~\ref{resultsTable} shows the results of running the two data sets through the
-default Weka J48 decision tree algorithm, first without downsampling. The decision tree built from
+default Weka J48 decision tree algorithm, first without downsampling. The 
+decision tree built from
 only the technical indicators has a correct classification rate of 77.01\% which
@@
 in the data set, the classifier correctly predicted 76.09\% of the data set,
-about a 12\% improvement from only the technical data
+about a 12\% improvement from only the technical data.  These results show that
+social data can be used to improve predictions of build integration success.
 
@@
 
-For the build success investigation,\clg{Is this a different investigation than
-  the previous subsection?}  we classified the build success rate for
-core team members and non-core team members.  We found that core team members
+To determine if core team member's have greater build success rates,
+we classified the build success rate for
+core team members and non-core team members in the data set without 
+downsampling.  We found that core team members
 triggered of 89.39\% of the builds in the data set and 75.58\% of those builds
-passed.  Non-core team members triggered 10.61\% of the builds in the\clg{which?} data set
-and 64.70\% of the builds passed.
-
-\clg{upshot?}
+passed.  Non-core team members triggered 10.61\% of the builds in the data set
+and 64.70\% of the builds passed.  This shows that core team members are more
+likely to have a successful build integration than non-core team members.
 
@@
 the developer's abilities.  We specifically investigated if a developer with 
-followers was more likely to pass the build.  We found that only 0.87\% of the
+followers was more likely to pass the build in the data set without 
+downsampling.  We found that only 0.87\% of the
 contributions in the data set was performed by developers with zero 
@@
 performed by developers with 1000 or more followers.  We found that these
-contributions had a 78.61\% success rate.
-
-\clg{upshot?}
+contributions had a 78.61\% success rate.  These results show that developers
+with more followers are more likely to have a successful integration build.
 
@@
 
-\clg{connection back to theory?}
+Overall, this shows that while experience is not a perfect indicator, more
+experienced developers are more likely to make high quality project commits.
 
@@
  that for different reasons the job may not be successful even if the code 
- commited does not have flaws (a flacky test case for example). Since continuous 
+ committed does not have flaws (a flacky test case for example). Since continuous 
  integration is a best known practice in industry and the use of this methodology 
  spreads out into the open source community, we consider that cases of misuse of 
- CI such that it will lead to failing travis jobs when they should have actually 
+ CI such that it will lead to failing Travis jobs when they should have actually 
  be successful are minimum, specially since having a solid build is one of the 
@@
 
-Our results show that adding social data to the construction of the decision tree increases the probability this correctly predicting future commit's success in integrating into their corresponding projects by a margin of 4.09\% to 11.99\%, depending on the ratio of successful vs unsuccessful instances are used to train the desicion tree.
+Our results show that adding social data to the construction of the decision 
+tree increases the probability this correctly predicting future commit's success 
+in integrating into their corresponding projects by a margin of 4.09\% to 
+11.99\%, depending on the ratio of successful vs unsuccessful instances are 
+used to train the decision tree.
 

### 2017-02-20 Paper/MSRChallenge2017.tex
added a tad bit more to the decision tree classifer description

@@
 \paragraph{Metric}
-Because decision trees are well tested and easy to interpret, we used a decision
+Because decision trees are well tested supervised classifiers and easy to interpret, we used a decision
 tree classifier to create models which predict build integration success. 

### 2017-02-20 Paper/MSRChallenge2017.tex
revisions to the abstract and keywords

@@
 
-\title{Analyzing the impact of social attributes on the success of commit integration}
+\title{Analyzing the impact of social attributes on commit integration success}
 %Or some better name, Zack can probably think of a better one, he is good with names
+%ZC- Haha thanks.  I'm starting to lean to very descriptive titles now.  They
+%are nice for searching.
 
@@
 Software quality is an important and desirable aspect of the software 
-development process overall, especially with the increasing participation of a very
-diverse pool of developers, the number of commits and pull requests keeps increasing 
-and the mechanisms available to identify which developers are pushing high 
-quality commits and pull requests is scarce.
+development process. 
+As the software development community continues to make it easier for everyone
+to contribute, the number of commits and pull requests keep increasing.
+As the number of commits and pull requests increase, it becomes more difficult
+to only accept quality contributions.
 Recent research has explored how the open source community manages
-this question finding that both technical and social factors are factors in 
+this question, finding that both technical and social factors are factors in 
 the success of project contributions on GitHub.  
-This investigation defined a successful project contribution as a project
-contribution that gets
-accepted to the project. However, with continuous integration, we can
+However, with continuous integration, we can
 explore this question a step further.  We can better estimate the success of a
@@
 \begin{IEEEkeywords}
-Social Attributes; Travis CI; Github; Social Networks; Predicting Integration 
+Social Attributes; Travis CI; GitHub; Social Networks; Predicting Integration 
 Success; Social Coding

### 2017-02-20 Paper/MSRChallenge2017.tex
fixed GitHub capitalization

@@
 context of continuous integration, using some of the social attributes provided
-by Github as a proxy for the developer's experience level and familiarity with
+by GitHub as a proxy for the developer's experience level and familiarity with
 the process, and their importance when grouped with technical attributes of the commit as 
@@
 success when integrated to the automatic build process. Yu et al.~\cite{yu16} 
-analyze the impact of CI usage in Github and its correlation with software 
+analyze the impact of CI usage in GitHub and its correlation with software 
 quality. Unlike the works previously listed, our study focuses on independent social 
@@
 \textbf{Do social attributes, gathered 
-from the Github profiles of developers,
+from the GitHub profiles of developers,
 allow for more accurate predictions than only using technical data?}
@@
 To give an answer to main research question: ``Do social attributes, gathered 
-from the Github profiles of developers,
+from the GitHub profiles of developers,
 allow for more accurate predictions than only using technical data?", we 
@@
  projects used in this dataset have also been filtered to be popular (having more 
- than 10 watches on Github), and to have a history of using the continuous 
+ than 10 watches on GitHub), and to have a history of using the continuous 
  integration tool Travis CI for more than 50 builds. All these features help to 

### 2017-02-20 Paper/MSRChallenge2017.tex
minor revisions to the beginning of the paper

@@
 factors and the build status, and another with both the technical and social
-factors, this is to be able to compare how well can the job status be predicted 
-by just technical data, and adding social data.
+factors. We performed this split to analyze how well job status be predicted 
+by just technical factors, and then with additional social factors.
 
@@
 (errored, failed, canceled
-and started in the original data set). At this point we had a 3:1 successful to 
+and started in the original data set). We also condensed down all passing and
+failing builds in a commit to a single pass or fail for each build status.
+At this point we had a 3:1 successful to 
 not successful ratio in the rows of the data sets.
@@
 
-To avoid this and have a 1:1 ratio successful to not successful, we created a 
-separate data set where the
-successful builds were a random sub-sample of successful builds were selected
-such that the number of successful builds equaled the number of failing builds,
-known as downsampling.  We used 
+The high ratio of successful to not successful builds cause the classifier to 
+favor misclassifying not successful builds over successful builds, because a 1\%
+misclassification rate in 3/4th of the data is greater than a 1\%
+misclassification rate in 1/4th of the data.  To penalize misclassification for
+both classes equally, we created a separate data set where the
+successful builds equaled the number of not successful builds.  
+We build this data set by copying over all not successful builds and randomly
+selecting a sub-sample of the successful builds until the two build status were
+equal, known as downsampling.  We used 
 both the downsampled and non-downsampled data sets in our results to show the 
 difference of the behavior of the decision tree when it is trained with a equal 
-ratio than when it is trained with a non equal ratio.
+ratio than when it is trained with a unequal ratio.
 

### 2017-02-20 Paper/MSRChallenge2017.tex
revised the introduction

@@
 a project has been described as a meritocracy, where only the code is a factor
-in the decision~\cite{Scacchi07}.  However, to better understand successful 
-project contributions, we must take into consideration and analyze 
-different social attributes from the developers creating the commits,
-which can be great predictors for the success of a contribution.
+in the decision~\cite{Scacchi07}.  Yet, as social coding sites continue to get
+more users and specific projects become more popular, projects receive more
+community contributions.  As the number of contributions to a project increase,
+the project must dedicate more time to vetting these contributions.
 
@@
 community has developed various techniques to vet project contributions, such as pull
-requests which must be approved by a core team member~\cite{gousios14}. 
-These kinds of mechanisms benefit in substancial part by knowing into which 
-aspects to look for as predictors of the quality of the contribution being made.
+requests which must be approved by a core team member~\cite{gousios14}. Another
+contribution mechanism these projects use is continuous
+integration, which notifies the team members if a change caused a test 
+failure~\cite{Meyer14}.
+Yet, these methods can become a bottleneck.
+To avoid a possible bottleneck, it would be beneficial to prioritize certain
+contributions.  This prioritize can be achieved with predictors of the
+contribution's quality.
 
+Past projects have shown that both technical factors, which describe the commit
+and the project receiving the commit, and social factors, which describe the
+developer making the commit, have been found useful when predicting a
+contribution's quality~\cite{tsay14icse,tsay14fse}.
 In this study we analyze a large set of technical and social attributes 
-and how these can be used to
-add certainty to the probability of a contribution being successful or not. 
-Our corpus is based on the entries of a large number of open source projects
-using continuous integration. Continuous integration automatically checks
-the contribution against the project's test cases, to notify the development
-team if the change caused a test case failure~\cite{Meyer14}. The
-projects using continuous integration provide quality standard barriers such as
-test cases which will cause the build to break if the commit does not perform
-accordingly to the standards. When a change
-passes these vetting techniques, it shows that the project developers
-have confidence in the changes, therefore, allowing us to analyze the success
-of the contributions made by passing the quality standards created by the 
-core developers of each project.
+and how these can be used to predict a contributions quality, measured by the
+success of build integration jobs.
+We performed this analysis with a large corpus of open source projects
+which incorporated continuous integration in their development practice. 
+When a contribution to these projects pass integration tests, 
+it shows that the project developers
+have confidence in the changes. 
+Thus, we can use the build integration status of the commit as documentation of
+the commit's quality.
 
-In past studies, both technical factors and social factors have been found to be
-important when predicting pull request success~\cite{tsay14icse,tsay14fse}.
-In this study we are interested in analyzing the quality of a contribution 
-at a lower granulairity level, commit level. We will analyze this in the 
-context of continuous integration, using some of the social attributes provided
-by GitHub as a proxy for the developer's experience level and familiarity with
-the process, and their importance when grouped with technical attributes of the commit as 
-confounds for the complexity of the commit being pushed.
+While past studies have analyzed pull request
+success~\cite{tsay14icse,tsay14fse}, we are interested in analyzing the quality 
+of a contribution 
+at a lower granulairity level: individual commits. \todo{Zack question for Mau:
+did we really do the investigation at the individual commit level?} 
+We analyzed commits in the 
+context of continuous integration, using the technical factors found in the 
+some of the social attributes provided in the challenge
+corpus~\cite{msr17challenge}, and the social factors found on a developer's
+GitHub profile.  We used the technical factors to estimate the complexity of the
+commit, and the social factors to estimate the developer's experience.
 
-The knowledge obtained by 
-analyzing how much impact social characteristics have on the success of a commit 
-integration will help developers further understand what social attributes are 
-better proxies for experience and coding excellence; and it will also help code 
-integrators and core team members to know how to prioritize pull requests coming 
-from different developers, which of them may have a higher probability of 
-integration success based not only on the technical difficulty of the 
-integration, but also on social factors that determine the expertise of the 
-developer in their integration practices.
+This study investigates how well different technical and social factors predict
+commit quality.  This information will help core team members prioritize project
+contributions.  It will also provide a further understand of quality enforcement
+in the software development process.
 

### 2017-02-20 Paper/MSRChallenge2017.tex
revisions to the related work and contributions

@@
 determine that the social connection between the developer who is asking the 
-pull request and the integrators is a key factor torwards acceptance of a pull 
+pull request and the integrators is a key factor towards acceptance of a pull 
 request. Unlike this previous study, in our study we look at a broader aspect of 
@@
 strong relationship with the acceptance rate of a pull request. Bettenburgh et 
-al~\cite{bettenburgh10} discuss the impact of social interactions with 
+al.~\cite{bettenburgh10} discuss the impact of social interactions with 
 post-release defects, Vasilescu et al.~\cite{vasilescu14} explored how different 
@@
 Our study shows that social factors are an important aspect of build success but
-these factors alone do not fully predict if a contribution will be successfully integrated into the project. We also show
+these factors alone do not fully predict if a contribution will be successfully 
+integrated into the project. We also show
 that core team members are more likely to achieve build success than non-core
-team members and having followers increases the likelihood passing the
+team members and a developer with followers is more likely to pass the
 continuous integration build.

### 2017-02-20 Paper/MSRChallenge2017.tex
adjustments into the building dataset section

@@
 The goal of this study is to identify and understand the relationship 
-between the several different social properties that estimate the
-developer's experience such as contributions in the last year, repositories 
-participated, stars, etc., technical properties, such as files added and 
-modified, and the likelihood of a developer's commit
+between the social factors that describe the
+developer's experience (stars, followers, etc.) and technical properties that
+describe the commit's complexity
+(files added, files modified, etc.)
+when predicting the likelihood a developer's commit
 to be considered successfully integrated in the project. We define successful
@@
 \paragraph{Metric}
-Because decision trees are well tested supervised classifiers and easy to interpret, we used a decision
-tree classifier to create models which predict build integration success. 
-The first model was generated with only
-the technical factors, that provide insight on the complexity of the commit, 
-to understand how well technical factors predicted build
-success.  We then added the social factors to the technical factors to determine
-the influence of additional social factors on predicting build success.
-We evaluate the predictive power of these two 
-models with 10-fold cross validation and determine the effects of adding social
-factors when predicting build integration success.
-
+We measure quality software contributions by based on the build status of the
+commit: if the build passes or fails.
+To determine which factors are important for predicting build success, we used
+a decision tree classifier, because decision tress are well a tested supervised 
+classifier that are easy to interpret.
+To explore the question of technical and social factors, we first build a
+decision tree classifier using only the technical factors.  This first model
+allowed us to understand how well commit complexity estimated build integration
+success.  We then added the social factors to understand how the social factors
+integrated with the technical factors when predicting build integration success.
+We evaluated the predictive power of these two 
+models with 10-fold cross validation.
 \section{Building Dataset}
@@
 
-\textbf{Technical Factors:} For the technical factors, we collected
-these from the data set provided by the MSR Challenge~\cite{msr17challenge}.
+\textbf{Technical Factors:} We collected these factors from the 
+MSR Challenge data set~\cite{msr17challenge}.
 We extracted only the attributes in the data set that proxy the commit's
-complexity such as the size of the changes being performed as listed below:\begin{itemize}
+complexity, such as the size of the changes being performed.  The technical
+factors used are listed below:
+\begin{itemize}
 %\item tr\_original\_commit
 %\item gh\_build\_started\_at 
-\item Source churn: How many lines of code were changed by the new commit in this build.
-\item Files added: How many files were added by this commit.
-\item Files deleted: How many files were deleted by this commit.
-\item Files modified: How many files were modified by this commit.
-\item Tests added: How many tests were added by this commit.
-\item Tests deleted: How many tests were deleted by this commit.
-\item Source files: Number of files in the new commits. 
-\item Source loc: Number of executable source lines of code, in the entire repository.
-\item Travis status: Status of the travis build.
+\item Source churn: lines of code changed by this commit
+\item Files added: files added by this commit
+\item Files modified: files modified by this commit
+\item Tests added: tests added by this commit
+\item Tests deleted: tests deleted by this commit
+\item Source files: files in project at the time of the commit
+\item Source loc: lines of source code in the project at
+	the time of the commit.
+\item Travis status: status of the Travis build integration
 \end{itemize}

### 2017-02-20 Paper/MSRChallenge2017.tex
finished reivsion of the social factors

@@
 We scraped the commit author's
-\textit{username} from a commit page. If the scraper was able to find username, the
+\textit{username} from a commit page. If the scraper was able to find the username, the
 scraper went to the user's profile information
@@
 \item Repositories: the repositories the developer has access to. This 
-includes where the developer is the repository owner,where the developer is a 
-collaborator, and repositories that the developer can access through an 
-organization membership.\footnote{https://developer.github.com/v3/repos/}
+includes repositories the developer owns, repositories the developer contributes
+to, and repositories for which the developer has organizational membership access.
+\footnote{https://developer.github.com/v3/repos/}
 \item Stars: a count of the projects the developer has stared. Starring a project
-means to showing approval of the repository and creating a bookmark for later 
+to shows approval of the repository and creates  a bookmark for later 
 access.\footnote{https://help.github.com/articles/about-stars/}
-\item Followers: number of developers that that are following the author. 
-\item Following: number of developers that that are being followed by the author.
-\item Contributions in the last year: Number of contributions made by the author in the last year.
+\item Followers: number of developers that follow the author. 
+\item Following: number of developers that the author follows 
+\item Contributions in the last year: number of contributions made by the author in the last year.
 \end{itemize}
@@
 gh\_by\_core\_team\_member.
-This factor indicates if the developer making a contribution is a core member 
+This factor indicates if the commit's developer is a core member 
 of that project.

### 2017-02-20 Paper/MSRChallenge2017.tex
revisions up to the evaluation section

@@
 factors and the build status, and another with both the technical and social
-factors. We performed this split to analyze how well job status be predicted 
-by just technical factors, and then with additional social factors.
+factors. We performed this split to analyze how well technical factors alone,
+and then both technical and social
+factors predict build integration status.
 
-The data set used in this study~\cite{msr17challenge} is very diverse 
-and consists of commits that date from far back. The social data we 
+The data set used in this study~\cite{msr17challenge} is very diverse.
+and consists of commits from multiple years ago. The social data we 
 gather is recent, gathered in January 2017. In an effort to mitigate the threat of
@@
 three years of the data set's release (2014,2015,2016).  While this is not
-perfect, we believe that these numbers are unlikely to have changed
+a perfect solution , we believe that these numbers are unlikely to have changed
 significantly in the last three years.\clg{...did you spot check? Mau's Response: Spot
@@
 
-Since we are interested in the success of the job status of each row, we 
+\todo{Zack: Mau, check this first sentence}
+Since we are interested in the success of the job status of each commit, we 
 converted the Travis build statuses to just two possible values,

### 2017-02-20 Paper/MSRChallenge2017.tex
updated the table

@@
 
-\todo{Zack: Mau, check this first sentence}
+\todo{Zack: Mau, check this paragraph}
 Since we are interested in the success of the job status of each commit, we 
@@
 and started in the original data set). We also condensed down all passing and
-failing builds in a commit to a single pass or fail for each build status.
+failing builds in a commit to a single pass or fail for each build status.  If
+the commit contained both passing and failing build statuses, we removed the
+commit from the data set.
+\todo{confirm that this number doesn't change}
 At this point we had a 3:1 successful to 
@@
 \center
-  \caption{Comparison of predictive power by running 10-fold
+	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
     cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column). 
-The higher the percentages represent the higher number of instances we are able to correctly predict.
-\label{resultsTable}}
+	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
+	%Zack: the above sentence isn't true for the second row.
+	}   
 \end{table*}

### 2017-02-20 Paper/MSRChallenge2017.tex
finished changes to the evaluation and discussion

@@
 To determine which factors are important for predicting build success, we used
-a decision tree classifier, because decision tress are well a tested supervised 
-classifier that are easy to interpret.
+a decision tree classifier~\cite{Quinlan86}, because decision tress are well a 
+tested supervised classifier that are easy to interpret.
 To explore the question of technical and social factors, we first build a
@@
 \end{table*}
-
-We evaluated the predictive power of the social factors using a decision
-tree~\cite{Quinlan86}.
+To give an address to main research question: ``Do social attributes, gathered 
+from the GitHub profiles of developers,
+allow for more accurate predictions than only using technical data?", we 
+created a decision tree classifier~\cite{Quinlan86}.
 Decision trees are a predictive model which uses binary decisions on the
@@
 validation with the data in each data set.
-To give an answer to main research question: ``Do social attributes, gathered 
-from the GitHub profiles of developers,
-allow for more accurate predictions than only using technical data?", we 
-present the following results:
 
@@
 only the technical indicators has a correct classification rate of 77.01\% which
-means the technical attributes only increased the prediction accuracy by about 3\%.
+means the technical attributes only increased the prediction accuracy by about 3\%
+compared to a base line rate of guessing the build passed in all cases.
 Adding the social data increased the classifier's accuracy from 77.01\% to
@@
 On the downsampled data, the decision tree created from the technical attributes
-had a classification accuracy of 64.10\%, when predicting a successful build in
-all instances would produce 50.00\% accuracy.  After including the social data
+had a classification accuracy of 64.10\%, which outperformed the baseline of
+guessing all builds passed (50.00\%).
+ After including the social data
 in the data set, the classifier correctly predicted 76.09\% of the data set,
 about a 12\% improvement from only the technical data.  These results show that
-social data can be used to improve predictions of build integration success.
+both technical and social data can be used to improve predictions of build 
+integration success.
 
@@
 downsampling.  We found that core team members
-triggered of 89.39\% of the builds in the data set and 75.58\% of those builds
+triggered 89.39\% of the builds in the data set and 75.58\% of those builds
 passed.  Non-core team members triggered 10.61\% of the builds in the data set
@@
 developers with at least one or more followers.
-We found that developers with 0 followers had a successful build commit 68.49\%
+Developers with 0 followers had a successful build commit 68.49\%
 of the time.  Developers with one or more followers were successful 74.78\% of

### 2017-02-20 Paper/MSRChallenge2017.tex
finished revisions to the conclusion

@@
 \section{Conclusion}
-In this study we have analyzed the probability of Travis job success as being predicted by two different categories of attributes: Technical and Social data.
-We gathered the attributes that describe complexity of each commit being pushed and have created a decision tree that predicts if a future pushed commit will be successfully integrated into its corresponding build or not.
-Afterwards, we have gathered social attributes from the developers who pushed each of these commits
-and we have augmented our dataset with these attributes to understand whether adding social information about the developer would help the decision tree predict with higher accuracy future 
-instances.
+In this study we have analyzed how technical and social factors can be used to
+predict high quality contributions.  We have found that these factors provide
+insight when predicting the success of a build with a technical factors leading
+to a 14\% increase in predictive power, and another 12\% increase when
+incorporating social factors into the prediction.
 
-Our results show that adding social data to the construction of the decision 
-tree increases the probability this correctly predicting future commit's success 
-in integrating into their corresponding projects by a margin of 4.09\% to 
-11.99\%, depending on the ratio of successful vs unsuccessful instances are 
-used to train the decision tree.
-
-We have also found that non-core contributors cause not successful builds more
-than core contributors.  This leads us to believe that non-core contributions
-are not inspected as closely as they should be.  We have also found that having
-a follower, and especially a large follower base, can be an indicator of build
-integration success.
+We have also found that being a core contributor and having a large follower
+base can be an indicator of build integration success.
+These results provide evidence that more experienced
+developers are more likely to generate a high quality contribution.
 

### 2017-02-20 Paper/MSRChallenge2017.tex
getting it to 4 pages

@@
 community has developed various techniques to vet project contributions, such as pull
-requests which must be approved by a core team member~\cite{gousios14}. Another
-contribution mechanism these projects use is continuous
-integration, which notifies the team members if a change caused a test 
-failure~\cite{Meyer14}.
-Yet, these methods can become a bottleneck.
-To avoid a possible bottleneck, it would be beneficial to prioritize certain
-contributions.  This prioritize can be achieved with predictors of the
+requests which must be approved by a core team member~\cite{gousios14}. 
+These methods can become a bottleneck, and to avoid a possible bottleneck, it is beneficial to prioritize certain
+contributions.  This prioritization can be achieved with predictors of the
 contribution's quality.
@@
 success~\cite{tsay14icse,tsay14fse}, we are interested in analyzing the quality 
-of a contribution 
-at a lower granulairity level: individual commits. \todo{Zack question for Mau:
-did we really do the investigation at the individual commit level?} 
-We analyzed commits in the 
-context of continuous integration, using the technical factors found in the 
+of a contribution in the context of continuous integration, we analyze the success every time a developer pushes a contribution to be built.
+We analyzed contributions in the 
+context of continuous integration, using the technical factors found in
 some of the social attributes provided in the challenge
@@
 This study investigates how well different technical and social factors predict
-commit quality.  This information will help core team members prioritize project
-contributions.  It will also provide a further understand of quality enforcement
+contribution quality.  This information will help core team members prioritize project
+contributions, and will also provide a further understand of quality enforcement
 in the software development process.
@@
 %\item gh\_build\_started\_at 
-\item Source churn: lines of code changed by this commit
-\item Files added: files added by this commit
-\item Files modified: files modified by this commit
-\item Tests added: tests added by this commit
-\item Tests deleted: tests deleted by this commit
-\item Source files: files in project at the time of the commit
+\item Source churn: lines of code changed by this commit.
+\item Files added: files added by this commit.
+\item Files modified: files modified by this commit.
+\item Tests added: tests added by this commit.
+\item Tests deleted: tests deleted by this commit.
+\item Source files: files in project at the time of the commit.
 \item Source loc: lines of source code in the project at
 	the time of the commit.
-\item Travis status: status of the Travis build integration
+\item Travis status: status of the Travis build integration.
 \end{itemize}
@@
 
-We also added one item from the MSR Challenge data set to the social factors:
-gh\_by\_core\_team\_member.
-This factor indicates if the commit's developer is a core member 
+We also added one item from the MSR Challenge data set to the social factors that indicates if the commit's developer is a core member 
 of that project.
@@
 a perfect solution , we believe that these numbers are unlikely to have changed
-significantly in the last three years.\clg{...did you spot check? Mau's Response: Spot
-check that they did belong to those years? Yeah. Zack's Response: assuming you
-are asking a different question of if the values changed in the last three
-years, than no, we did not check because we weren't sure how.  What should we
-say here?}
+significantly in the last three years.
 
-\todo{Zack: Mau, check this paragraph}
-Since we are interested in the success of the job status of each commit, we 
+Since we are interested in the success of the job status of each contribution, we 
 converted the Travis build statuses to just two possible values,
@@
 failing builds in a commit to a single pass or fail for each build status.  If
-the commit contained both passing and failing build statuses, we removed the
-commit from the data set.
-\todo{confirm that this number doesn't change}
-At this point we had a 3:1 successful to 
-not successful ratio in the rows of the data sets.
-
-In the non-downsampled data set, 74.43\% of the builds were successful, the rest were not
+the commit contained both passing and failing build statuses, this means it is a failed build and we qualify it as such.
+At this point 74.43\% of the builds were successful, the rest were not
 successful.  This means that a classifier which guesses successful every time
@@
 selecting a sub-sample of the successful builds until the two build status were
-equal, known as downsampling.  We used 
+equal, a process known as downsampling.  We used 
 both the downsampled and non-downsampled data sets in our results to show the 
@@
 \section{Evaluation}
-
 \begin{table*}[ht]
@@
 
-%\textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\
+\textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\
 
-%\textbf{Mean absolute error}& 0.34 &  0.28 & 0.43 & 0.32\\
+\textbf{Mean absolute error}& 0.34 &  0.28 & 0.43 & 0.32\\
 
@@
 \end{table*}
-To give an address to main research question: ``Do social attributes, gathered 
+To address our main research question: ``Do social attributes, gathered 
 from the GitHub profiles of developers,
@@
 default Weka J48 decision tree algorithm, first without downsampling. The 
-decision tree built from
-only the technical indicators has a correct classification rate of 77.01\% which
-means the technical attributes only increased the prediction accuracy by about 3\%
-compared to a base line rate of guessing the build passed in all cases.
-Adding the social data increased the classifier's accuracy from 77.01\% to
-81.10\%, a 4.09\% increase.
-
-On the downsampled data, the decision tree created from the technical attributes
+decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
 had a classification accuracy of 64.10\%, which outperformed the baseline of
@@
 integration success.
+
+It is also worth noticing that in both cases the Kappa statistic increases when adding social data (100\% and 85\% respectively) which represents a more robust measure than Correctly classified instances, since it takes into account the correctly guessed instances occurring by chance, and we may also notice that the Mean absolute error decreases, giving stronger confidence to our claims when considering eventual outcomes.
 
@@
 
-\paragraph{Internal validity}
-The researchers in this study used the dataset provided by the 
- MSRChallenge~\cite{msr17challenge} to gain useful information regarding the 
- behavior of developers when pushing commits and how well these commits integrate 
- successfully with the project. The authors have used 
+%\paragraph{Internal validity}
+ The authors used 
  Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for 
@@
  scripts to obtain the developer social data are publicly available to facilitate 
- the transparency and quality of the process(Will be made available after double blind review).%\footnote{https://goo.gl/CqTX44}
+ the transparency and quality of the process (Will be available after double blind review).%\footnote{https://goo.gl/CqTX44}
 
-\paragraph{External validity} 
+%\paragraph{External validity} 
  To tackle the concern that the results of this study might not generalize to 
  other instances outside of the studied cases, we have used a broad and rich 
- dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
- projects used in this dataset have also been filtered to be popular (having more 
- than 10 watches on GitHub), and to have a history of using the continuous 
- integration tool Travis CI for more than 50 builds. All these features help to 
+ dataset~\cite{msr17challenge} in our analysis that comprises 1,359 popular projects, which help to 
  build the notion that since we are building our analysis on top of a vast 
- dataset comprehending a wide diversity of projects, the threat of this analysis 
+ data set, the threat of this analysis 
  not generalizing to other projects is mitigated.
-
-\paragraph{Construct validity}
- Travis job success is not the only way to analyze the success of a commit, and 
- that for different reasons the job may not be successful even if the code 
- committed does not have flaws (a flacky test case for example). Since continuous 
- integration is a best known practice in industry and the use of this methodology 
- spreads out into the open source community, we consider that cases of misuse of 
- CI such that it will lead to failing Travis jobs when they should have actually 
- be successful are minimum, specially since having a solid build is one of the 
- main purposes of the methodology, and taking into account that the projects in 
- out dataset are projects with a history of using continuous integration and 
- having a certain level of popularity, this threat is minimized. We therefore 
- consider Travis job success to be a proxy 
- for success when integrating a commit into a larger project.
 

### 2017-02-20 Paper/MSRChallenge2017.tex
todos through top of research design

@@
 For managers of an open source project, it is important to ensure that the
-project consists of high quality contributions.  The decision to include code in
-a project has been described as a meritocracy, where only the code is a factor
-in the decision~\cite{Scacchi07}.  Yet, as social coding sites continue to get
-more users and specific projects become more popular, projects receive more
+project consists of high quality contributions.  As social coding sites attract
+more users and projects become more popular, they receive ever more
 community contributions.  As the number of contributions to a project increase,
 the project must dedicate more time to vetting these contributions. 
-
+%
 Over the years, the open source
@@
 requests which must be approved by a core team member~\cite{gousios14}. 
-These methods can become a bottleneck, and to avoid a possible bottleneck, it is beneficial to prioritize certain
-contributions.  This prioritization can be achieved with predictors of the
+These methods can become a bottleneck, and thus it is beneficial to prioritize certain
+contributions.  This prioritization can be achieved with predictors of a
 contribution's quality.
 
-Past projects have shown that both technical factors, which describe the commit
+The decision to include code in
+a project has been described as a meritocracy, where only the code is a factor
+in the decision~\cite{Scacchi07}.
+However, past research 
+has shown that both technical factors, which describe the commit
 and the project receiving the commit, and social factors, which describe the
 developer making the commit, have been found useful when predicting a
-contribution's quality~\cite{tsay14icse,tsay14fse}.
-In this study we analyze a large set of technical and social attributes 
+contribution's quality~\cite{tsay14icse,tsay14fse}.\todo{One or two more
+  sentences, either here or earlier in the paragraph (between the first and
+  second sentence), about why social factors might be interesting to study, or informative.}
+
+This previous work has focused on the predicted acceptance of \emph{pull requests}. 
+By contrast,  we are interested in analyzing the quality 
+of a contribution in the context of continuous integration. \todo{What's the
+  difference, and why might it matter? Why is CI interesting or different as
+  compared to pull requests?(one sentence or so).} Thus, we propose to analyze the
+success every time a developer pushes a contribution to be built. 
+In this study, we analyze a large set of technical and social attributes 
 and how these can be used to predict a contributions quality, measured by the
 success of build integration jobs.
-We performed this analysis with a large corpus of open source projects
+We performed this analysis on a large corpus of open source projects
 which incorporated continuous integration in their development practice. 
-When a contribution to these projects pass integration tests, 
-it shows that the project developers
-have confidence in the changes. 
+When a contribution to these projects passes integration tests, 
+it suggests that the project developers
+might have confidence in the changes. 
 Thus, we can use the build integration status of the commit as documentation of
@@
 
-While past studies have analyzed pull request
-success~\cite{tsay14icse,tsay14fse}, we are interested in analyzing the quality 
-of a contribution in the context of continuous integration, we analyze the success every time a developer pushes a contribution to be built.
-We analyzed contributions in the 
+In particular, we analyzed contributions in the 
 context of continuous integration, using the technical factors found in
-some of the social attributes provided in the challenge
+some\todo{First: don't use the word some basically ever.  Second: I'm not sure
+  what it means to analyze technical factors found in social attributes.  Maybe rephrase?} of the social attributes provided in the challenge
 corpus~\cite{msr17challenge}, and the social factors found on a developer's
@@
 commit, and the social factors to estimate the developer's experience.
-
-This study investigates how well different technical and social factors predict
-contribution quality.  This information will help core team members prioritize project
+Overall, our study investigates how well different technical and social factors predict
+contribution quality.\todo{One sentence summary of results}  This information can help core team members prioritize project
 contributions, and will also provide a further understand of quality enforcement
@@
 \textbf{Related work:}
-Similar studies have shown the relationship between different attributes and 
+Similar studies have shown the relationship between different\todo{which?
+  Social, technical?  Both?} attributes and 
 different measures of success: pull request acceptance~\cite{gousios14, 
 gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
-Tsay et al.~\cite{tsay14icse} performed a very relevant study where they 
-determine that the social connection between the developer who is asking the 
-pull request and the integrators is a key factor towards acceptance of a pull 
-request. Unlike this previous study, in our study we look at a broader aspect of 
-social aspects and how this attributes towards the success in Travis
-CI jobs.\footnote{https://docs.travis-ci.com/user/customizing-the-build} 
+Tsay et al.~\cite{tsay14icse} \todo{Read and delete this comment: one of you has
+  a habit of saying something like ``...performed a very relevant study where
+  they...'' in describing previous work.  This is needlessly wordy.  You can
+  write the exact same sentence, more or less (I changed ``determine'' to
+  ``show'', ``find'' might also work) without that clause} 
+show that the social connection between the developer initiating a
+pull request and the project integrators is a key factor towards acceptance of a pull 
+\todo{I think you mean something like ``in predicting acceptance'', not
+  ``towards''; do they argue causality?}
+request. Unlike this previous study, in our study, we look at a broader aspect of 
+social aspects and how this attributes\todo{wrong word (as in, this is a noun as
+  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
+CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
+  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
 Gousios et al.~\cite{gousios14} study the relationship between the area of the 
-source code being modified by the developer requesting the changes to be pulled 
-and the acceptance rate of these changes is highly correlated. Also existence of 
+source code being modified by the developer initiating a pull request 
+and the acceptance rate of these changes is highly correlated.\todo{The
+  preceding sentence is not grammatical.  Please fix.} Also existence of 
 tests and overall code quality~\cite{gousios15} are attributes that have a 
-strong relationship with the acceptance rate of a pull request. Bettenburgh et 
+strong relationship with the acceptance rate of a pull request.\todo{the
+  previous sentence is not a sentence.} Bettenburgh et 
 al.~\cite{bettenburgh10} discuss the impact of social interactions with 
-post-release defects, Vasilescu et al.~\cite{vasilescu14} explored how different 
+post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
 project characteristics (programming language, project age, etc.) affect commit 
-success when integrated to the automatic build process. Yu et al.~\cite{yu16} 
+success when integrated to\todo{wrong word} the automatic build process. Yu et al.~\cite{yu16} 
 analyze the impact of CI usage in GitHub and its correlation with software 
-quality. Unlike the works previously listed, our study focuses on independent social 
+quality. Unlike the works previously listed, we focus on independent social 
 attributes and how these relate to the success of the integration of a commit 
@@
 team members and a developer with followers is more likely to pass the
-continuous integration build.
+continuous integration build.\todo{This paragraph doesn't really belong in the
+  related work; I might move it above, near where I have a todo asking for a
+  summary of results.}
 

### 2017-02-20 Paper/MSRChallenge2017.tex
CLG edits todos through end

@@
 
-\textbf{Technical Factors:} We collected these factors from the 
+\todo{I would like both attribute description subsections better if they
+  provided a sentence (or a half sentence) of intuition explaining why the
+  proposed factors might be correlated with build success.  Maybe not one
+  sentence per factor (since some might be repetitive), but some epxlanation on
+  the underlying intuition or theory.}
+
+\paragraph{Technical Factors:} We collected these factors from the 
 MSR Challenge data set~\cite{msr17challenge}.
@@
 
-\textbf{Social Factors:} To collect the social data, we created a web scraper to extract the social data
+\paragraph{Social Factors:} To collect the social data, we created a web scraper to extract the social data
 from developer's profiles.
@@
 \footnote{https://developer.github.com/v3/repos/}
+\todo{Is this a count, or what?}
 \item Stars: a count of the projects the developer has stared. Starring a project
@@
 
-\textbf{Comparing two data sets:} We used the social data gathered to create two data 
+\paragraph{Comparing two data sets:} We used the social data\todo{Confusing,
+  since you proceed to say you build a dataset with technical factors as well as
+  social factors.} gathered to create two data 
 sets: one with only the technical
@@
 The data set used in this study~\cite{msr17challenge} is very diverse.
-and consists of commits from multiple years ago. The social data we 
+and consists of commits from multiple\todo{How many? Please be precise.} years ago. The social data we 
 gather is recent, gathered in January 2017. In an effort to mitigate the threat of
@@
 a perfect solution , we believe that these numbers are unlikely to have changed
-significantly in the last three years.
+significantly in the last three years.\todo{Why?}
 
@@
 
-The high ratio of successful to not successful builds cause the classifier to 
-favor misclassifying not successful builds over successful builds, because a 1\%
+The high ratio of successful to not successful builds leads a naive classifier to 
+favor misclassifying not successful\todo{everywhere you say ``not successful'',
+  replace with ``unsuccessful''.} builds over successful builds, because a 1\%
 misclassification rate in 3/4th of the data is greater than a 1\%
@@
 
+\todo{Maybe a quick list of the 3--4 factors you actually look at?}
+
 \subsection{Success Classification}
 
+\todo{a better subsection heading might be ``Classification with and without
+  social factors.'', since all experiments look at success classification.}
 Table~\ref{resultsTable} shows the results of running the two data sets through the
-default Weka J48 decision tree algorithm, first without downsampling. The 
+default Weka J48 decision tree algorithm.  Without downsampling, the 
 decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
@@
 
-It is also worth noticing that in both cases the Kappa statistic increases when adding social data (100\% and 85\% respectively) which represents a more robust measure than Correctly classified instances, since it takes into account the correctly guessed instances occurring by chance, and we may also notice that the Mean absolute error decreases, giving stronger confidence to our claims when considering eventual outcomes.
+It is also worth noticing that in both cases the Kappa statistic increases when
+adding social data (100\% and 85\% respectively) which represents a more robust
+measure than Correctly classified instances\todo{Whenever you use a phrase that
+  is a key label in your data (like ``Correctly classified''), find a way to
+  typeset it differently so it scans as an important concept.  Quotes or Italics/emphasis
+  is fine.}, since it takes into account the
+correctly guessed instances occurring by chance, and we may also notice that the
+Mean absolute error decreases, giving stronger confidence to our claims when
+considering eventual outcomes.
 
@@
 
+\todo{One sentence introducing this experiment.}
 To determine if core team member's have greater build success rates,
@@
 
-We also investigated if developers with followers were more likely to have a
-successful build integration, since have followers may be seen as vouching for
+\todo{Maybe ``relationship with'' rather than ``effect on''?
+
+We also investigated whether developers with followers were more likely to have a
+successful build integration, since followers may be seen as vouching for
 the developer's abilities.  We specifically investigated if a developer with 
@@
 
-Overall, we have found that social attributes which proxy experience produce a 
+Overall, we have found that social attributes which proxy experience\todo{, such
+  as, example,} produce a 
 noticeable increase in predicting build success.  While the increase was noticeable 
@@
  not generalizing to other projects is mitigated.
+\todo{mention the threat of the collapsing of data as you were discussing over email.}
 

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed a few comments

@@
 in the decision~\cite{Scacchi07}.
-However, past research 
-has shown that both technical factors, which describe the commit
-and the project receiving the commit, and social factors, which describe the
-developer making the commit, have been found useful when predicting a
-contribution's quality~\cite{tsay14icse,tsay14fse}.\todo{One or two more
-  sentences, either here or earlier in the paragraph (between the first and
-  second sentence), about why social factors might be interesting to study, or informative.}
+While one would think that only the complexity of the commit is important, past
+studies have shown that the developer making the commit is also an important
+indicator when investigating contribution quality~\cite{tsay14icse, tasy14fse}.
+Thus, both technical factors, which describe the complexity of the commit, and
+social factors, which describe the developer's experience, are important when
+investigating contribution quality.
 
@@
 By contrast,  we are interested in analyzing the quality 
-of a contribution in the context of continuous integration. \todo{What's the
-  difference, and why might it matter? Why is CI interesting or different as
-  compared to pull requests?(one sentence or so).} Thus, we propose to analyze the
-success every time a developer pushes a contribution to be built. 
+of a contribution in the context of continuous integration.  While pull requests
+quality is determined through manual inspection, continuous integration quality
+is automatically determined through test cases, and thus approach the problem of
+quality determination differently.
+We investigate the factors involved in continuous integration build success.
 In this study, we analyze a large set of technical and social attributes 
@@
 converted the Travis build statuses to just two possible values,
-successful (passed in the original provided data set) and not successful 
+successful (passed in the original provided data set) and unsuccessful 
 (errored, failed, canceled
@@
 
-The high ratio of successful to not successful builds leads a naive classifier to 
-favor misclassifying not successful\todo{everywhere you say ``not successful'',
-  replace with ``unsuccessful''.} builds over successful builds, because a 1\%
+The high ratio of successful to unsuccessful builds leads a naive classifier to 
+favor misclassifying unsuccessful builds over successful builds, because a 1\%
 misclassification rate in 3/4th of the data is greater than a 1\%
@@
 both classes equally, we created a separate data set where the
-successful builds equaled the number of not successful builds.  
-We build this data set by copying over all not successful builds and randomly
+successful builds equaled the number of unsuccessful builds.  
+We build this data set by copying over all unsuccessful builds and randomly
 selecting a sub-sample of the successful builds until the two build status were

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed more todos

@@
 Overall, our study investigates how well different technical and social factors predict
-contribution quality.\todo{One sentence summary of results}  This information can help core team members prioritize project
+contribution quality. This information can help core team members prioritize project
 contributions, and will also provide a further understand of quality enforcement
 in the software development process.
+
+Our study shows that social factors are an important aspect of build success but
+these factors alone do not fully predict if a contribution will be successfully 
+integrated into the project. We also show
+that core team members are more likely to achieve build success than non-core
+team members and a developer with followers is more likely to pass the
+continuous integration build.
 
@@
   above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
-Gousios et al.~\cite{gousios14} study the relationship between the area of the 
-source code being modified by the developer initiating a pull request 
-and the acceptance rate of these changes is highly correlated.\todo{The
-  preceding sentence is not grammatical.  Please fix.} Also existence of 
+Gousios et al.~\cite{gousios14} found that the change location of a commit was
+an important indicator in the acceptance rate of those commits by the project.
+Also, the inclusion of test cases with a commit has been shown to increase the
+commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
+previous sentence is correct.  I am just guessing by what you had earlier}.
 tests and overall code quality~\cite{gousios15} are attributes that have a 
-strong relationship with the acceptance rate of a pull request.\todo{the
-  previous sentence is not a sentence.} Bettenburgh et 
+strong relationship with the acceptance rate of a pull request.
+ Bettenburgh et 
 al.~\cite{bettenburgh10} discuss the impact of social interactions with 
@@
 project characteristics (programming language, project age, etc.) affect commit 
-success when integrated to\todo{wrong word} the automatic build process. Yu et al.~\cite{yu16} 
+success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
 analyze the impact of CI usage in GitHub and its correlation with software 
@@
 pushed by the developer being described by these social attributes.
-
-Our study shows that social factors are an important aspect of build success but
-these factors alone do not fully predict if a contribution will be successfully 
-integrated into the project. We also show
-that core team members are more likely to achieve build success than non-core
-team members and a developer with followers is more likely to pass the
-continuous integration build.\todo{This paragraph doesn't really belong in the
-  related work; I might move it above, near where I have a todo asking for a
-  summary of results.}
 
@@
 %\item gh\_build\_started\_at 
-\item Source churn: lines of code changed by this commit.
-\item Files added: files added by this commit.
-\item Files modified: files modified by this commit.
-\item Tests added: tests added by this commit.
-\item Tests deleted: tests deleted by this commit.
-\item Source files: files in project at the time of the commit.
-\item Source loc: lines of source code in the project at
+\item Source churn: a count of the lines of code changed by this commit.
+\item Files added: a count of the files added by this commit.
+\item Files modified: a count of the files modified by this commit.
+\item Tests added: a count of the tests added by this commit.
+\item Tests deleted: a count of the tests deleted by this commit.
+\item Source files: a count of the files in project at the time of the commit.
+\item Source loc: a count of the lines of source code in the project at
 	the time of the commit.
@@
 \begin{itemize}
-\item Repositories: the repositories the developer has access to. This 
+\item Repositories: a count of the repositories the developer has access to. This 
 includes repositories the developer owns, repositories the developer contributes
@@
 \footnote{https://developer.github.com/v3/repos/}
-\todo{Is this a count, or what?}
 \item Stars: a count of the projects the developer has stared. Starring a project

### 2017-02-21 Paper/MSRChallenge2017.tex
fixed broken todo

@@
 
-\paragraph{Comparing two data sets:} We used the social data\todo{Confusing,
-  since you proceed to say you build a dataset with technical factors as well as
-  social factors.} gathered to create two data 
-sets: one with only the technical
+\paragraph{Comparing two data sets:} We compiled all the gather data into 
+two data sets: one with only the technical
 factors and the build status, and another with both the technical and social
-factors. We performed this split to analyze how well technical factors alone,
+factors and the build status. We performed this split to analyze how well technical factors alone,
 and then both technical and social
@@
 
-\todo{Maybe ``relationship with'' rather than ``effect on''?
+\todo{Maybe ``relationship with'' rather than ``effect on''?}
 

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed subsection title
Fixed example of proxy of experience

@@
 
-Overall, we have found that social attributes which proxy experience\todo{, such
-  as, example,} produce a 
+Overall, we have found that social attributes which proxy experience, such as number of followers, produce a 
 noticeable increase in predicting build success.  While the increase was noticeable 

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed a comment in the discussion section

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 
-\subsection{Follower effect on build success}
-
-\todo{Maybe ``relationship with'' rather than ``effect on''?}
+\subsection{Follower relationship with build success}
 
@@
 
-Overall, we have found that social attributes which proxy experience\todo{, such
-  as, example,} produce a 
+Overall, we have found that social attributes which proxy experience, such if
+the developer is a core contributor for the project, produce a 
 noticeable increase in predicting build success.  While the increase was noticeable 

### 2017-02-21 Paper/MSRChallenge2017.tex
why we take recent years only

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 we removed the commits in the data set that were not performed within the last
-three years of the data set's release (2014,2015,2016).  While this is not
-a perfect solution , we believe that these numbers are unlikely to have changed
-significantly in the last three years.\todo{Why?}
+three years of the data set's release (2014,2015,2016).
+This is with the intuition that the social attributes are more likely to have similar values in the most recent years than if we were to consider the whole time span of the projects in the data set.
 

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed the roadmap todo

@@
 
-\todo{Maybe a quick list of the 3--4 factors you actually look at?}
+In Section~\ref{sec:successClassification} we discuss the build classification
+success rate for the technical and social factors.  In Section~\ref{sec:core},
+we compare the build success rate of core project members to non-core project
+members.  In Section~\ref{sec:folowerSuccess}, we compare the relationship
+between a developer's followers and the build integration success.
 
 \subsection{Success Classification}
+\label{sec:successClassification}
 
@@
 \subsection{Build success by core team member}
+\label{sec:core}
 
@@
 \subsection{Follower relationship with build success}
+\label{sec:followerSuccess}
 

### 2017-02-21 Paper/MSRChallenge2017.tex
subsection heading

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 
-\paragraph{Technical Factors:} We collected these factors from the 
+\paragraph{Technical Factors} We collected these factors from the 
 MSR Challenge data set~\cite{msr17challenge}.
@@
 
-\paragraph{Social Factors:} To collect the social data, we created a web scraper to extract the social data
+\paragraph{Social Factors} To collect the social data, we created a web scraper to extract the social data
 from developer's profiles.
@@
 
-\paragraph{Comparing two data sets:} We compiled all the gather data into 
+\paragraph{Comparing two data sets} We compiled all the gather data into 
 two data sets: one with only the technical
@@
 
-The data set used in this study~\cite{msr17challenge} is very diverse.
-and consists of commits from multiple\todo{How many? Please be precise.} years ago. The social data we 
+The data set used in this study~\cite{msr17challenge} is very diverse,
+and consists of commits that date as far back as 2011. The social data we 
 gather is recent, gathered in January 2017. In an effort to mitigate the threat of
@@
 
-\subsection{Success Classification}
+\subsection{Classification with and without social factors}
 
-\todo{a better subsection heading might be ``Classification with and without
-  social factors.'', since all experiments look at success classification.}
 Table~\ref{resultsTable} shows the results of running the two data sets through the

### 2017-02-21 Paper/MSRChallenge2017.tex

@@
 
-\todo{Maybe a quick list of the 3--4 factors you actually look at?}
+In Section~\ref{sec:successClassification} we discuss the build classification
+success rate for the technical and social factors.  In Section~\ref{sec:core},
+we compare the build success rate of core project members to non-core project
+members.  In Section~\ref{sec:folowerSuccess}, we compare the relationship
+between a developer's followers and the build integration success.
 
 \subsection{Classification with and without social factors}
+\label{sec:successClassification}
 

### 2017-02-21 Paper/MSRChallenge2017.tex
added more to the threats to validity

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
  not generalizing to other projects is mitigated.
-\todo{mention the threat of the collapsing of data as you were discussing over email.}
+
+ Other concerns of the study include the possibility that the social factors
+ have changed significantly in the past three years, the collapsing of a
+ commit's build success to a single successful build and unsuccessful build
+ distorted the results, and the possibility that unsuccessful builds were due to
+ incorrect test cases and not low quality contributions.
 

### 2017-02-21 Paper/MSRChallenge2017.tex
italics in correctly classified

@@
 default Weka J48 decision tree algorithm.  Without downsampling, the 
-decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
+decision tree shows an increase of 4.09\% \textit{correctly classified} instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
 had a classification accuracy of 64.10\%, which outperformed the baseline of
@@
 adding social data (100\% and 85\% respectively) which represents a more robust
-measure than Correctly classified instances\todo{Whenever you use a phrase that
-  is a key label in your data (like ``Correctly classified''), find a way to
-  typeset it differently so it scans as an important concept.  Quotes or Italics/emphasis
-  is fine.}, since it takes into account the
+measure than \textit{correctly classified} instances, since it takes into account the
 correctly guessed instances occurring by chance, and we may also notice that the

### 2017-02-21 Paper/MSRChallenge2017.tex
remvoing a comment

@@
 \textbf{Related work:}
-Similar studies have shown the relationship between different\todo{which?
-  Social, technical?  Both?} attributes and 
+Similar studies have shown the relationship between both social and technical attributes attributes and 
 different measures of success: pull request acceptance~\cite{gousios14, 
 gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
-Tsay et al.~\cite{tsay14icse} \todo{Read and delete this comment: one of you has
-  a habit of saying something like ``...performed a very relevant study where
-  they...'' in describing previous work.  This is needlessly wordy.  You can
-  write the exact same sentence, more or less (I changed ``determine'' to
-  ``show'', ``find'' might also work) without that clause} 
-show that the social connection between the developer initiating a
+Tsay et al.~\cite{tsay14icse} show that the social connection between the developer initiating a
 pull request and the project integrators is a key factor towards acceptance of a pull 

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed some related work todos

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
-Tsay et al.~\cite{tsay14icse} \todo{Read and delete this comment: one of you has
-  a habit of saying something like ``...performed a very relevant study where
-  they...'' in describing previous work.  This is needlessly wordy.  You can
-  write the exact same sentence, more or less (I changed ``determine'' to
-  ``show'', ``find'' might also work) without that clause} 
+Tsay et al.~\cite{tsay14icse} 
 show that the social connection between the developer initiating a
-pull request and the project integrators is a key factor towards acceptance of a pull 
-\todo{I think you mean something like ``in predicting acceptance'', not
-  ``towards''; do they argue causality?}
+pull request and the project integrators is a key factor in predicting 
+acceptance of a pull 
 request. Unlike this previous study, in our study, we look at a broader aspect of 
-social aspects and how this attributes\todo{wrong word (as in, this is a noun as
-  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
-CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
-  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
-Gousios et al.~\cite{gousios14} found that the change location of a commit was
+social aspects, and focus on predicting the success in Travis
+CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
 an important indicator in the acceptance rate of those commits by the project.

### 2017-02-21 Paper/MSRChallenge2017.tex

@@
 \textbf{Related work:}
-Similar studies have shown the relationship between different\todo{which?
-  Social, technical?  Both?} attributes and 
+Similar studies have shown the relationship between both social and technical attributes attributes and 
 different measures of success: pull request acceptance~\cite{gousios14, 

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed more related work todos

@@
 In particular, we analyzed contributions in the 
-context of continuous integration, using the technical factors found in
-some\todo{First: don't use the word some basically ever.  Second: I'm not sure
-  what it means to analyze technical factors found in social attributes.  Maybe rephrase?} of the social attributes provided in the challenge
+context of continuous integration, using the technical factors and one social
+factor found in the challenge
 corpus~\cite{msr17challenge}, and the social factors found on a developer's

### 2017-02-21 Paper/MSRChallenge2017.tex
four pager can have a shorter abstract.  Also a todo

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
   {{\scriptsize \textbf{\color{red} {#1}}}}
+%\newcommand{\todo}[1] {}
 \newcommand{\clg}[1]
@@
 \begin{abstract}
-Software quality is an important and desirable aspect of the software 
-development process. 
 As the software development community continues to make it easier for everyone
-to contribute, the number of commits and pull requests keep increasing.
-As the number of commits and pull requests increase, it becomes more difficult
-to only accept quality contributions.
-Recent research has explored how the open source community manages
-this question, finding that both technical and social factors are factors in 
+to contribute, the number of commits and pull requests keep increasing. However, this exciting growth
+renders it more difficult to only accept quality contributions.
+Recent research has found 
+that both technical and social factors predict
 the success of project contributions on GitHub.  
-However, with continuous integration, we can
-explore this question a step further.  We can better estimate the success of a
-contribution by investigating if the contribution passed all the quality standards set 
-by the repository owners.  We performed an initial investigation into the technical and
-social factors involved in a commit that successfully passes the integration
-tests. Specifically, we investigated if social factors (such as being a
+We take this question a step further, focusing on predicting continuous
+integration build success based on technical and
+social factors involved in a commit.
+Specifically, we investigated if social factors (such as being a
 core member of the development team, having a large number of followers,
 or contributing a large number of commits) improve predictions of build
-success.  We have found that while social factors cause a noticeable increase
+success.  We found that while social factors cause a noticeable increase
 in predictive power (12\%), further investigation into these factors are
-required.
+required.\todo{drop the post-comma clause and instead summarize the specific
+  effects we investigated (contributor, followers, etc).}
 \end{abstract}
@@
 gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
-Tsay et al.~\cite{tsay14icse} 
-show that the social connection between the developer initiating a
-pull request and the project integrators is a key factor in predicting 
-acceptance of a pull 
+Tsay et al.~\cite{tsay14icse} show that the social connection between the developer initiating a
+pull request and the project integrators is a key factor towards acceptance of a pull 
+\todo{I think you mean something like ``in predicting acceptance'', not
+  ``towards''; do they argue causality?}
 request. Unlike this previous study, in our study, we look at a broader aspect of 
-social aspects, and focus on predicting the success in Travis
-CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
+social aspects and how this attributes\todo{wrong word (as in, this is a noun as
+  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
+CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
+  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
+Gousios et al.~\cite{gousios14} found that the change location of a commit was
 an important indicator in the acceptance rate of those commits by the project.

### 2017-02-21 Paper/MSRChallenge2017.tex
address a result todo

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 
-\todo{One sentence introducing this experiment.}
-To determine if core team member's have greater build success rates,
-we classified the build success rate for
-core team members and non-core team members in the data set without 
+Based on the decision tree results, we noticed that core team members where
+important when classifying build success, so we decided to investigate if core
+team members have greater build success rates.
+We classified the build success rate for
+core team members and non-core team members using the data set without 
 downsampling.  We found that core team members

### 2017-02-21 Paper/MSRChallenge2017.tex
a bit of space in the intro

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 \usepackage[usenames,dvipsnames]{color}
-\newcommand{\todo}[1]
-  {{\scriptsize \textbf{\color{red} {#1}}}}
-%\newcommand{\todo}[1] {}
+%\newcommand{\todo}[1]
+%  {{\scriptsize \textbf{\color{red} {#1}}}}
+\newcommand{\todo}[1] {}
 \newcommand{\clg}[1]
@@
 might have confidence in the changes. 
-Thus, we can use the build integration status of the commit as documentation of
-the commit's quality.
+Thus, we use the commit's build integration status as a proxy for its quality.
 
@@
 
-Our study shows that social factors are an important aspect of build success but
+We find that social factors are an important aspect of build success but
 these factors alone do not fully predict if a contribution will be successfully 
-integrated into the project. We also show
+integrated into the project. We find
 that core team members are more likely to achieve build success than non-core
-team members and a developer with followers is more likely to pass the
+members, and that developers with more followers are more likely to submit commits that pass the
 continuous integration build.
 
-\textbf{Related work:}
+\vspace{1ex}
+\noindent\textbf{Related work:}
 Similar studies have shown the relationship between both social and technical attributes attributes and 

### 2017-02-21 Paper/MSRChallenge2017.tex
a bit of space in the intro
space saving

@@
 \usepackage[usenames,dvipsnames]{color}
-%\newcommand{\todo}[1]
-%  {{\scriptsize \textbf{\color{red} {#1}}}}
-\newcommand{\todo}[1] {}
+\newcommand{\todo}[1]
+  {{\scriptsize \textbf{\color{red} {#1}}}}
+%\newcommand{\todo}[1] {}
 \newcommand{\clg}[1]
@@
 
-\paragraph{Goal}
+\vspace{1ex}
+\noindent\textbf{Goal.}
 The goal of this study is to identify and understand the relationship 
@@
 
-\paragraph{Question}
+\vspace{1ex}
+
+\noindent\textbf{Question.}
 Previous studies have identified a relationship between technical and social 
@@
 of a contribution performed by a particular developer.
-
-Therefore our main research question is presented as follows:
+%
+Therefore our main research question, upon which we can build by investigating particular attributes, is:
 
@@
 allow for more accurate predictions than only using technical data?}
-
-Depending on the results of this question, we can further explore which
-attributes are most important for predicting build integration success.
 
@@
 
-\paragraph{Metric}
-We measure quality software contributions by based on the build status of the
+\vspace{1ex}
+\noindent\textbf{Metric.} We measure quality software contributions by based on the build status of the
 commit: if the build passes or fails.
@@
 models with 10-fold cross validation.
+
 \section{Building Dataset}
@@
 We scraped the commit author's
-\textit{username} from a commit page. If the scraper was able to find the username, the
-scraper went to the user's profile information
-(\textit{https://github.com/\textbf{UserName}}).
-
+\textit{username} from each commit page, and then
+collected user's public profile information. 
+%(\textit{https://github.com/\textbf{UserName}}). 
+%
 The scraper then extracted the following items from the user's

### 2017-02-21 Paper/MSRChallenge2017.tex
bib todo
addressed description todo

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 might have confidence in the changes. 
-Thus, we use the commit's build integration status as a proxy for its quality.
+Thus, we can use the build integration status of the commit as documentation of
+the commit's quality.
 
@@
 
-We find that social factors are an important aspect of build success but
+Our study shows that social factors are an important aspect of build success but
 these factors alone do not fully predict if a contribution will be successfully 
-integrated into the project. We find
+integrated into the project. We also show
 that core team members are more likely to achieve build success than non-core
-members, and that developers with more followers are more likely to submit commits that pass the
+team members and a developer with followers is more likely to pass the
 continuous integration build.
 
-\vspace{1ex}
-\noindent\textbf{Related work:}
+\textbf{Related work:}
 Similar studies have shown the relationship between both social and technical attributes attributes and 
@@
 
-\todo{I would like both attribute description subsections better if they
-  provided a sentence (or a half sentence) of intuition explaining why the
-  proposed factors might be correlated with build success.  Maybe not one
-  sentence per factor (since some might be repetitive), but some epxlanation on
-  the underlying intuition or theory.}
-
 \paragraph{Technical Factors} We collected these factors from the 
@@
 We extracted only the attributes in the data set that proxy the commit's
-complexity, such as the size of the changes being performed.  The technical
+complexity, such as the size of the changes being performed.  
+The technical
 factors used are listed below:
@@
 \end{itemize}
+
+The first five factors represent the changes caused by the commit.  The next two
+factors cover the size of the project.  These factors represent the complexity
+of the change, and the complexity of the project incorporating the change.
 
@@
 \end{itemize}
+
+These social factors are all factors that are tied to a GitHub user's profile.
+These factors are likely to increase as developers spend more time on the site
+and gain more open source experience.  Thus, we use them as a proxy for
+experience.
 

### 2017-02-21 Paper/MSRChallenge2017.tex

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 
+\todo{It is not acceptable to only use the shortened venue name.  Also, bilbiography entries are missing venues again; fix it.}
+
 \bibliographystyle{plain}

### 2017-02-21 Paper/MSRChallenge2017.tex
comment
tightening

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 analyze the impact of CI usage in GitHub and its correlation with software 
-quality. Unlike the works previously listed, we focus on independent social 
-attributes and how these relate to the success of the integration of a commit 
-pushed by the developer being described by these social attributes.
+quality. By contrast, we focus on the relationship between independent social 
+attributes and continuous integration success.
 
@@
 \vspace{1ex}
-
 \noindent\textbf{Question.}
-Previous studies have identified a relationship between technical and social 
-factors and pull request acceptance. We are interested in understanding if
+%Previous studies have identified a relationship between technical and social 
+%factors and pull request acceptance. 
+We are interested in understanding whether
 social factors, used as a proxy for experience, can be used to predict
@@
 %
-Therefore our main research question, upon which we can build by investigating particular attributes, is:
+Our main research question, upon which we can build by investigating particular attributes, is:
 
@@
 \vspace{1ex}
-\noindent\textbf{Metric.} We measure quality software contributions by based on the build status of the
-commit: if the build passes or fails.
-To determine which factors are important for predicting build success, we used
-a decision tree classifier~\cite{Quinlan86}, because decision tress are well a 
-tested supervised classifier that are easy to interpret.
-To explore the question of technical and social factors, we first build a
-decision tree classifier using only the technical factors.  This first model
-allowed us to understand how well commit complexity estimated build integration
-success.  We then added the social factors to understand how the social factors
-integrated with the technical factors when predicting build integration success.
-We evaluated the predictive power of these two 
-models with 10-fold cross validation.
+\noindent\textbf{Metric.} We measure quality software contributions based on the build status of the
+commit. We used a decision tree classifier~\cite{Quinlan86} to identify
+important factors in predicting build success;  decision tress are well
+established  and interpretable. 
+We first build a
+decision tree classifier using only technical factors, which highlights
+the degree to which commit complexity predicts build integration
+success.  We then added the social factors to identify the degree to which they
+add predictive power to a the initial technical model. 
+We use 10-fold cross validation across our evaluation.
 

### 2017-02-21 Paper/MSRChallenge2017.tex

@@
 commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
-previous sentence is correct.  I am just guessing by what you had earlier}.
+previous sentence is correct.  I am just guessing by what you had earlier RESPONSE: Zack, I can't find what it used to say. You can just remove the sentence}.
 tests and overall code quality~\cite{gousios15} are attributes that have a 

### 2017-02-21 Paper/MSRChallenge2017.tex
tried to address the abstract

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 or contributing a large number of commits) improve predictions of build
-success.  We found that while social factors cause a noticeable increase
-in predictive power (12\%), further investigation into these factors are
-required.\todo{drop the post-comma clause and instead summarize the specific
-  effects we investigated (contributor, followers, etc).}
+success.  We found that social factors cause a noticeable increase
+in predictive power (12\%), core team members are more likely to pass the build
+tests (10\%), and users with 1000 or more follower are more likely to
+pass the build tests (10\%).
 \end{abstract}

### 2017-02-21 Paper/MSRChallenge2017.tex
removing unclear sentence

@@
 an important indicator in the acceptance rate of those commits by the project.
-Also, the inclusion of test cases with a commit has been shown to increase the
-commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
-previous sentence is correct.  I am just guessing by what you had earlier RESPONSE: Zack, I can't find what it used to say. You can just remove the sentence}.
-tests and overall code quality~\cite{gousios15} are attributes that have a 
+Tests and overall code quality~\cite{gousios15} are attributes that have a 
 strong relationship with the acceptance rate of a pull request.

### 2017-02-21 Paper/MSRChallenge2017.tex
fixed references and removed a todo

@@
 studies have shown that the developer making the commit is also an important
-indicator when investigating contribution quality~\cite{tsay14icse, tasy14fse}.
+indicator when investigating contribution quality~\cite{tsay14icse, tsay14fse}.
 Thus, both technical factors, which describe the complexity of the commit, and
@@
 an important indicator in the acceptance rate of those commits by the project.
-Tests and overall code quality~\cite{gousios15} are attributes that have a 
-strong relationship with the acceptance rate of a pull request.
+Also, the inclusion of test cases with a commit has been shown to increase the
+commit's acceptance rate~\cite{gousios15}.
 Bettenburgh et 
@@
 we compare the build success rate of core project members to non-core project
-members.  In Section~\ref{sec:folowerSuccess}, we compare the relationship
+members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
 between a developer's followers and the build integration success.

### 2017-02-21 Paper/MSRChallenge2017.tex
tightening

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 or contributing a large number of commits) improve predictions of build
-success.  We found that social factors cause a noticeable increase
-in predictive power (12\%), core team members are more likely to pass the build
-tests (10\%), and users with 1000 or more follower are more likely to
-pass the build tests (10\%).
+success.  We found that while social factors cause a noticeable increase
+in predictive power (12\%), further investigation into these factors are
+required.\todo{drop the post-comma clause and instead summarize the specific
+  effects we investigated (contributor, followers, etc).}
 \end{abstract}
@@
 
-To investigate our research questions, we built a data set based on the 
-attributes that consisted of both technical and social factors.
+We built a data set of
+attributes consisting of both technical and social factors:
 
-\paragraph{Technical Factors} We collected these factors from the 
+\vspace{1ex}
+\noindent\textbf{Technical Factors} We collected technical factors from the 
 MSR Challenge data set~\cite{msr17challenge}.
-We extracted only the attributes in the data set that proxy the commit's
-complexity, such as the size of the changes being performed.  
-The technical
-factors used are listed below:
+We extracted only the attributes in the data set that proxy a commit's
+complexity, such as commit size. 
+The technical factors used are:
 \begin{itemize}
@@
 
-\paragraph{Social Factors} To collect the social data, we created a web scraper to extract the social data
+\vspace{1ex}
+\noindent\textbf{Social Factors} To collect the social data, we created a web scraper to extract the social data
 from developer's profiles.
@@
 \textit{username} from each commit page, and then
-collected user's public profile information. 
+collected the following from the user's public profile information:
 %(\textit{https://github.com/\textbf{UserName}}). 
 %
-The scraper then extracted the following items from the user's
-profile.
 
@@
 
-These social factors are all factors that are tied to a GitHub user's profile.
-These factors are likely to increase as developers spend more time on the site
-and gain more open source experience.  Thus, we use them as a proxy for
+These social factors are all factors that are tied to a GitHub user's profile
+and that are generally correlated with user time and engagement with the site.
+Thus, we use them as a proxy for
 experience.
+We also added one item from the MSR Challenge data set, indiating
+whether the commit's developer is a core member  
+of the associated project.
 
-We also added one item from the MSR Challenge data set to the social factors that indicates if the commit's developer is a core member 
-of that project.
-
-\paragraph{Comparing two data sets} We compiled all the gather data into 
+\vspace{1ex}
+\noindent\textbf{Comparing two data sets.} We compiled the gathered data into 
 two data sets: one with only the technical
-factors and the build status, and another with both the technical and social
+factors and the build status, and another with both technical and social
 factors and the build status. We performed this split to analyze how well technical factors alone,
@@
 
-The data set used in this study~\cite{msr17challenge} is very diverse,
-and consists of commits that date as far back as 2011. The social data we 
+Our data set~\cite{msr17challenge} is very diverse, consisting
+of commits that date as far back as 2011. The social data we 
 gather is recent, gathered in January 2017. In an effort to mitigate the threat of
@@
 we removed the commits in the data set that were not performed within the last
-three years of the data set's release (2014,2015,2016).
-This is with the intuition that the social attributes are more likely to have similar values in the most recent years than if we were to consider the whole time span of the projects in the data set.
+three years of the data set's release (2014--2016).  Our intuition is
+that the social attributes are less likely to have substantively changed over a
+recent time span.
 
 Since we are interested in the success of the job status of each contribution, we 
-converted the Travis build statuses to just two possible values,
-successful (passed in the original provided data set) and unsuccessful 
+converted all Travis build statuses to two possible values:
+\emph{successful} (passed in the original provided data set) and \emph{unsuccessful}
 (errored, failed, canceled

### 2017-02-21 Paper/MSRChallenge2017.tex
space in lists

@@
 %\item gh\_build\_started\_at 
-\item Source churn: a count of the lines of code changed by this commit.
-\item Files added: a count of the files added by this commit.
-\item Files modified: a count of the files modified by this commit.
-\item Tests added: a count of the tests added by this commit.
-\item Tests deleted: a count of the tests deleted by this commit.
-\item Source files: a count of the files in project at the time of the commit.
-\item Source loc: a count of the lines of source code in the project at
+\item Source churn, changed lines of code.
+\item Files added by this commit.
+\item Files modified by this commit.
+\item Tests added by this commit.
+\item Tests deleted by this commit.
+\item Total source files in project at the time of the commit.
+\item Source lines of source code in the project at
 	the time of the commit.
-\item Travis status: status of the Travis build integration.
+\item Travis status, or status of the Travis build integration.
 \end{itemize}
@@
 \begin{itemize}
-\item Repositories: a count of the repositories the developer has access to. This 
-includes repositories the developer owns, repositories the developer contributes
-to, and repositories for which the developer has organizational membership access.
+\item Repositories: number of repositories the developer can access, including those
+the developer owns, contributes
+to, and for which the developer has organizational membership access.%
 \footnote{https://developer.github.com/v3/repos/}

### 2017-02-21 Paper/MSRChallenge2017.tex
cutting repeteitive stuff

@@
 
-\section{Building Dataset}
+\section{Building the Dataset}
 \label{approach}
@@
 \vspace{1ex}
-\noindent\textbf{Social Factors} To collect the social data, we created a web scraper to extract the social data
+\noindent\textbf{Social Factors.} We created a web scraper to extract the social data
 from developer's profiles.
 We used the commit hash and the project name in the original data
-set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
+set provided by the MSR Challenge~\cite{msr17challenge} to locate thecommit web page
 of the commit, leveraging \textit{github.com}'s URL standard for projects and
@@
 % \newline \newline
-
+%
 We scraped the commit author's
 \textit{username} from each commit page, and then
-collected the following from the user's public profile information:
+collected the following from the user's public profile:
 %(\textit{https://github.com/\textbf{UserName}}). 
@@
 
-Our data set~\cite{msr17challenge} is very diverse, consisting
+Our data set~\cite{msr17challenge} consists
 of commits that date as far back as 2011. The social data we 
-gather is recent, gathered in January 2017. In an effort to mitigate the threat of
-using future result to predict previous events,
-we removed the commits in the data set that were not performed within the last
-three years of the data set's release (2014--2016).  Our intuition is
-that the social attributes are less likely to have substantively changed over a
-recent time span.
+gather is recent, gathered in January 2017. To mitigate the threat of
+using future results to predict previous events,
+we removed only include data set commits from the years 2014--2016.  Our intuition is
+that the social attributes are less likely to have substantively changed more recently.
 
@@
 failing builds in a commit to a single pass or fail for each build status.  If
-the commit contained both passing and failing build statuses, this means it is a failed build and we qualify it as such.
-At this point 74.43\% of the builds were successful, the rest were not
-successful.  This means that a classifier which guesses successful every time
-would produce a classification rate of 74.43\% if ran on the full data
-set.
+the commit contained both passing and failing build statuses, we treat it as a failed build.
 
-The high ratio of successful to unsuccessful builds leads a naive classifier to 
-favor misclassifying unsuccessful builds over successful builds, because a 1\%
-misclassification rate in 3/4th of the data is greater than a 1\%
-misclassification rate in 1/4th of the data.  To penalize misclassification for
-both classes equally, we created a separate data set where the
-successful builds equaled the number of unsuccessful builds.  
-We build this data set by copying over all unsuccessful builds and randomly
-selecting a sub-sample of the successful builds until the two build status were
-equal, a process known as downsampling.  We used 
-both the downsampled and non-downsampled data sets in our results to show the 
-difference of the behavior of the decision tree when it is trained with a equal 
-ratio than when it is trained with a unequal ratio.
+74.43\% of the builds in the reduced dataset were successful, and thus a naive
+classifer that always guesses ``successful'' would succeed 74.43\% of the time.
+To penalize misclassification for
+both classes equally, we created a second balanced dataset by randomly 
+sub-sampling the successful builds until the two build status were
+equal, a process known as downsampling.  We show results on both the 
+downsampled and non-downsampled data sets.
 

### 2017-02-21 Paper/MSRChallenge2017.tex

@@
   {{\scriptsize \textbf{\color{red} {#1}}}}
+
 %\newcommand{\todo}[1] {}
@@
 sub-sampling the successful builds until the two build status were
-equal, a process known as downsampling.  We show results on both the 
-downsampled and non-downsampled data sets.
+equal, a process known as downsampling.  We train on the down-sampled data but show results on both 
+downsampled and non-downsampled data sets.\todo{CLG says: that last sentence is
+  true, right?}
 
@@
 %\paragraph{Internal validity}
- The authors used 
- Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for 
- usage of machine learning algorithms to analyze our datasets. We are aware that, 
- as every human written tool, Weka is prone to contain errors and/or bugs; 
- nonetheless, Weka is a broadly used, open source tool that is subject to high 
- quality standards and a vast user and developer base which makes it more likely 
- to be a high quality code and to have less bugs than lesser used tools.
+We use Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, a well known machine-learning tool,
+to analyze our data.
+Like all tools, Weka is prone to contain errors and/or bugs. 
+Nonetheless, Weka is a well-known used, open source tool, and as such is likely
+to be of relatively high quality, mitigating threats to internal validity.
 
@@
 %\paragraph{External validity} 
- To tackle the concern that the results of this study might not generalize to 
- other instances outside of the studied cases, we have used a broad and rich 
- dataset~\cite{msr17challenge} in our analysis that comprises 1,359 popular projects, which help to 
- build the notion that since we are building our analysis on top of a vast 
- data set, the threat of this analysis 
- not generalizing to other projects is mitigated.
-
+Our results might not generalize to 
+ other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
+ dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
  Other concerns of the study include the possibility that the social factors
@@
  distorted the results, and the possibility that unsuccessful builds were due to
- incorrect test cases and not low quality contributions.
+ incorrect test cases and not low quality contributions.\todo{...and?  Something
+   like ``future work remains to assess the degree of these threats'' will do.}
 
 \section{Conclusion}
-In this study we have analyzed how technical and social factors can be used to
-predict high quality contributions.  We have found that these factors provide
+
+We have analyzed how technical and social factors can be used to
+predict high quality open source contributions, as measured by continuous
+integration build success.  We have found that these factors provide
 insight when predicting the success of a build with a technical factors leading

### 2017-02-21 Paper/MSRChallenge2017.tex
fixed the todos

@@
 sub-sampling the successful builds until the two build status were
-equal, a process known as downsampling.  We train on the down-sampled data but show results on both 
-downsampled and non-downsampled data sets.\todo{CLG says: that last sentence is
-  true, right?}
-
+equal, a process known as downsampling.  We train and present results for both
+data sets individually.
 \section{Evaluation}
@@
  distorted the results, and the possibility that unsuccessful builds were due to
- incorrect test cases and not low quality contributions.\todo{...and?  Something
-   like ``future work remains to assess the degree of these threats'' will do.}
+ incorrect test cases and not low quality contributions.  Future work will be
+ required to investigate the influence of these threats.
 
@@
 
-\todo{It is not acceptable to only use the shortened venue name.  Also, bilbiography entries are missing venues again; fix it.}
-
 \bibliographystyle{plain}

### 2017-02-21 Paper/MSRChallenge2017.tex
added a line space
fixed a spacing problem

@@
 social aspects, and focus on predicting the success in Travis
-CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
+CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
 an important indicator in the acceptance rate of those commits by the project.
@@
  dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
+
  Other concerns of the study include the possibility that the social factors

### 2017-02-21 Paper/MSRChallenge2017.tex
changed capitatlization

@@
 correctly guessed instances occurring by chance, and we may also notice that the
-Mean absolute error decreases, giving stronger confidence to our claims when
+mean absolute error decreases, giving stronger confidence to our claims when
 considering eventual outcomes.

### 2017-02-21 Paper/MSRChallenge2017.tex
adjusted a sentence

@@
 
-Overall, this shows that while experience is not a perfect indicator, more
+Overall, we have found that while experience is not a perfect indicator, 
 experienced developers are more likely to make high quality project commits.

### 2017-02-21 Paper/MSRChallenge2017.tex
typo

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 In this study, we analyze a large set of technical and social attributes 
-and how these can be used to predict a contributions quality, measured by the
+and how these can be used to predict a contribution's quality, measured by the
 success of build integration jobs.
@@
 social aspects, and focus on predicting the success in Travis
-CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
+CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
 an important indicator in the acceptance rate of those commits by the project.
@@
  dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
-
  Other concerns of the study include the possibility that the social factors

### 2017-02-21 Paper/MSRChallenge2017.tex
adjusted the social factors list

--- 2017-02-21 Paper/MSRChallenge2017.tex
@@
 \begin{itemize}
-\item Repositories: number of repositories the developer can access, including those
+\item Number of repositories the developer can access, including those
 the developer owns, contributes
@@
 \footnote{https://developer.github.com/v3/repos/}
-\item Stars: a count of the projects the developer has stared. Starring a project
+\item  Number of projects the developer has stared. Starring a project
 to shows approval of the repository and creates  a bookmark for later 
 access.\footnote{https://help.github.com/articles/about-stars/}
-\item Followers: number of developers that follow the author. 
-\item Following: number of developers that the author follows 
-\item Contributions in the last year: number of contributions made by the author in the last year.
+\item Number of developers that follow the author. 
+\item Number of developers that the author follows .
+\item Number of contributions made by the author in the last year.
 \end{itemize}

### 2017-03-14 Paper/MSRChallenge2017.tex
Submission version
changes to abstract

@@
 \begin{abstract}
-As the software development community continues to make it easier for everyone
-to contribute, the number of commits and pull requests keep increasing. However, this exciting growth
+As the software development community makes it easier for everyone
+to contribute to open source projects, the number of commits and pull requests 	
+keep increasing. However, this exciting growth
 renders it more difficult to only accept quality contributions.
@@
 in predictive power (12\%), core team members are more likely to pass the build
-tests (10\%), and users with 1000 or more follower are more likely to
+tests (10\%), and users with 1000 or more followers are more likely to
 pass the build tests (10\%).

### 2017-03-14 Paper/MSRChallenge2017.tex
quick spelling pass

@@
 \noindent\textbf{Technical Factors} We collected technical factors from the 
-MSR Challenge data set~\cite{msr17challenge}.
+Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
 We extracted only the attributes in the data set that proxy a commit's
@@
 We used the commit hash and the project name in the original data
-set provided by the MSR Challenge~\cite{msr17challenge} to locate thecommit web page
+set provided by the MSR Challenge~\cite{msr17challenge} to locate the
+commit web page
 of the commit, leveraging \textit{github.com}'s URL standard for projects and
@@
 experience.
-We also added one item from the MSR Challenge data set, indiating
+We also added one item from the MSR Challenge data set, indicating
 whether the commit's developer is a core member  
@@
 74.43\% of the builds in the reduced dataset were successful, and thus a naive
-classifer that always guesses ``successful'' would succeed 74.43\% of the time.
+classifier that always guesses ``successful'' would succeed 74.43\% of the time.
 To penalize misclassification for

### 2017-03-14 Paper/MSRChallenge2017.tex
added a related work recommended by reviwers, paper is over the required length now

@@
 \noindent\textbf{Related work:}
+The most similar related work to this paper is a case study investigating how
+social, technical, coordination, and prior-certification factors affect build
+success for a project at IBM Toronto Labs~\cite{Hassan06}.  This work only
+focused on one project and measured experience as the number of contributions to
+that project while our study focuses on a wide range of open source projects and
+measures experience through developers' profile information.
 Similar studies have shown the relationship between both social and technical attributes attributes and 

### 2017-03-14 createWekaData.py

@@ -79,6 +79,7 @@ with open('wekaData.arff','w') as outFile:
             location = location.replace("'",'')
             projectsLastYear = lineItems[8].rstrip()
             if projectsLastYear == '':
+                print(line)
                 projectsLastYear = '?'
             print('{0},{1},{2},{3},{4},{5},{6},{7}'.format(lineItems[0], lineItems[3], lineItems[4], lineItems[5], lineItems[6], location, projectsLastYear, lineItems[2]), file= outFile)
 

### 2017-03-15 Paper/MSRChallenge2017.tex
added a threat to validity requested by reviewers
changed a long sentence into multiple paragraphs

@@
 
-It is also worth noticing that in both cases the Kappa statistic increases when
-adding social data (100\% and 85\% respectively) which represents a more robust
-measure than \textit{correctly classified} instances, since it takes into account the
-correctly guessed instances occurring by chance, and we may also notice that the
-mean absolute error decreases, giving stronger confidence to our claims when
-considering eventual outcomes.
+It is also worth noting that the Kappa statistic increases in both cases when
+adding social data (100\% and 85\% respectively). The Kappa statistic is a more 
+robust measure than \textit{correctly classified} instances, since it takes into account the
+correctly guessed instances occurring by chance. The mean absolute error also
+decreases in both cases, which provides further evidences that social factors
+are important when predicting build success.
 
@@
  distorted the results, and the possibility that unsuccessful builds were due to
- incorrect test cases and not low quality contributions.  Future work will be
- required to investigate the influence of these threats.
+ incorrect test cases and not low quality contributions. Also, the social factors used
+ in this study may not apply to closed source applications, and the factors may
+ only capture a developer's experience with open source projects. Future work 
+ will be required to investigate the influence of these threats.
 

### 2017-03-23 Paper/MSRChallenge2017.tex
added the related work about socio-technical congruence

@@
 social, technical, coordination, and prior-certification factors affect build
-success for a project at IBM Toronto Labs~\cite{Hassan06}.  This work only
+success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
 focused on one project and measured experience as the number of contributions to
@@
 measures experience through developers' profile information.
+Another study investigated the relationship between authors, files in project,
+and team organization when predicting build
+success on an IBM project with 151 developers.  The study found that as the
+number of authors or files in a build increases, the probability of build
+success decreases~\cite{Kwan11}.
 Similar studies have shown the relationship between both social and technical attributes attributes and 

### 2017-03-24 Paper/MSRChallenge2017.tex
added the last recommended related work
added the counts to section B and C along with justification to section C

@@
 number of authors or files in a build increases, the probability of build
-success decreases~\cite{Kwan11}.
+success decreases~\cite{Kwan11}. Another investigation used the same dataset and
+found that team structures affected the teams' build success rate~\cite{Wolf09}.
 Similar studies have shown the relationship between both social and technical attributes attributes and 
@@
 Thus, we use them as a proxy for
-experience.
+experience. If we were unable to find information about an author than we
+assigned the commit empty values for these factors.
 We also added one item from the MSR Challenge data set, indicating
@@
 downsampling.  We found that core team members
-triggered 89.39\% of the builds in the data set and 75.58\% of those builds
-passed.  Non-core team members triggered 10.61\% of the builds in the data set
-and 64.70\% of the builds passed.  This shows that core team members are more
+triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
+(250808/331827) of those builds
+passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
+in the data set
+and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
+members are more
 likely to have a successful build integration than non-core team members.
@@
 followers was more likely to pass the build in the data set without 
-downsampling.  We found that only 0.87\% of the
-contributions in the data set was performed by developers with zero 
+downsampling.  We first investigated whether developers with one or more followers
+were more likely to pass the build than developers without any followers, to
+verify the assumption that followers vouch for a developer's abilities. To
+investigate this question, we removed the commits without author profile
+information (20374 builds which reduced the total build count from 371208 to
+350834). We found 
+that only 0.87\% (3059/350834) of the
+contributions in the data set were performed by developers with zero 
 followers (excluding the developers in which we were not able to extract profile
-information for). We found that 99.13\% of the contributions were performed by
+information for). We found that 99.13\% (347775/350834) of the contributions 
+were performed by
 developers with at least one or more followers.
-Developers with 0 followers had a successful build commit 68.49\%
-of the time.  Developers with one or more followers were successful 74.78\% of
-the time.
+Developers with 0 followers had a successful build commit 68.49\% (2095/3059)
+of the time.  Developers with one or more followers were successful 74.78\%
+(260056/347775) of the time.
 
 We also investigated developers with a large number of followers (1000 or more
-followers).  We found that 6.94\% of the contributions in the data set were
+followers).  We found that 6.94\% (24347/350834) of the contributions in the 
+data set were
 performed by developers with 1000 or more followers.  We found that these
-contributions had a 78.61\% success rate.  These results show that developers
+contributions had a 78.61\% (19138/24347) success rate.  These results show 
+developers
 with more followers are more likely to have a successful integration build.

### 2017-03-24 Paper/MSRChallenge2017.tex
slight rewording of related work to make it more accurate
Adding authors

@@
 \\}
+%\\     
+%}
+%\\      
+%}
+%\\    
+%
 
@@
 % 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+\author{\IEEEauthorblockN{Zack Coker,
+Mauricio Soto and
+Claire Le Goues}
+\IEEEauthorblockA{School of Computer Science\\
+Carnegie Mellon University,
+Pittsburgh PA\\ 
+zfc@cs.cmu.edu, mauriciosoto@cmu.edu, clegoues@cs.cmu.edu}
+}
 
@@
 number of authors or files in a build increases, the probability of build
-success decreases~\cite{Kwan11}. Another investigation used the same dataset and
+success decreases~\cite{Kwan11}. Another investigation used a dataset from the
+same project and
 found that team structures affected the teams' build success rate~\cite{Wolf09}.

### 2017-03-24 Paper/MSRChallenge2017.tex
Adding authors

@@
 
-\vspace{1ex}
-\noindent\textbf{Related work:}
-The most similar related work to this paper is a case study investigating how
-social, technical, coordination, and prior-certification factors affect build
-success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
-focused on one project and measured experience as the number of contributions to
-that project while our study focuses on a wide range of open source projects and
-measures experience through developers' profile information.
-Another study investigated the relationship between authors, files in project,
-and team organization when predicting build
-success on an IBM project with 151 developers.  The study found that as the
-number of authors or files in a build increases, the probability of build
-success decreases~\cite{Kwan11}. Another investigation used a dataset from the
-same project and
-found that team structures affected the teams' build success rate~\cite{Wolf09}.
-Similar studies have shown the relationship between both social and technical attributes attributes and 
-different measures of success: pull request acceptance~\cite{gousios14, 
-gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
-Tsay et al.~\cite{tsay14icse} 
-show that the social connection between the developer initiating a
-pull request and the project integrators is a key factor in predicting 
-acceptance of a pull 
-request. Unlike this previous study, in our study, we look at a broader aspect of 
-social aspects, and focus on predicting the success in Travis
-CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
-an important indicator in the acceptance rate of those commits by the project.
-Also, the inclusion of test cases with a commit has been shown to increase the
-commit's acceptance rate~\cite{gousios15}.
-Bettenburgh et 
-al.~\cite{bettenburgh10} discuss the impact of social interactions with 
-post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
-project characteristics (programming language, project age, etc.) affect commit 
-success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
-analyze the impact of CI usage in GitHub and its correlation with software 
-quality. By contrast, we focus on the relationship between independent social 
-attributes and continuous integration success.
-
 \section{Research Design}
@@
 
+\section{Related work:}
+The most similar related work to this paper is a case study investigating how
+social, technical, coordination, and prior-certification factors affect build
+success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
+focused on one project and measured experience as the number of contributions to
+that project while our study focuses on a wide range of open source projects and
+measures experience through developers' profile information.
+Another study investigated the relationship between authors, files in project,
+and team organization when predicting build
+success on an IBM project with 151 developers.  The study found that as the
+number of authors or files in a build increases, the probability of build
+success decreases~\cite{Kwan11}. Another investigation used a dataset from the
+same project and
+found that team structures affected the teams' build success rate~\cite{Wolf09}.
+Similar studies have shown the relationship between both social and technical attributes attributes and 
+different measures of success: pull request acceptance~\cite{gousios14, 
+gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
+Tsay et al.~\cite{tsay14icse} 
+show that the social connection between the developer initiating a
+pull request and the project integrators is a key factor in predicting 
+acceptance of a pull 
+request. Unlike this previous study, in our study, we look at a broader aspect of 
+social aspects, and focus on predicting the success in Travis
+CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
+an important indicator in the acceptance rate of those commits by the project.
+Also, the inclusion of test cases with a commit has been shown to increase the
+commit's acceptance rate~\cite{gousios15}.
+Bettenburgh et 
+al.~\cite{bettenburgh10} discuss the impact of social interactions with 
+post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
+project characteristics (programming language, project age, etc.) affect commit 
+success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
+analyze the impact of CI usage in GitHub and its correlation with software 
+quality. By contrast, we focus on the relationship between independent social 
+attributes and continuous integration success.
+
 \section{Conclusion}

### 2017-03-24 Paper/MSRChallenge2017.tex
hanged author order based on Claire's response

@@
 % 
-\author{\IEEEauthorblockN{Zack Coker,
-Mauricio Soto and
+\author{\IEEEauthorblockN{
+Mauricio Soto, Zack Coker, and
 Claire Le Goues}
@@
 Pittsburgh PA\\ 
-zfc@cs.cmu.edu, mauriciosoto@cmu.edu, clegoues@cs.cmu.edu}
+mauriciosoto@cmu.edu, zfc@cs.cmu.edu, clegoues@cs.cmu.edu}
 }

### 2017-03-25 Paper/MSRChallenge2017.tex
several todos addressed

--- 2017-03-24 Paper/MSRChallenge2017.tex
@@
 from the GitHub profiles of developers,
-allow for more accurate predictions than only using technical data?}
+allow for more accurate predictions of 
+the developer's build success
+than only using technical data?}
 
@@
 whether the commit's developer is a core member  
-of the associated project.
+of the associated project. These values were investigated to understand and be able to quantify the developers’ experience.
 
@@
 sub-sampling the successful builds until the two build status were
-equal, a process known as downsampling.  We train and present results for both
-data sets individually.
-\section{Evaluation}
+equal, a process known as downsampling.
+We downsampled the entire dataset being analyzed and then performed cross-validation on it.
+Since the cross-validation is stratified, the proportion of 50-50 is maintained through the training and testing folds.
+We train and present results for both
+data sets individually in Sections \ref{eval}A, \ref{eval}B and \ref{eval}C.
+\section{Evaluation} \label{eval}
 \begin{table*}[ht]

### 2017-03-25 Paper/MSRChallenge2017.tex
addressed some other todos

--- 2017-03-25 Paper/MSRChallenge2017.tex
@@
 established  and interpretable.
+In particular, we use a J48 decision tree because this classification mechanism has the ability to identify the attributes that discriminate the various instances most clearly, and we are interested in analyzing what particular features can predict with higher accuracy build success.
 We first build a
@@
 It is also worth noting that the Kappa statistic increases in both cases when
-adding social data (100\% and 85\% respectively). The Kappa statistic is a more 
+adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
 robust measure than \textit{correctly classified} instances, since it takes into account the
@@
 likely to have a successful build integration than non-core team members.
+We hypothesize the reason for this to be that core team members are more familiar with the code, therefore are more likely to have their builds pass.
 
@@
 developers
-with more followers are more likely to have a successful integration build.
+with more followers are more likely to have a successful integration build. Reasons for this might be
 

### 2017-03-25 Paper/MSRChallenge2017.tex
adjusted the title and authors

@@
 
-\title{Analyzing the impact of social attributes on commit integration success}
+\title{Analyzing the Impact of Social Attributes on Commit Integration Success}
 %Or some better name, Zack can probably think of a better one, he is good with names

### 2017-03-25 Paper/MSRChallenge2017.tex
added numbers to the table and performed a pass through the paper to check for typos

@@
 
-\begin{comment}
-we have created a dataset with technical attributes to be able to analyze the 
-predictive power of these attributes and its relationship with commit integration 
-success. This way, we are able to create a model
-We are afterwards interested in knowing if adding social attributes to this 
-predictability model will increase the probability of the model asserting 
-correctly future instances by knowing not only technical data about the commit 
-being pushed but also social attributes of the developer pushing the changes.
-\end{comment}
-
 \vspace{1ex}
@@
 \hline
-\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\
+	\textbf{Correctly Classified Instances}&  285882 (77.01\%) & 301068
+	(81.10\%)  & 121694 (64.10\%) & 144441 (76.09\%)\\
 
-\textbf{Incorrectly Classified Instances}&  22.99\% & 18.90\% & 35.90\% & 23.91\%\\
+	\textbf{Incorrectly Classified Instances}&  85326 (22.99\%) & 70140
+	(18.90\%) & 68147 (35.90\%) &  45400 (23.91\%)\\
 
@@
  scripts to obtain the developer social data are publicly available to facilitate 
- the transparency and quality of the process (Will be available after double blind review).%\footnote{https://goo.gl/CqTX44}
+ the transparency and quality of the process\footnote{https://goo.gl/CqTX44}.
 
@@
 
-\section{Related work:}
+\section{Related work}
 The most similar related work to this paper is a case study investigating how
@@
 number of authors or files in a build increases, the probability of build
-success decreases~\cite{Kwan11}. Another investigation used a dataset from the
+success decreases~\cite{Kwan11}. A separate investigation used a dataset from the
 same project and
@@
 analyze the impact of CI usage in GitHub and its correlation with software 
-quality. By contrast, we focus on the relationship between independent social 
+quality. By contrast with their work, we focus on the relationship between independent social 
 attributes and continuous integration success.

### 2017-03-25 Paper/MSRChallenge2017.tex
changed incorrect sentence

@@
 In particular, we analyzed contributions in the 
-context of continuous integration, using the technical factors and one social
-factor found in the challenge
-corpus~\cite{msr17challenge}, and the social factors found on a developer's
-GitHub profile.  We used the technical factors to estimate the complexity of the
-commit, and the social factors to estimate the developer's experience.
-Overall, our study investigates how well different technical and social factors predict
+context of continuous integration, using technical factors and one social
+factor from the challenge
+corpus~\cite{msr17challenge}, and social factors from a developer's
+GitHub profile.  We used the technical factors to estimate the commit's
+complexity, and the social factors to estimate the developer's experience.
+Overall, our study investigates how different technical and social factors predict
 contribution quality. This information can help core team members prioritize project
@@
 We find that social factors are an important aspect of build success but
-these factors alone do not fully predict if a contribution will be successfully 
-integrated into the project. We find
+these factors alone do not fully predict whether a contribution will be successfully 
+pass the build tests. We find
 that core team members are more likely to achieve build success than non-core
@@
 (files added, files modified, etc.)
-when predicting the likelihood a developer's commit
-to be considered successfully integrated in the project. We define successful
-integration as passing the continuous integration build tests in the project.
+when predicting the likelihood that a developer's commit
+will pass the continuous integration build tests for the project.
 
@@
 social factors, used as a proxy for experience, can be used to predict
-a different success measure: commit integration success, therefore giving
-developers and integrators another tool to be able to identify the quality
-of a contribution performed by a particular developer.
+commit integration success. If so, 
+developers and integrators will have another tool to estimate the quality
+of a developer's contribution.
 %
-Our main research question, upon which we can build by investigating particular attributes, is:
+Our main research question is:
 
 \textbf{Do social attributes, gathered 
-from the GitHub profiles of developers,
+from developers' GitHub profiles ,
 allow for more accurate predictions of 
 the developer's build success
-than only using technical data?}
+than only technical attributes?}
+
+If social attributes improve the prediction of build success, then we are
+interested in investigating how certain attributes, such as the developer's
+follower count, correlates with build success.
 
 \vspace{1ex}
-\noindent\textbf{Metric.} We measure quality software contributions based on the build status of the
+\noindent\textbf{Metric.} We measure quality software contributions based on the
+build status of the
 commit. We used a decision tree classifier~\cite{Quinlan86} to identify
 important factors in predicting build success;  decision tress are well
-established  and interpretable.
-In particular, we use a J48 decision tree because this classification mechanism has the ability to identify the attributes that discriminate the various instances most clearly, and we are interested in analyzing what particular features can predict with higher accuracy build success.
+established and interpretable. In particular, we use a J48 decision tree because
+this classifier has the ability to identify which attributes 
+discriminate the various instances most clearly, and we are interested in
+analyzing which features can be used to predict build success.
 We first build a
-decision tree classifier using only technical factors, which highlights
-the degree to which commit complexity predicts build integration
-success.  We then added the social factors to identify the degree to which they
-add predictive power to a the initial technical model. 
-We use 10-fold cross validation across our evaluation.
+decision tree classifier using only technical factors to determine
+how well commit complexity predicts build integration
+success.  We then include the social factors in the classification problem to 
+identify the degree to which the social factors improve the model's predictive
+power.
+We evaluate the models with 10-fold cross-validation.
 
@@
 \vspace{1ex}
-\noindent\textbf{Technical Factors} We collected technical factors from the 
+\noindent\textbf{Technical Factors.} We collected technical factors from the 
 Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
@@
 \begin{itemize}
-\item Number of repositories the developer can access, including those
+	\item Number of repositories the developer can access (including those
 the developer owns, contributes
-to, and for which the developer has organizational membership access.%
+		to, and for which the developer has organizational membership
+		access).%
 \footnote{https://developer.github.com/v3/repos/}
@@
 \item Number of developers that follow the author. 
-\item Number of developers that the author follows .
+\item Number of developers that the author follows.
 \item Number of contributions made by the author in the last year.
@@
 Thus, we use them as a proxy for
-experience. If we were unable to find information about an author than we
+experience. If we were unable to find information about an author, then we
 assigned the commit empty values for these factors.
@@
 whether the commit's developer is a core member  
-of the associated project. These values were investigated to understand and be able to quantify the developers’ experience.
+of the associated project. These values were investigated to estimate developers’ experience.
 
@@
 
-Our data set~\cite{msr17challenge} consists
+The challenge dataset~\cite{msr17challenge} consists
 of commits that date as far back as 2011. The social data we 
-gather is recent, gathered in January 2017. To mitigate the threat of
+gathered is accurate for January 2017. To mitigate the threat of
 using future results to predict previous events,
 we removed only include data set commits from the years 2014--2016.  Our intuition is
-that the social attributes are less likely to have substantively changed more recently.
+that these social attributes are unlikely to have significant recent changes.
 
@@
 converted all Travis build statuses to two possible values:
-\emph{successful} (passed in the original provided data set) and \emph{unsuccessful}
+\emph{successful} (passed in the challenge dataset~\cite{msr17challenge}) and \emph{unsuccessful}
 (errored, failed, canceled
-and started in the original data set). We also condensed down all passing and
+and started in the original data set). We also condensed all passing and
 failing builds in a commit to a single pass or fail for each build status.  If
-the commit contained both passing and failing build statuses, we treat it as a failed build.
+the commit contained both passing and failing build statuses, we treat it as
+both a passing and failed build.
 
@@
 sub-sampling the successful builds until the two build status were
-equal, a process known as downsampling.
-We downsampled the entire dataset being analyzed and then performed cross-validation on it.
-Since the cross-validation is stratified, the proportion of 50-50 is maintained through the training and testing folds.
-We train and present results for both
-data sets individually in Sections \ref{eval}A, \ref{eval}B and \ref{eval}C.
+equal, through a process known as downsampling. We downsampled the entire
+dataset and then trained decision tree classifiers.  We validated the
+classifiers with cross-validation. Since the cross-validation is stratified, the
+proportion of 50-50 is maintained through the training and testing folds for the
+downsampled data. We present results for both
+datasets in Section \ref{eval}A,  and only the full dataset for Sections \ref{eval}B and \ref{eval}C.
+
 \section{Evaluation} \label{eval}
@@
 	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
-    cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column). 
+    cross-validation of two decision trees with a non-downsampled dataset
+	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled
+	(4\textsuperscript{th} and 5\textsuperscript{th} column). 
 	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
@@
 In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
-with default settings. The decision trees were evaluated using 10-fold cross 
-validation with the data in each data set.
+with default settings. The decision trees were evaluated using 10-fold 
+cross-validation with the data in each data set.
 
@@
  After including the social data
-in the data set, the classifier correctly predicted 76.09\% of the data set,
+in the dataset, the classifier correctly predicted 76.09\% of the data set,
 about a 12\% improvement from only the technical data.  These results show that
@@
 
-Based on the decision tree results, we noticed that core team members where
+Based on the decision tree results, we noticed that core team members were
 important when classifying build success, so we decided to investigate if core
@@
 contributions in the data set were performed by developers with zero 
-followers (excluding the developers in which we were not able to extract profile
-information for). We found that 99.13\% (347775/350834) of the contributions 
+followers. We found that 99.13\% (347775/350834) of the contributions 
 were performed by
@@
 developers
-with more followers are more likely to have a successful integration build. Reasons for this might be
+with more followers are more likely to have a successful integration build.
+These
+result may be due to the fact that developers with followers are more likely to
+have open source development experience, and the developers' experience
+influenced the build success rate..
 
@@
 
-Overall, we have found that social attributes which proxy experience, such if
-the developer is a core contributor for the project, produce a 
+Overall, we have found that social attributes which proxy experience, such as if
+the developer is a core project contributor , produce a 
 noticeable increase in predicting build success.  While the increase was noticeable 
 with the full data set, there was a much greater increase in prediction
-accuracy after performing downsampling. These results show that social factors
-as the ones studied in this paper are significant predictors when
+accuracy after performing downsampling. These results show that social factors,
+such 
+as the ones studied in this paper, are significant predictors when
 evaluating the predictive power of build commit success.
@@
 more likely to have the build integration pass than non-core team members.  This
-result provides evidence that non-core team member commit are not thoroughly
-scrutinized, although further studied will be required to draw definite
+result provides evidence that non-core team member commits are not as
+scrutinized as core team member commits before the integration build tests, although further studied will be required to draw definite
 conclusions.
@@
 Developers with over 1000 followers had more than a 10\% increase compared to
-developers with no followers.  This shows that higher quality developers are more
+developers with no followers.  This shows that higher quality open source developers are more
 likely to have a large number of followers.
@@
 
- The scripts we have created to adapt and extract the datasets we needed, and the 
- scripts to obtain the developer social data are publicly available to facilitate 
- the transparency and quality of the process\footnote{https://goo.gl/CqTX44}.
+ The scripts we have created to create the datasets and the 
+ scripts to obtain the developer social data are publicly available 
+ \footnote{https://goo.gl/CqTX44}.
 
@@
 focused on one project and measured experience as the number of contributions to
-that project while our study focuses on a wide range of open source projects and
+the project while our study focuses on a wide range of open source projects and
 measures experience through developers' profile information.

### 2017-03-27 Paper/MSRChallenge2017.tex
slightly shorter intro

@@
 requests which must be approved by a core team member~\cite{gousios14}. 
-These methods can become a bottleneck, and thus it is beneficial to prioritize certain
-contributions.  This prioritization can be achieved with predictors of a
-contribution's quality.
+This can become a bottleneck, and thus it is beneficial to prioritize certain
+contributions, ideally by predicted quality.
 
-The decision to include code in
-a project has been described as a meritocracy, where only the code is a factor
+Ideally, the decision to include code in
+a project is meritocratic, such that only the code is a factor
 in the decision~\cite{Scacchi07}.
@@
 By contrast,  we are interested in analyzing the quality 
-of a contribution in the context of continuous integration.  While pull requests
+of a contribution in the context of \emph{continuous integration}.  While pull request
 quality is determined through manual inspection, continuous integration quality
@@
 quality determination differently.
-We investigate the factors involved in continuous integration build success.
+We investigate the factors related to continuous integration build success.
 In this study, we analyze a large set of technical and social attributes 
@@
 
-In particular, we analyzed contributions in the 
-context of continuous integration, using technical factors and one social
+We analyzed contributions in the 
+context of continuous integration using technical factors and one social
 factor from the challenge
@@
 contribution quality. This information can help core team members prioritize project
-contributions, and will also provide a further understand of quality enforcement
-in the software development process.
+contributions, and increases understanding of quality enforcement
+in software development.
 
-We find that social factors are an important aspect of build success but
-these factors alone do not fully predict whether a contribution will be successfully 
-pass the build tests. We find
+We find that social factors are an important aspect of build success ,
+do not fully predict whether a contribution will 
+pass all build tests;
 that core team members are more likely to achieve build success than non-core
-members, and that developers with more followers are more likely to submit commits that pass the
+members; and that developers with more followers are more likely to submit commits that pass the
 continuous integration build.

### 2017-03-27 Paper/MSRChallenge2017.tex
shorter through midway through section III

@@
 We present the approach taken to guide this study by
-following the Goal-Question-Metric (GQM) methodology described by Basili et 
-al.~\cite{Basili84}.
+following the Goal-Question-Metric (GQM) methodology~\cite{Basili84}:
 
@@
 \noindent\textbf{Goal.}
-The goal of this study is to identify and understand the relationship 
+The \emph{goal} of this study is to identify and understand the relationship 
 between the social factors that describe the
 developer's experience (stars, followers, etc.) and technical properties that
-describe the commit's complexity
+describe a commit's complexity
 (files added, files modified, etc.)
@@
 
-\textbf{Do social attributes, gathered 
-from developers' GitHub profiles ,
-allow for more accurate predictions of 
-the developer's build success
-than only technical attributes?}
+\vspace{1ex}
+\noindent \emph{Do social attributes, gathered from developers' GitHub profiles, allow for
+  more accurate predictions of the developer's build success than only technical
+  attributes?}
 
-If social attributes improve the prediction of build success, then we are
-interested in investigating how certain attributes, such as the developer's
-follower count, correlates with build success.
+If social attributes improve build success predication, we are
+interested in investigating how particular attributes, such as the developer's
+follower count, similarly correlate with success.
 
 \vspace{1ex}
-\noindent\textbf{Metric.} We measure quality software contributions based on the
+\noindent\textbf{Metric.} We measure software contribution quality by the
 build status of the
 commit. We used a decision tree classifier~\cite{Quinlan86} to identify
-important factors in predicting build success;  decision tress are well
-established and interpretable. In particular, we use a J48 decision tree because
-this classifier has the ability to identify which attributes 
-discriminate the various instances most clearly, and we are interested in
-analyzing which features can be used to predict build success.
+important factors in predicting build success;  decision trees are well
+established and interpretable. We use a J48 decision tree, which
+has the ability to identify which attributes 
+discriminate the various instances most clearly.
 We first build a
-decision tree classifier using only technical factors to determine
-how well commit complexity predicts build integration
-success.  We then include the social factors in the classification problem to 
+decision tree classifier using only technical factors to 
+predict build integration
+success.  We then include the social factors, to 
 identify the degree to which the social factors improve the model's predictive
@@
 Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
-We extracted only the attributes in the data set that proxy a commit's
-complexity, such as commit size. 
-The technical factors used are:
+We extracted the following techical attributes as proxy to a commit's
+complexity: 
 \begin{itemize}
@@
 \item Total source files in project at the time of the commit.
-\item Source lines of source code in the project at
+\item Number of source lines of code in the project at
 	the time of the commit.
@@
 from developer's profiles.
-We used the commit hash and the project name in the original data
-set provided by the MSR Challenge~\cite{msr17challenge} to locate the
-commit web page
-of the commit, leveraging \textit{github.com}'s URL standard for projects and
+We used the commit hash and the project name in the 
+MSR Challenge~\cite{msr17challenge} dataset to locate the
+commit web page, leveraging \textit{github.com}'s URL standard for projects and
 commit hashes.
@@
 We scraped the commit author's
-\textit{username} from each commit page, and then
-collected the following from the user's public profile:
+\textit{username} from each commit page to
+collect the following from the user's public profile:
 %(\textit{https://github.com/\textbf{UserName}}). 
@@
 	\item Number of repositories the developer can access (including those
-the developer owns, contributes
-		to, and for which the developer has organizational membership
-		access).%
+the developer owns, contributes to, or for which they have
+organizational membership access).%
 \footnote{https://developer.github.com/v3/repos/}
@@
 \item Number of developers that the author follows.
-\item Number of contributions made by the author in the last year.
+\item Number of contributions made in the last year.
 \end{itemize}
@@
 \center
-	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
-    cross-validation of two decision trees with a non-downsampled dataset
+	\caption{\label{resultsTable} Predictive power 
+      decision trees with a non-downsampled dataset
 	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled

### 2017-03-27 Paper/MSRChallenge2017.tex
tightening through top of eval, and fixing the labels

@@
 
-These social factors are all factors that are tied to a GitHub user's profile
-and that are generally correlated with user time and engagement with the site.
-Thus, we use them as a proxy for
-experience. If we were unable to find information about an author, then we
-assigned the commit empty values for these factors.
 We also added one item from the MSR Challenge data set, indicating
 whether the commit's developer is a core member  
-of the associated project. These values were investigated to estimate developers’ experience.
+of the associated project.
+These social factors are all tied to a GitHub user's profile,
+and are generally correlated with user time and engagement with the site.
+Thus, we use them as a proxy for
+experience.  If we were unable to find information about an author, we
+assigned empty values to the commit.
 
@@
 using future results to predict previous events,
-we removed only include data set commits from the years 2014--2016.  Our intuition is
+we only include commits from the years 2014--2016.  Our intuition is
 that these social attributes are unlikely to have significant recent changes.
 
-Since we are interested in the success of the job status of each contribution, we 
-converted all Travis build statuses to two possible values:
-\emph{successful} (passed in the challenge dataset~\cite{msr17challenge}) and \emph{unsuccessful}
+We converted all Travis build statuses to two possible values:
+\emph{successful} (passed in the challenge dataset) and \emph{unsuccessful}
 (errored, failed, canceled
-and started in the original data set). We also condensed all passing and
+or started in the original data set). We also condensed all passing and
 failing builds in a commit to a single pass or fail for each build status.  If
@@
 To penalize misclassification for
-both classes equally, we created a second balanced dataset by randomly 
+both classes equally, we created a second \emph{balanced} dataset by randomly 
 sub-sampling the successful builds until the two build status were
 equal, through a process known as downsampling. We downsampled the entire
-dataset and then trained decision tree classifiers.  We validated the
+dataset and then trained decision tree classifiers on both.  We validated the
 classifiers with cross-validation. Since the cross-validation is stratified, the
@@
 downsampled data. We present results for both
-datasets in Section \ref{eval}A,  and only the full dataset for Sections \ref{eval}B and \ref{eval}C.
+datasets in Section~\ref{sec:successClassification},  and only the full dataset for Sections~\ref{sec:core} and \ref{sec:followerSuccess}.
 

### 2017-03-27 Paper/MSRChallenge2017.tex
adding other success measures

--- 2017-03-27 Paper/MSRChallenge2017.tex
@@
 requests which must be approved by a core team member~\cite{gousios14}. 
-This can become a bottleneck, and thus it is beneficial to prioritize certain
-contributions, ideally by predicted quality.
+These methods can become a bottleneck, and thus it is beneficial to prioritize certain
+contributions.  This prioritization can be achieved with predictors of a
+contribution's quality.
 
-Ideally, the decision to include code in
-a project is meritocratic, such that only the code is a factor
+The decision to include code in
+a project has been described as a meritocracy, where only the code is a factor
 in the decision~\cite{Scacchi07}.
@@
 By contrast,  we are interested in analyzing the quality 
-of a contribution in the context of \emph{continuous integration}.  While pull request
+of a contribution in the context of continuous integration.  While pull requests
 quality is determined through manual inspection, continuous integration quality
@@
 quality determination differently.
-We investigate the factors related to continuous integration build success.
+We investigate the factors involved in continuous integration build success.
 In this study, we analyze a large set of technical and social attributes 
@@
 
-We analyzed contributions in the 
-context of continuous integration using technical factors and one social
-factor from the challenge
-corpus~\cite{msr17challenge}, and social factors from a developer's
-GitHub profile.  We used the technical factors to estimate the commit's
-complexity, and the social factors to estimate the developer's experience.
-Overall, our study investigates how different technical and social factors predict
+In particular, we analyzed contributions in the 
+context of continuous integration, using the technical factors and one social
+factor found in the challenge
+corpus~\cite{msr17challenge}, and the social factors found on a developer's
+GitHub profile.  We used the technical factors to estimate the complexity of the
+commit, and the social factors to estimate the developer's experience.
+Overall, our study investigates how well different technical and social factors predict
 contribution quality. This information can help core team members prioritize project
-contributions, and increases understanding of quality enforcement
-in software development.
+contributions, and will also provide a further understand of quality enforcement
+in the software development process.
 
-We find that social factors are an important aspect of build success ,
-do not fully predict whether a contribution will 
-pass all build tests;
+We find that social factors are an important aspect of build success but
+these factors alone do not fully predict if a contribution will be successfully 
+integrated into the project. We find
 that core team members are more likely to achieve build success than non-core
-members; and that developers with more followers are more likely to submit commits that pass the
+members, and that developers with more followers are more likely to submit commits that pass the
 continuous integration build.
@@
 (files added, files modified, etc.)
-when predicting the likelihood that a developer's commit
-will pass the continuous integration build tests for the project.
+when predicting the likelihood a developer's commit
+to be considered successfully integrated in the project. We define successful
+integration as passing the continuous integration build tests in the project.
 
@@
 social factors, used as a proxy for experience, can be used to predict
-commit integration success. If so, 
-developers and integrators will have another tool to estimate the quality
-of a developer's contribution.
+a different success measure: commit integration success, therefore giving
+developers and integrators another tool to be able to identify the quality
+of a contribution performed by a particular developer.
 %
-Our main research question is:
+Our main research question, upon which we can build by investigating particular attributes, is:
 
 \textbf{Do social attributes, gathered 
-from developers' GitHub profiles ,
+from the GitHub profiles of developers,
 allow for more accurate predictions of 
 the developer's build success
-than only technical attributes?}
-
-If social attributes improve the prediction of build success, then we are
-interested in investigating how certain attributes, such as the developer's
-follower count, correlates with build success.
+than only using technical data?}
 
 \vspace{1ex}
-\noindent\textbf{Metric.} We measure quality software contributions based on the
-build status of the
+\noindent\textbf{Metric.} We measure quality software contributions based on the build status of the
 commit. We used a decision tree classifier~\cite{Quinlan86} to identify
 important factors in predicting build success;  decision tress are well
-established and interpretable. In particular, we use a J48 decision tree because
-this classifier has the ability to identify which attributes 
-discriminate the various instances most clearly, and we are interested in
-analyzing which features can be used to predict build success.
+established  and interpretable.
+In particular, we use a J48 decision tree because this classification mechanism has the ability to identify the attributes that discriminate the various instances most clearly, and we are interested in analyzing what particular features can predict with higher accuracy build success.
 We first build a
-decision tree classifier using only technical factors to determine
-how well commit complexity predicts build integration
-success.  We then include the social factors in the classification problem to 
-identify the degree to which the social factors improve the model's predictive
-power.
-We evaluate the models with 10-fold cross-validation.
+decision tree classifier using only technical factors, which highlights
+the degree to which commit complexity predicts build integration
+success.  We then added the social factors to identify the degree to which they
+add predictive power to a the initial technical model. 
+We use 10-fold cross validation across our evaluation.
 
@@
 \vspace{1ex}
-\noindent\textbf{Technical Factors.} We collected technical factors from the 
+\noindent\textbf{Technical Factors} We collected technical factors from the 
 Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
@@
 \begin{itemize}
-	\item Number of repositories the developer can access (including those
+\item Number of repositories the developer can access, including those
 the developer owns, contributes
-		to, and for which the developer has organizational membership
-		access).%
+to, and for which the developer has organizational membership access.%
 \footnote{https://developer.github.com/v3/repos/}
@@
 \item Number of developers that follow the author. 
-\item Number of developers that the author follows.
+\item Number of developers that the author follows .
 \item Number of contributions made by the author in the last year.
@@
 Thus, we use them as a proxy for
-experience. If we were unable to find information about an author, then we
+experience. If we were unable to find information about an author than we
 assigned the commit empty values for these factors.
@@
 whether the commit's developer is a core member  
-of the associated project. These values were investigated to estimate developers’ experience.
+of the associated project. These values were investigated to understand and be able to quantify the developers’ experience.
 
@@
 
-The challenge dataset~\cite{msr17challenge} consists
+Our data set~\cite{msr17challenge} consists
 of commits that date as far back as 2011. The social data we 
-gathered is accurate for January 2017. To mitigate the threat of
+gather is recent, gathered in January 2017. To mitigate the threat of
 using future results to predict previous events,
 we removed only include data set commits from the years 2014--2016.  Our intuition is
-that these social attributes are unlikely to have significant recent changes.
+that the social attributes are less likely to have substantively changed more recently.
 
@@
 converted all Travis build statuses to two possible values:
-\emph{successful} (passed in the challenge dataset~\cite{msr17challenge}) and \emph{unsuccessful}
+\emph{successful} (passed in the original provided data set) and \emph{unsuccessful}
 (errored, failed, canceled
-and started in the original data set). We also condensed all passing and
+and started in the original data set). We also condensed down all passing and
 failing builds in a commit to a single pass or fail for each build status.  If
-the commit contained both passing and failing build statuses, we treat it as
-both a passing and failed build.
+the commit contained both passing and failing build statuses, we treat it as a failed build.
 
@@
 sub-sampling the successful builds until the two build status were
-equal, through a process known as downsampling. We downsampled the entire
-dataset and then trained decision tree classifiers.  We validated the
-classifiers with cross-validation. Since the cross-validation is stratified, the
-proportion of 50-50 is maintained through the training and testing folds for the
-downsampled data. We present results for both
-datasets in Section \ref{eval}A,  and only the full dataset for Sections \ref{eval}B and \ref{eval}C.
-
+equal, a process known as downsampling.
+We downsampled the entire dataset being analyzed and then performed cross-validation on it.
+Since the cross-validation is stratified, the proportion of 50-50 is maintained through the training and testing folds.
+We train and present results for both
+data sets individually in Sections \ref{eval}A, \ref{eval}B and \ref{eval}C.
 \section{Evaluation} \label{eval}
@@
 \textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\
+\textbf{Avg Precision}& 0.75 & 0.80  & 0.65  & 0.76 \\
+\textbf{Avg Recall}& 0.77 & 0.81 & 0.64 & 0.76 \\
+\textbf{Avg F-Measure}& 0.72 & 0.79  & 0.63  & 0.76 \\
 
@@
 	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
-    cross-validation of two decision trees with a non-downsampled dataset
-	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled
-	(4\textsuperscript{th} and 5\textsuperscript{th} column). 
+    cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column). 
 	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
@@
 In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
-with default settings. The decision trees were evaluated using 10-fold 
-cross-validation with the data in each data set.
+with default settings. The decision trees were evaluated using 10-fold cross 
+validation with the data in each data set.
 
@@
  After including the social data
-in the dataset, the classifier correctly predicted 76.09\% of the data set,
+in the data set, the classifier correctly predicted 76.09\% of the data set,
 about a 12\% improvement from only the technical data.  These results show that
@@
 robust measure than \textit{correctly classified} instances, since it takes into account the
-correctly guessed instances occurring by chance. The mean absolute error also
+correctly guessed instances occurring by chance.
+The precision, recall and F-measure are calculated over the successful and unsuccessful classes and then averaged (standard procedure in Weka).
+Precision and recall are calculated as follows:
+
+\begingroup
+    \fontsize{9pt}{12pt}\selectfont
+Precision = True Positives / (True Positives + False Positives)\
+
+Recall = True Positives / (True Positives + False Negatives)
+\endgroup
+
+F-score is a correlation of these two values.
+We can see that all these measures increase when we add social data into the feature space, making the prediction more reliable.
+Besides this, the mean absolute error
 decreases in both cases, which provides further evidences that social factors
@@
 
-Based on the decision tree results, we noticed that core team members were
+Based on the decision tree results, we noticed that core team members where
 important when classifying build success, so we decided to investigate if core
@@
 contributions in the data set were performed by developers with zero 
-followers. We found that 99.13\% (347775/350834) of the contributions 
+followers (excluding the developers in which we were not able to extract profile
+information for). We found that 99.13\% (347775/350834) of the contributions 
 were performed by
@@
 developers
-with more followers are more likely to have a successful integration build.
-These
-result may be due to the fact that developers with followers are more likely to
-have open source development experience, and the developers' experience
-influenced the build success rate..
+with more followers are more likely to have a successful integration build. Reasons for this might be
 
@@
 
-Overall, we have found that social attributes which proxy experience, such as if
-the developer is a core project contributor , produce a 
+Overall, we have found that social attributes which proxy experience, such if
+the developer is a core contributor for the project, produce a 
 noticeable increase in predicting build success.  While the increase was noticeable 
 with the full data set, there was a much greater increase in prediction
-accuracy after performing downsampling. These results show that social factors,
-such 
-as the ones studied in this paper, are significant predictors when
+accuracy after performing downsampling. These results show that social factors
+as the ones studied in this paper are significant predictors when
 evaluating the predictive power of build commit success.
@@
 more likely to have the build integration pass than non-core team members.  This
-result provides evidence that non-core team member commits are not as
-scrutinized as core team member commits before the integration build tests, although further studied will be required to draw definite
+result provides evidence that non-core team member commit are not thoroughly
+scrutinized, although further studied will be required to draw definite
 conclusions.
@@
 Developers with over 1000 followers had more than a 10\% increase compared to
-developers with no followers.  This shows that higher quality open source developers are more
+developers with no followers.  This shows that higher quality developers are more
 likely to have a large number of followers.
@@
 
- The scripts we have created to create the datasets and the 
- scripts to obtain the developer social data are publicly available 
- \footnote{https://goo.gl/CqTX44}.
+ The scripts we have created to adapt and extract the datasets we needed, and the 
+ scripts to obtain the developer social data are publicly available to facilitate 
+ the transparency and quality of the process\footnote{https://goo.gl/CqTX44}.
 
@@
 focused on one project and measured experience as the number of contributions to
-the project while our study focuses on a wide range of open source projects and
+that project while our study focuses on a wide range of open source projects and
 measures experience through developers' profile information.

### 2017-03-27 Paper/MSRChallenge2017.tex
edits through end of eval

--- 2017-03-27 Paper/MSRChallenge2017.tex
@@
 \usepackage{verbatim}
+\usepackage{balance}
 \newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
@@
 commit. We used a decision tree classifier~\cite{Quinlan86} to identify
-important factors in predicting build success;  decision trees are well
+important factors in predicting build success. Decision trees are a predictive model which uses binary decisions on the
+attributes to predict a final class. They are well
 established and interpretable. We use a J48 decision tree, which
@@
 \end{table*}
-To address our main research question: ``Do social attributes, gathered 
+
+We created decision tree classifiers~\cite{Quinlan86} to address our main research question: ``Do social attributes, gathered 
 from the GitHub profiles of developers,
-allow for more accurate predictions than only using technical data?", we 
-created a decision tree classifier~\cite{Quinlan86}.
-Decision trees are a predictive model which uses binary decisions on the
-attributes to predict a final class.  The predicted class is represented as the
-leaves, while the attribute decisions used in the prediction cause the
-different branches.
-In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
-with default settings. The decision trees were evaluated using 10-fold 
-cross-validation with the data in each data set.
+allow for more accurate predictions than only using technical data?''
+%   The predicted class is represented as the
+% leaves, while the attribute decisions used in the prediction cause the
+% different branches.
+We used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
+with default settings. We mitigate the risk of overfitting through 10-fold 
+cross-validation.
 
@@
 members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
-between a developer's followers and the build integration success.
+between a developer's followers and build integration success.
 
@@
 correctly guessed instances occurring by chance. The mean absolute error also
-decreases in both cases, which provides further evidences that social factors
-are important when predicting build success.
+decreases in both cases, providing further evidence that social factors
+importantly predict build success.
 
@@
 
-Based on the decision tree results, we noticed that core team members were
-important when classifying build success, so we decided to investigate if core
-team members have greater build success rates.
+The decision tree results suggested that core team members are
+important to classifying build success, and thus we investigated the question
+directly. 
 We classified the build success rate for
@@
 We also investigated whether developers with followers were more likely to have a
-successful build integration, since followers may be seen as vouching for
-the developer's abilities.  We specifically investigated if a developer with 
-followers was more likely to pass the build in the data set without 
-downsampling.  We first investigated whether developers with one or more followers
-were more likely to pass the build than developers without any followers, to
-verify the assumption that followers vouch for a developer's abilities. To
-investigate this question, we removed the commits without author profile
-information (20374 builds which reduced the total build count from 371208 to
-350834). We found 
-that only 0.87\% (3059/350834) of the
+successful build integration, since followers may be seen as ``vouching'' for
+the developer's abilities.  We therefore investigated the relationship between
+follower count and build success rate (on the data without 
+downsampling).  We first investigated whether developers with one or more followers
+were more likely to pass the build than those without any followers by
+removing commits without any author profile
+information (20374 builds, reducing the total build count to
+350834). Only 0.87\% (3059/350834) of the
 contributions in the data set were performed by developers with zero 
-followers. We found that 99.13\% (347775/350834) of the contributions 
-were performed by
-developers with at least one or more followers.
+followers.  %, leaving 99.13\% (347775/350834) of the contributions 
+%performed by developers with at least one follower.
 Developers with 0 followers had a successful build commit 68.49\% (2095/3059)
@@
 (260056/347775) of the time.
+%
+By contrast, developers with a large number of followers (1000 or more),
+performed 6.94\% (24347/350834) of the contributions in the 
+data set; their
+contributions had a 78.61\% (19138/24347) success rate.
 
-We also investigated developers with a large number of followers (1000 or more
-followers).  We found that 6.94\% (24347/350834) of the contributions in the 
-data set were
-performed by developers with 1000 or more followers.  We found that these
-contributions had a 78.61\% (19138/24347) success rate.  These results show 
-developers
+These results suggest that developers
 with more followers are more likely to have a successful integration build.
-These
-result may be due to the fact that developers with followers are more likely to
+This may be due to the fact that developers with followers are more likely to
 have open source development experience, and the developers' experience
-influenced the build success rate..
+influenced their build success.
 
-\subsection{Discussion}
+\subsection{Summary}
 
-Overall, we have found that social attributes which proxy experience, such as if
-the developer is a core project contributor , produce a 
-noticeable increase in predicting build success.  While the increase was noticeable 
+Social attributes proxying experience, such as whether
+the developer is a core project contributor,
+noticeably influence build success prediction.  While the increase was noticeable 
 with the full data set, there was a much greater increase in prediction
-accuracy after performing downsampling. These results show that social factors,
-such 
-as the ones studied in this paper, are significant predictors when
-evaluating the predictive power of build commit success.
-
-The build success by core team member results show that core team members are
+accuracy after downsampling. 
+%These results suggest that social factors
+%are significant predictors when
+%evaluating the predictive power of build commit success.
+%
+In particular, core team members are
 more likely to have the build integration pass than non-core team members.  This
-result provides evidence that non-core team member commits are not as
-scrutinized as core team member commits before the integration build tests, although further studied will be required to draw definite
+result provides evidence that non-core team member commits may not be as
+scrutinized as core team member commits before the integration build tests,
+although further study is required to draw definitive
 conclusions.
-
-The follower results indicate that developers with more followers are more
+%
+Likewise, developers with more followers are more
 likely to pass the build, although followers are not a perfect indicator.
-Developers with over 1000 followers had more than a 10\% increase compared to
-developers with no followers.  This shows that higher quality open source developers are more
+Developers with 1000+ followers were more than a 10\% more succesful in their
+builds as compared to
+developers with no followers.  This suggests that open source developers with
+high quality commits may be more
 likely to have a large number of followers.
 
-Overall, we have found that while experience is not a perfect indicator, 
-experienced developers are more likely to make high quality project commits.
+Overall, although experience is an imperfect indicator, but
+experienced developers appear more likely to make high quality commits.
 
@@
 
+\balance
 \bibliographystyle{plain}

### 2017-03-27 Paper/MSRChallenge2017.tex

@@
 robust measure than \textit{correctly classified} instances, since it takes into account the
-correctly guessed instances occurring by chance. The mean absolute error also
-decreases in both cases, providing further evidence that social factors
-importantly predict build success.
+correctly guessed instances occurring by chance.
+The precision, recall and F-measure are calculated over the successful and unsuccessful classes and then averaged (standard procedure in Weka).
+Precision and recall are calculated as follows:
+
+\begingroup
+    \fontsize{9pt}{12pt}\selectfont
+Precision = True Positives / (True Positives + False Positives)\
+
+Recall = True Positives / (True Positives + False Negatives)
+\endgroup
+
+F-score is a correlation\todo{this is not true; please correct} of these two values.
+We can see that all these measures increase when we add social data into the feature space, making the prediction more reliable.
+Besides this, the mean absolute error
+decreases in both cases, which provides further evidences that social factors
+are important when predicting build success.
 

### 2017-03-27 Paper/MSRChallenge2017.tex
todo

@@
 
-F-score is a correlation\todo{this is not true; please correct} of these two values.
+F-score is a correlation\todo{this is not true; please correct.  Also, we really
+don't have the space to include precision/recall formulae, given that they're
+well-known; correct your understanding, then delete this comment and the formulae} of these two values.
 We can see that all these measures increase when we add social data into the feature space, making the prediction more reliable.

### 2017-03-27 Paper/MSRChallenge2017.tex
removing formulae for P/R, condensing discussion into conclusions for space

--- 2017-03-27 Paper/MSRChallenge2017.tex
@@
 members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
-between a developer's followers and build integration success.
+between a developer's followers and build integration success. We conclude the
+section with a discussion of threats to validity (Section~\ref{sec-threats}).
 
@@
 
-It is also worth noting that the Kappa statistic increases in both cases when
-adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
-robust measure than \textit{correctly classified} instances, since it takes into account the
-correctly guessed instances occurring by chance. The mean absolute error also
-decreases in both cases, providing further evidence that social factors
-importantly predict build success.
+Note also that the Kappa statistic increases in both cases when
+adding social data (100\% and 85\% respectively). The Kappa statistic accounts
+for the accuracy of the model's predictive power. It is more
+robust than \textit{correctly classified} instances alone, since it takes into account the
+correctly guessed instances occurring by chance. The precision, recall and
+F-measure are calculated over the successful and unsuccessful classes and then
+averaged (standard procedure in Weka).  All these measures increase with social
+data in the feature space, making the prediction more reliable. The mean absolute error
+decreases in both cases, further subtantiating the importance of social factors
+in predicting build success.
 
@@
 
-\subsection{Summary}
-
-Social attributes proxying experience, such as whether
-the developer is a core project contributor,
-noticeably influence build success prediction.  While the increase was noticeable 
-with the full data set, there was a much greater increase in prediction
-accuracy after downsampling. 
-%These results suggest that social factors
-%are significant predictors when
-%evaluating the predictive power of build commit success.
-%
-In particular, core team members are
-more likely to have the build integration pass than non-core team members.  This
-result provides evidence that non-core team member commits may not be as
-scrutinized as core team member commits before the integration build tests,
-although further study is required to draw definitive
-conclusions.
-%
-Likewise, developers with more followers are more
-likely to pass the build, although followers are not a perfect indicator.
-Developers with 1000+ followers were more than a 10\% more succesful in their
-builds as compared to
-developers with no followers.  This suggests that open source developers with
-high quality commits may be more
-likely to have a large number of followers.
-
-Overall, although experience is an imperfect indicator, but
-experienced developers appear more likely to make high quality commits.
-
-\section{Threats to validity}
+\subsection{Threats to validity}
+\label{sec-threats}
 
@@
 
-We have also found that being a core contributor and having a large follower
-base can be an indicator of build integration success.
-These results provide evidence that more experienced
-developers are more likely to generate a high quality contribution.
+Overall, we conclude that social attributes proxying experience, such as whether
+the developer is a core project contributor,
+noticeably influence build success prediction.  While the increase was noticeable 
+with the full data set, there was a much greater increase in prediction
+accuracy after downsampling. 
+%These results suggest that social factors
+%are significant predictors when
+%evaluating the predictive power of build commit success.
+%
+In particular, core team members are
+more likely to have the build integration pass than non-core team members.  This
+result provides evidence that non-core team member commits may not be as
+scrutinized as core team member commits before the integration build tests,
+although further study is required to draw definitive
+conclusions.
+%
+Likewise, developers with more followers are more
+likely to pass the build, although followers are not a perfect indicator.
+Developers with 1000+ followers were more than a 10\% more succesful in their
+builds as compared to
+developers with no followers.  This suggests that open source developers with
+high quality commits may be more
+likely to have a large number of followers.
+
+Although experience is an imperfect indicator, 
+experienced developers appear more likely to make high quality commits.
 

### 2017-03-27 Paper/MSRChallenge2017.tex
condensing threats

@@
 %\paragraph{Internal validity}
-We use Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, a well known machine-learning tool,
+We use Weka, a well known machine-learning toolkit,
 to analyze our data.
-Like all tools, Weka is prone to contain errors and/or bugs. 
-Nonetheless, Weka is a well-known used, open source tool, and as such is likely
+Like all tools, Weka may contain errors and/or bugs. 
+Nonetheless, it is a well-known used, open source tool, and as such is likely
 to be of relatively high quality, mitigating threats to internal validity. 
-
- The scripts we have created to create the datasets and the 
- scripts to obtain the developer social data are publicly available 
- \footnote{https://goo.gl/CqTX44}.
-
+We have made our scripts, which analyzed the datasets and
+obtained social data publicly available\footnote{https://goo.gl/CqTX44}, for
+extension and reproducibility.
+We mitigate the risk that our results fail to 
 %\paragraph{External validity} 
-Our results might not generalize to 
- other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
- dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
-
- Other concerns of the study include the possibility that the social factors
- have changed significantly in the past three years, the collapsing of a
- commit's build success to a single successful build and unsuccessful build
- distorted the results, and the possibility that unsuccessful builds were due to
- incorrect test cases and not low quality contributions. Also, the social factors used
- in this study may not apply to closed source applications, and the factors may
- only capture a developer's experience with open source projects. Future work 
- will be required to investigate the influence of these threats.
+generalize externally by studying a broad and rich 
+ dataset~\cite{msr17challenge} comprising 1,359 popular projects.
+Similarly, the social factors we study may not apply to closed-source
+applications; however, open-source ecosystems are intellectually
+valuable sources of study on their own. 
+%
+ Other concerns include the possibility that social factors
+ have changed significantly in the past three years, that unsuccessful
+ builds are due to
+ incorrect test cases (rather than low quality contributions), and that
+ information is lost in collapsing commits' multiple builds. We believe these
+ are similarly mitigated by a large and varied dataset, but leave investigation
+ of the effects of these decisions to future work.
 

### 2017-03-27 Paper/MSRChallenge2017.tex
acks
shorter roadmap

@@
 
-We created decision tree classifiers~\cite{Quinlan86} to address our main research question: ``Do social attributes, gathered 
-from the GitHub profiles of developers,
-allow for more accurate predictions than only using technical data?''
+We assess our main research question using decision tree
+classifiers~\cite{Quinlan86}, using
+%
+% to address our main research question: ``Do social attributes, gathered 
+%from the GitHub profiles of developers,
+%allow for more accurate predictions than only using technical data?''
 %   The predicted class is represented as the
@@
 % different branches.
-We used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
-with default settings. We mitigate the risk of overfitting through 10-fold 
+the Weka J48 decision tree~\cite{Weka,Quinlan1993}
+with default settings and 10-fold 
 cross-validation.
-
-In Section~\ref{sec:successClassification} we discuss the build classification
-success rate for the technical and social factors.  In Section~\ref{sec:core},
-we compare the build success rate of core project members to non-core project
-members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
-between a developer's followers and build integration success. We conclude the
-section with a discussion of threats to validity (Section~\ref{sec-threats}).
+We present classification
+success rate for technical versus social factors
+(Section~\ref{sec:successClassification}); 
+build success rate of core project members versus non-core 
+members (Section~\ref{sec:core}); and the relationship 
+between follower count and build success (Section~\ref{sec:followerSuccess}).
 
@@
 
-\subsection{Threats to validity}
+\section{Threats to validity}
 \label{sec-threats}
@@
 % use section* for acknowledgement
-\section*{Acknowledgment}
+\section*{Acknowledgments}
 
-The acknowledgments will be added for the camera ready version.
+The authors gratefully acknowledge the partial support
+of the AFRL under AFRL Contract No. FA8750-15-2-0075. Any views, opinions,
+findings or recommendations are those of the author(s) and do not
+necessarily reflect the views of the sponsoring agencies.
 

### 2017-03-27 Paper/MSRChallenge2017.tex
a bit of tightening; will wait on bibtex and stats changes to find the last few lines

@@
 \section{Related work}
+
 The most similar related work to this paper is a case study investigating how
@@
 focused on one project and measured experience as the number of contributions to
-the project while our study focuses on a wide range of open source projects and
-measures experience through developers' profile information.
-Another study investigated the relationship between authors, files in project,
-and team organization when predicting build
-success on an IBM project with 151 developers.  The study found that as the
+the project. We focus on a wide range of open source projects and
+measure experience through developer profile information.
+Another study of the relationship between authors, files in project,
+and team organization and build
+success on an IBM project with 151 developers found that as the
 number of authors or files in a build increases, the probability of build
-success decreases~\cite{Kwan11}. A separate investigation used a dataset from the
-same project and
-found that team structures affected the teams' build success rate~\cite{Wolf09}.
-Similar studies have shown the relationship between both social and technical attributes attributes and 
-different measures of success: pull request acceptance~\cite{gousios14, 
-gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
+success decreases~\cite{Kwan11}. A separate investigation of the
+same project 
+found that team structure affected the teams' build success rate~\cite{Wolf09}.
+Others have established relationships between both social and technical attributes and 
+different measures of success, such as pull request acceptance~\cite{gousios14, 
+gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
 Tsay et al.~\cite{tsay14icse} 
@@
 acceptance of a pull 
-request. Unlike this previous study, in our study, we look at a broader aspect of 
-social aspects, and focus on predicting the success in Travis
-CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
-an important indicator in the acceptance rate of those commits by the project.
-Also, the inclusion of test cases with a commit has been shown to increase the
+request. Unlike this previous study, we look at a broader aspect of 
+social factors, and focus on predicting the Travis CI build success.
+Gousios et al.~\cite{gousios14} found that the commit change location is
+an important indicator to commit acceptance rate, and that including
+test cases increases a
 commit's acceptance rate~\cite{gousios15}.
@@
 al.~\cite{bettenburgh10} discuss the impact of social interactions with 
-post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
+post-release defects, while Vasilescu et al.~\cite{vasilescu14} explore how different 
 project characteristics (programming language, project age, etc.) affect commit 
@@
 The authors gratefully acknowledge the partial support
-of the AFRL under AFRL Contract No. FA8750-15-2-0075. Any views, opinions,
+of the AFRL (AFRL Contract No. FA8750-15-2-0075). Any 
 findings or recommendations are those of the author(s) and do not

### 2017-03-28 Paper/MSRChallenge2017.tex
added the NSF GRFP acknowledgement text
fixed a weird comma

@@
 
-We find that social factors are an important aspect of build success ,
+We find that social factors are an important aspect of build success,
 do not fully predict whether a contribution will 
@@
 \section*{Acknowledgments}
-
+This material is based upon work supported by the National Science Foundation
+Graduate Research Fellowship under Grant No. DGE-1252522.
 The authors gratefully acknowledge the partial support

### 2017-03-28 Paper/MSRChallenge2017.tex
added statistical significance to the percentages

@@
 in the data set
-and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
+and 64.70\% (25479/39381) of the builds passed.  The p-value from a Fisherexact
+test 0.0000, which means that this difference is extremely unlikely to occur by
+chance. These results show core team 
 members are more
@@
 of the time.  Developers with one or more followers were successful 74.78\%
-(260056/347775) of the time.
+(260056/347775) of the time.  The p-value of this difference, calculated with a
+Fisher exact test, is 0.000.  This shows commit success difference between
+developers with no followers and developers with at least one follower is
+very unlikely to occur by chance.
 %
@@
 data set; their
-contributions had a 78.61\% (19138/24347) success rate.
+contributions had a 78.61\% (19138/24347) success rate. The p-value calculated
+by comparing this success rate to the success rate of developers with no
+followers is 0.0000.  The p-value means that that the difference between
+developers with 1000 followers and developers with no followers is very unlikely
+to occur by chance.
 

### 2017-03-28 Paper/MSRChallenge2017.tex
part of proof reading pass

@@
 \begin{abstract}
-As the software development community makes it easier for everyone
+As the software development community makes it easier 
 to contribute to open source projects, the number of commits and pull requests 	
@@
 more users and projects become more popular, they receive ever more
-community contributions.  As the number of contributions to a project increase,
+community contributions.  As the number of project contributions increase,
 the project must dedicate more time to vetting these contributions. 
@@
 community has developed various techniques to vet project contributions, such as pull
-requests which must be approved by a core team member~\cite{gousios14}. 
+requests that must be approved by a core team member~\cite{gousios14}. 
 This can become a bottleneck, and thus it is beneficial to prioritize certain
@@
 studies have shown that the developer making the commit is also an important
-indicator when investigating contribution quality~\cite{tsay14icse, tsay14fse}.
-Thus, both technical factors, which describe the complexity of the commit, and
+indicator for contribution quality~\cite{tsay14icse, tsay14fse}.
+Thus, both technical factors, which describe the commit's complexity, and
 social factors, which describe the developer's experience, are important when
@@
 
-This previous work has focused on the predicted acceptance of \emph{pull requests}. 
-By contrast,  we are interested in analyzing the quality 
-of a contribution in the context of \emph{continuous integration}.  While pull request
+Previous work has focused on the predicted acceptance of open source \emph{pull
+requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
+in a single project.
+By contrast,  we are interested in analyzing contribution quality 
+in \emph{continuous integration} across multiple open source projects.  While 
+pull request
 quality is determined through manual inspection, continuous integration quality
-is automatically determined through test cases, and thus approach the problem of
-quality determination differently.
-We investigate the factors related to continuous integration build success.
+is automatically determined through test cases, and thus may lead to different
+quality predictors. 
+We investigate the factors related to continuous integration build success
+across open source projects.
 In this study, we analyze a large set of technical and social attributes 
@@
 
-We find that social factors are an important aspect of build success,
-do not fully predict whether a contribution will 
+We find that social factors are an important predictor of build success,
+but do not fully predict whether a contribution will 
 pass all build tests;
 that core team members are more likely to achieve build success than non-core
-members; and that developers with more followers are more likely to submit commits that pass the
+members; and that developers with more followers are more likely to submit 
+commits that pass the
 continuous integration build.
@@
 \noindent\textbf{Goal.}
-The \emph{goal} of this study is to identify and understand the relationship 
-between the social factors that describe the
+The \emph{goal} of this study is to understand the relationship 
+between social factors that describe 
 developer's experience (stars, followers, etc.) and technical properties that
@@
 (files added, files modified, etc.)
-when predicting the likelihood that a developer's commit
+when predicting whether a developer's commit
 will pass the continuous integration build tests for the project.
@@
 \vspace{1ex}
-\noindent \emph{Do social attributes, gathered from developers' GitHub profiles, allow for
-  more accurate predictions of the developer's build success than only technical
-  attributes?}
+\noindent \emph{Do social attributes
+improve the predictions of a contribution's build success when compared to
+predictions from only technical attributes?}
 
@@
 commit. We used a decision tree classifier~\cite{Quinlan86} to identify
-important factors in predicting build success. Decision trees are a predictive model which uses binary decisions on the
+important factors in predicting build success. Decision trees are a predictive 
+model which uses binary decisions on the
 attributes to predict a final class. They are well
@@
 averaged (standard procedure in Weka).  All these measures increase with social
-data in the feature space, making the prediction more reliable. The mean absolute error
-decreases in both cases, further subtantiating the importance of social factors
+data in the feature space, making the prediction more reliable. The mean 
+absolute error decreases in both cases, further substantiating the importance 
+of social factors
 in predicting build success.

### 2017-03-28 Paper/MSRChallenge2017.tex
made the term data set consistent

@@
 \vspace{1ex}
-\noindent\textbf{Metric.} We measure software contribution quality by the
+\noindent\textbf{Metric.} We measured software contribution quality by the
 build status of the
-commit. We used a decision tree classifier~\cite{Quinlan86} to identify
-important factors in predicting build success. Decision trees are a predictive 
-model which uses binary decisions on the
+commit. We used a decision tree classifier~\cite{Quinlan86} to predict build 
+success. Decision trees 
+use binary decisions on the
 attributes to predict a final class. They are well
-established and interpretable. We use a J48 decision tree, which
-has the ability to identify which attributes 
-discriminate the various instances most clearly.
-We first build a
+established and interpretable. We used a WEKA J48 decision tree for readability.
+We first built a
 decision tree classifier using only technical factors to 
 predict build integration
-success.  We then include the social factors, to 
-identify the degree to which the social factors improve the model's predictive
+success.  We then included the social factors, to 
+identify the degree to which social factors improve the model's predictive
 power.
-We evaluate the models with 10-fold cross-validation.
+We evaluated the models with 10-fold cross-validation.
 
@@
 
-We built a data set of
-attributes consisting of both technical and social factors:
+We built a data set consisting of both technical and social factors:
 
@@
 Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
-We extracted the following techical attributes as proxy to a commit's
+We extracted the following technical attributes to proxy a commit's
 complexity: 
@@
 The first five factors represent the changes caused by the commit.  The next two
-factors cover the size of the project.  These factors represent the complexity
-of the change, and the complexity of the project incorporating the change.
+factors cover the size of the project.  These factors represent the commit's complexity
+, and the complexity of the project incorporating the commit.
 
 \vspace{1ex}
-\noindent\textbf{Social Factors.} We created a web scraper to extract the social data
+\noindent\textbf{Social Factors.} We created a web scraper to extract social data
 from developer's profiles.
 We used the commit hash and the project name in the 
-MSR Challenge~\cite{msr17challenge} dataset to locate the
+MSR Challenge~\cite{msr17challenge} data set to locate the
 commit web page, leveraging \textit{github.com}'s URL standard for projects and
@@
 These social factors are all tied to a GitHub user's profile,
-and are generally correlated with user time and engagement with the site.
+and are generally correlated with users' open source engagement.
 Thus, we use them as a proxy for
@@
 factors and the build status, and another with both technical and social
-factors and the build status. We performed this split to analyze how well technical factors alone,
+factors and the build status. We performed this split to analyze how well 
+technical factors alone,
 and then both technical and social
@@
 
-The challenge dataset~\cite{msr17challenge} consists
+The challenge data set~\cite{msr17challenge} consists
 of commits that date as far back as 2011. The social data we 
@@
 We converted all Travis build statuses to two possible values:
-\emph{successful} (passed in the challenge dataset) and \emph{unsuccessful}
+\emph{successful} (passed in the challenge data set) and \emph{unsuccessful}
 (errored, failed, canceled
@@
 
-74.43\% of the builds in the reduced dataset were successful, and thus a naive
+74.43\% of the builds in the reduced data set were successful, and thus a naive
 classifier that always guesses ``successful'' would succeed 74.43\% of the time.
 To penalize misclassification for
-both classes equally, we created a second \emph{balanced} dataset by randomly 
+both classes equally, we created a second \emph{balanced} data set by randomly 
 sub-sampling the successful builds until the two build status were
 equal, through a process known as downsampling. We downsampled the entire
-dataset and then trained decision tree classifiers on both.  We validated the
+data set and then trained decision tree classifiers on both.  We validated the
 classifiers with cross-validation. Since the cross-validation is stratified, the
@@
 downsampled data. We present results for both
-datasets in Section~\ref{sec:successClassification},  and only the full dataset for Sections~\ref{sec:core} and \ref{sec:followerSuccess}.
+data sets in Section~\ref{sec:successClassification},  and only the full data 
+set in Sections~\ref{sec:core} and \ref{sec:followerSuccess}.
 
@@
 	\caption{\label{resultsTable} Predictive power 
-      decision trees with a non-downsampled dataset
+      decision trees with a non-downsampled data set
 	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled
@@
 default Weka J48 decision tree algorithm.  Without downsampling, the 
-decision tree shows an increase of 4.09\% \textit{correctly classified} instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
+decision tree\footnote{decisions trees and datasets: } shows an increase of 4.09\% \textit{correctly classified} instances when adding social data.
+On the downsampled data, the decision tree created from the technical attributes
 had a classification accuracy of 64.10\%, which outperformed the baseline of
@@
 After including the social data
-in the dataset, the classifier correctly predicted 76.09\% of the data set,
+in the data set, the classifier correctly predicted 76.09\% of the data set,
 about a 12\% improvement from only the technical data.  These results show that
@@
 
-Note also that the Kappa statistic increases in both cases when
-adding social data (100\% and 85\% respectively). The Kappa statistic accounts
-for the accuracy of the model's predictive power. It is more
-robust than \textit{correctly classified} instances alone, since it takes into account the
-correctly guessed instances occurring by chance. The precision, recall and
+The precision, recall and
 F-measure are calculated over the successful and unsuccessful classes and then
-averaged (standard procedure in Weka).  All these measures increase with social
-data in the feature space, making the prediction more reliable. The mean 
+averaged (standard procedure in Weka).  All these measures, along with the Kappa
+statistic, increase with social features, which provide evidence that social 
+factors improve build success predictions. The mean 
 absolute error decreases in both cases, further substantiating the importance 
@@
 in the data set
-and 64.70\% (25479/39381) of the builds passed.  The p-value from a Fisherexact
+and 64.70\% (25479/39381) of the builds passed.  The p-value from a Fisher exact
 test 0.0000, which means that this difference is extremely unlikely to occur by
@@
 members are more
-likely to have a successful build integration than non-core team members.
-We hypothesize the reason for this to be that core team members are more familiar with the code, therefore are more likely to have their builds pass.
+likely to have a successful build integration than non-core team members. We
+hypothesize this occurs because core team members are more familiar with the 
+code, and therefore more likely to have their builds pass.
 
@@
 to analyze our data.
-Like all tools, Weka may contain errors and/or bugs. 
-Nonetheless, it is a well-known used, open source tool, and as such is likely
-to be of relatively high quality, mitigating threats to internal validity. 
-We have made our scripts, which analyzed the datasets and
+Like all tools, Weka may contain bugs. 
+Nonetheless, it is a community tested open source tool, which mitigates threats to 
+internal validity. 
+We have made our scripts, which analyzed the data sets and
 obtained social data publicly available\footnote{https://goo.gl/CqTX44}, for
@@
 generalize externally by studying a broad and rich 
- dataset~\cite{msr17challenge} comprising 1,359 popular projects.
+ data set~\cite{msr17challenge} comprising 1,359 popular projects.
 Similarly, the social factors we study may not apply to closed-source
@@
  information is lost in collapsing commits' multiple builds. We believe these
- are similarly mitigated by a large and varied dataset, but leave investigation
+ are similarly mitigated by a large and varied data set, but leave investigation
  of the effects of these decisions to future work.
@@
 The most similar related work to this paper is a case study investigating how
-social, technical, coordination, and prior-certification factors affect build
-success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
-focused on one project and measured experience as the number of contributions to
-the project. We focus on a wide range of open source projects and
+social and technical factors affect build
+success on a project with 40 developers~\cite{Hassan06}.
+In contrast to this work, we focus on a wide range of open source projects and
 measure experience through developer profile information.
-Another study of the relationship between authors, files in project,
-and team organization and build
-success on an IBM project with 151 developers found that as the
-number of authors or files in a build increases, the probability of build
-success decreases~\cite{Kwan11}. A separate investigation of the
-same project 
-found that team structure affected the teams' build success rate~\cite{Wolf09}.
-Others have established relationships between both social and technical attributes and 
+Other work has investigated the effects of various factors, such as team
+organization, on predicting build success in a single
+project~\cite{Kwan11,Wolf09}.
+Previous investigations have established relationships between both social and 
+technical 
+attributes and 
 different measures of success, such as pull request acceptance~\cite{gousios14, 
 gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
-Tsay et al.~\cite{tsay14icse} 
-show that the social connection between the developer initiating a
-pull request and the project integrators is a key factor in predicting 
-acceptance of a pull 
-request. Unlike this previous study, we look at a broader aspect of 
-social factors, and focus on predicting the Travis CI build success.
 Gousios et al.~\cite{gousios14} found that the commit change location is
@@
 analyze the impact of CI usage in GitHub and its correlation with software 
-quality. By contrast with their work, we focus on the relationship between independent social 
+quality. By contrast with their work, we focus on the relationship between social 
 attributes and continuous integration success.
@@
 predict high quality open source contributions, as measured by continuous
-integration build success.  We have found that these factors provide
-insight when predicting the success of a build with a technical factors leading
-to a 14\% increase in predictive power, and another 12\% increase when
-incorporating social factors into the prediction.
+integration build success.  We have found that these factors can
+insight when predicting the success of a build; technical factors led
+to a 14\% increase in predictive power, and adding social factors led to another
+12\% increase.
 
@@
 the developer is a core project contributor,
-noticeably influence build success prediction.  While the increase was noticeable 
-with the full data set, there was a much greater increase in prediction
-accuracy after downsampling. 
+noticeably influence build success prediction, especially on the downsampled
+data. 
 %These results suggest that social factors
@@
 more likely to have the build integration pass than non-core team members.  This
-result provides evidence that non-core team member commits may not be as
-scrutinized as core team member commits before the integration build tests,
+result provides evidence that non-core team member commits may not be
+scrutinized as closely as core team member commits before the integration build 
+tests,
 although further study is required to draw definitive
@@
 Likewise, developers with more followers are more
-likely to pass the build, although followers are not a perfect indicator.
-Developers with 1000+ followers were more than a 10\% more succesful in their
-builds as compared to
+likely to pass the build.
+Developers with 1000+ followers were more than 10\% more succesful in their
+builds compared to
 developers with no followers.  This suggests that open source developers with

### 2017-03-28 Paper/MSRChallenge2017.tex
Adding back Tsay and pages of TravisTorrent
changes to the threats to validity

@@
 attributes to predict a final class. They are well
-established and interpretable. We used a WEKA J48 decision tree for readability.
+established and interpretable. We used a Weka J48 decision tree for readability.
 We first built a
@@
 default Weka J48 decision tree algorithm.  Without downsampling, the 
-decision tree\footnote{decisions trees and datasets: } shows an increase of 4.09\% \textit{correctly classified} instances when adding social data.
-On the downsampled data, the decision tree created from the technical attributes
+decision tree shows an increase of 4.09\% \textit{correctly classified} instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
 had a classification accuracy of 64.10\%, which outperformed the baseline of
@@
 
-\section{Threats to validity}
+\section{Threats to Validity}
 \label{sec-threats}
@@
 %\paragraph{Internal validity}
-We use Weka, a well known machine-learning toolkit,
+We have made our scripts, data, and decision tree results publicly 
+available\footnote{https://goo.gl/CqTX44}. 
+We released these files for
+extension, reproducibility, and further investigation of results.
+In the study, we use Weka, a well known machine-learning toolkit,
 to analyze our data.
@@
 internal validity. 
-We have made our scripts, which analyzed the data sets and
-obtained social data publicly available\footnote{https://goo.gl/CqTX44}, for
-extension and reproducibility.
 We mitigate the risk that our results fail to 
@@
 likely to have a large number of followers.
-
-Although experience is an imperfect indicator, 
+Although we find experience is an imperfect indicator, 
 experienced developers appear more likely to make high quality commits.

### 2017-03-28 Paper/MSRChallenge2017.tex
revisions to the threats to validity and other minor updates

@@
 
-The precision, recall and
+The precision, recall, and
 F-measure are calculated over the successful and unsuccessful classes and then
-averaged (standard procedure in Weka).  All these measures, along with the Kappa
+averaged (standard in Weka).  All these measures, along with the Kappa
 statistic, increase with social features, which provide evidence that social 
 factors improve build success predictions. The mean 
-absolute error decreases in both cases, further substantiating the importance 
+absolute error also decreases, further substantiating the importance 
 of social factors
@@
 %\paragraph{Internal validity}
-We have made our scripts, data, and decision tree results publicly 
-available\footnote{https://goo.gl/CqTX44}. 
-We released these files for
-extension, reproducibility, and further investigation of results.
 In the study, we use Weka, a well known machine-learning toolkit,
@@
 Nonetheless, it is a community tested open source tool, which mitigates threats to 
-internal validity. 
+internal validity. We also release our scripts, data, and decision tree 
+results in the study\footnote{https://goo.gl/CqTX44}.
+
 We mitigate the risk that our results fail to 
@@
 gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
+Tsay et al.~\cite{tsay14icse} 
+show the importance of the social connection between the developer initiating a
+pull request and the project integrators. We look at a broader aspect of 
+social factors, and focus on predicting the Travis CI build success.
 Gousios et al.~\cite{gousios14} found that the commit change location is
@@
 We have analyzed how technical and social factors can be used to
-predict high quality open source contributions, as measured by continuous
-integration build success.  We have found that these factors can
-insight when predicting the success of a build; technical factors led
-to a 14\% increase in predictive power, and adding social factors led to another
-12\% increase.
+predict high quality open source contributions, measured by continuous
+integration build success.  We found social factors improve predictions of build 
+success; technical factors led to a 14\% increase in predictive power, and 
+adding social factors led to another 12\% increase.
 
@@
 likely to have a large number of followers.
+
 Although we find experience is an imperfect indicator, 

### 2017-03-29 Paper/MSRChallenge2017.tex
moved the balance call after a complaint in the build process
changed a link and full name of avg
CLG edits, looking nice

@@
 more users and projects become more popular, they receive ever more
-community contributions.  As the number of project contributions increase,
+community contributions.  As the number of project contributions increases,
 the project must dedicate more time to vetting these contributions. 
 %
-Over the years, the open source
-community has developed various techniques to vet project contributions, such as pull
-requests that must be approved by a core team member~\cite{gousios14}. 
+The open source
+community has developed various techniques to vet project contributions, such as
+requiring that pull requests be approved by a core team member~\cite{gousios14}. 
 This can become a bottleneck, and thus it is beneficial to prioritize certain
@@
 Ideally, the decision to include code in
-a project is meritocratic, such that only the code is a factor
+a project is meritocratic, such that only code quality is a factor
 in the decision~\cite{Scacchi07}.
-While one would think that only the complexity of the commit is important, past
-studies have shown that the developer making the commit is also an important
-indicator for contribution quality~\cite{tsay14icse, tsay14fse}.
+However, beyond commit complexity or correctness, past
+studies have shown that the social factors describing the committing developer also importantly
+predict contribution success~\cite{tsay14icse, tsay14fse}.
 Thus, both technical factors, which describe the commit's complexity, and
 social factors, which describe the developer's experience, are important when
-investigating contribution quality.
+investigating contribution success (and thus by extension predicted quality).
 
-Previous work has focused on the predicted acceptance of open source \emph{pull
+This previous work has focused on the predicted acceptance of open source \emph{pull
 requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
-in a single project.
+in a single project. %TODO: should there be a ref here?
 By contrast,  we are interested in analyzing contribution quality 
@@
 pull request
-quality is determined through manual inspection, continuous integration quality
-is automatically determined through test cases, and thus may lead to different
-quality predictors. 
+quality is ultimately determined through manual inspection, continuous
+integration uses test cases to automatically assess commit quality,
+and thus may provide different quality predictors. 
 We investigate the factors related to continuous integration build success
@@
 
-We present the approach taken to guide this study by
+We present the approach we took to design our study by
 following the Goal-Question-Metric (GQM) methodology~\cite{Basili84}:
@@
 
-\vspace{1ex}
-\noindent \emph{Do social attributes
-improve the predictions of a contribution's build success when compared to
-predictions from only technical attributes?}
+\begin{quotation}
+\noindent\emph{Do social attributes
+improve prediction of a contribution's build success when compared to
+predictions based only on technical attributes?}
+\end{quotation}
 
@@
 power.
-We evaluated the models with 10-fold cross-validation.
+%We evaluated the models with 10-fold cross-validation.
 
@@
 
-The first five factors represent the changes caused by the commit.  The next two
-factors cover the size of the project.  These factors represent the commit's complexity
-, and the complexity of the project incorporating the commit.
+The first five factors describe the changes in the commit.  The next two
+factors cover the size of the project.  These factors proxy both the commit's complexity,
+and the complexity of the project incorporating it.
 
@@
 \noindent\textbf{Social Factors.} We created a web scraper to extract social data
-from developer's profiles.
+from developers' profiles.
 We used the commit hash and the project name in the 
@@
 \vspace{1ex}
-\noindent\textbf{Comparing two data sets.} We compiled the gathered data into 
+\noindent\textbf{Compiling the data sets.} We compiled the gathered data into 
 two data sets: one with only the technical
@@
 and then both technical and social
-factors predict build integration status.
+factors together predict build integration status.
 
@@
 classifiers with cross-validation. Since the cross-validation is stratified, the
-proportion of 50-50 is maintained through the training and testing folds for the
+50-50 proportion is maintained through the training and testing folds for the
 downsampled data. We present results for both
@@
 \textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\
-\textbf{Avg Precision}& 0.75 & 0.80  & 0.65  & 0.76 \\
-\textbf{Avg Recall}& 0.77 & 0.81 & 0.64 & 0.76 \\
-\textbf{Avg F-Measure}& 0.72 & 0.79  & 0.63  & 0.76 \\
+\textbf{Average Precision}& 0.75 & 0.80  & 0.65  & 0.76 \\
+\textbf{Average Recall}& 0.77 & 0.81 & 0.64 & 0.76 \\
+\textbf{Average F-Measure}& 0.72 & 0.79  & 0.63  & 0.76 \\
 
@@
 decision tree shows an increase of 4.09\% \textit{correctly classified} instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
-had a classification accuracy of 64.10\%, which outperformed the baseline of
-guessing all builds passed (50.00\%).
+had a classification accuracy of 64.10\%, which outperformed the na\"ive
+baseline model that 
+guesses all builds passed (50.00\%).
 After including the social data
 in the data set, the classifier correctly predicted 76.09\% of the data set,
-about a 12\% improvement from only the technical data.  These results show that
-both technical and social data can be used to improve predictions of build 
-integration success.
+about a 12\% improvement over the model that uses only the technical data.  These results show that
+while technical data is helpful in predicting build integration success, social
+data can be used to measurably improve predictive accuracy.
 
@@
 factors improve build success predictions. The mean 
-absolute error also decreases, further substantiating the importance 
-of social factors
-in predicting build success.
+absolute error also decreases, further substantiating the result.
 
@@
 
-The decision tree results suggested that core team members are
-important to classifying build success, and thus we investigated the question
+The decision tree results suggested that core team membership is
+important to classifying build success (results not shown), and thus we investigated the question
 directly. 
@@
 downsampling.  We found that core team members
-triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
+triggered 89.39\% (331827/371208) of the builds in the data set; 75.58\%
 (250808/331827) of those builds
 passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
-in the data set
-and 64.70\% (25479/39381) of the builds passed.  The p-value from a Fisher exact
-test 0.0000, which means that this difference is extremely unlikely to occur by
-chance. These results show core team 
+in the data set,
+and 64.70\% (25479/39381) of the builds passed.  The difference in success rate
+is statistically significant (the p-value from a Fisher exact
+test is 0.0000), suggesting that it is extremely unlikely to have occurred by
+chance. Thus, in our dataset, core team 
 members are more
-likely to have a successful build integration than non-core team members. We
-hypothesize this occurs because core team members are more familiar with the 
-code, and therefore more likely to have their builds pass.
+likely to have a successful build integration than non-core team developers, likely
+because core team members are naturally more familiar with the 
+codebase.
 
@@
 We also investigated whether developers with followers were more likely to have a
-successful build integration, since followers may be seen as ``vouching'' for
-the developer's abilities.  We therefore investigated the relationship between
+successful build integration, since followers could be seen as ``vouching'' for
+a developer's abilities.  We therefore investigated the relationship between
 follower count and build success rate (on the data without 
 downsampling).  We first investigated whether developers with one or more followers
-were more likely to pass the build than those without any followers by
-removing commits without any author profile
+were more likely to pass the build than those without any followers at all. We
+removed commits without any author profile
 information (20374 builds, reducing the total build count to
@@
 (260056/347775) of the time.  The p-value of this difference, calculated with a
-Fisher exact test, is 0.000.  This shows commit success difference between
-developers with no followers and developers with at least one follower is
-very unlikely to occur by chance.
+Fisher exact test, is 0.000, suggesting the difference in commit success rate between
+developers with no followers and those with at least one follower is
+very unlikely to have occurred by chance.
 %
@@
 data set; their
-contributions had a 78.61\% (19138/24347) success rate. The p-value calculated
-by comparing this success rate to the success rate of developers with no
-followers is 0.0000.  The p-value means that that the difference between
-developers with 1000 followers and developers with no followers is very unlikely
-to occur by chance.
+contributions had a 78.61\% (19138/24347) success rate. The p-value of the
+difference between this success rate and that of developers with no
+followers is again 0.0000.  % The p-value means that that the difference between
+% developers with 1000 followers and developers with no followers is very unlikely
+% to occur by chance.
 
@@
 internal validity. We also release our scripts, data, and decision tree 
-results in the study\footnote{https://goo.gl/CqTX44}.
+results in the study.\footnote{https://github.com/mausotog/MSRChallenge2017/}
 
@@
 success on a project with 40 developers~\cite{Hassan06}.
-In contrast to this work, we focus on a wide range of open source projects and
+We focus on a wide range of open source projects and
 measure experience through developer profile information.
@@
 
+\balance
 \section{Conclusion}
@@
 Graduate Research Fellowship under Grant No. DGE-1252522.
-The authors gratefully acknowledge the partial support
+The authors also gratefully acknowledge the partial support
 of the AFRL (AFRL Contract No. FA8750-15-2-0075). Any 
@@
 
-\balance
 \bibliographystyle{plain}

### 2017-03-29 Paper/MSRChallenge2017.tex
adding stuff to related work

@@
 Gousios et al.~\cite{gousios14} found that the commit change location is
-an important indicator to commit acceptance rate, and that including
+an important indicator to commit acceptance rate and that including
 test cases increases a
-commit's acceptance rate~\cite{gousios15}.
+commit's acceptance rate~\cite{gousios15}. We found that number of followers and being a core member are important indicators of built success. 
 Bettenburgh et 
@@
 project characteristics (programming language, project age, etc.) affect commit 
-success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
+success when integrated into the automatic build process. In our study we focus on the comparisson between similar technical characteristics and social attributes. Yu et al.~\cite{yu16} 
 analyze the impact of CI usage in GitHub and its correlation with software 
-quality. By contrast with their work, we focus on the relationship between social 
-attributes and continuous integration success.
+quality, while we focus on gain in predictability of software quality when using CI.
 

### 2017-03-29 Paper/MSRChallenge2017.tex
changed the not shown and added citations to introduction

@@
 requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
-in a single project. %TODO: should there be a ref here?
+in a single project~\cite{Hassan06,Kwan11,Wolf09}. 
 By contrast,  we are interested in analyzing contribution quality 
@@
 The decision tree results suggested that core team membership is
-important to classifying build success (results not shown), and thus we investigated the question
+important to classifying build success (in supplemental material), and thus 
+we investigated the question
 directly. 

### 2017-03-29 Paper/MSRChallenge2017.tex
fixed typos in related work

@@
 test cases increases a
-commit's acceptance rate~\cite{gousios15}. We found that number of followers and being a core member are important indicators of built success. 
+commit's acceptance rate~\cite{gousios15}. We found that number of followers and being a core member are important indicators of build success. 
 Bettenburgh et 
@@
 project characteristics (programming language, project age, etc.) affect commit 
-success when integrated into the automatic build process. In our study we focus on the comparisson between similar technical characteristics and social attributes. Yu et al.~\cite{yu16} 
+success when integrated into the automatic build process. In our study we focus on the comparison between similar technical characteristics and social attributes. Yu et al.~\cite{yu16} 
 analyze the impact of CI usage in GitHub and its correlation with software 

### 2017-03-29 Paper/MSRChallenge2017.tex
added a comma
Changed link

@@
 internal validity. We also release our scripts, data, and decision tree 
-results in the study.\footnote{https://github.com/mausotog/MSRChallenge2017/}
+results in the study.\footnote{https://github.com/squaresLab/MSR-challenge-2017}
 
@@
 project characteristics (programming language, project age, etc.) affect commit 
-success when integrated into the automatic build process. In our study we focus on the comparison between similar technical characteristics and social attributes. Yu et al.~\cite{yu16} 
+success when integrated into the automatic build process. In our study, we focus on the comparison between similar technical characteristics and social attributes. Yu et al.~\cite{yu16} 
 analyze the impact of CI usage in GitHub and its correlation with software 

### 2017-03-31 Paper/MSRChallenge2017.tex
fixed a typo
minor changes on last proof-read

@@
 This previous work has focused on the predicted acceptance of open source \emph{pull
-requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
+requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} (CI) builds
 in a single project~\cite{Hassan06,Kwan11,Wolf09}. 
@@
 %\item gh\_build\_started\_at 
-\item Source churn, changed lines of code.
+\item Source churn (changed lines of code).
 \item Files added by this commit.
@@
 
-74.43\% of the builds in the reduced data set were successful, and thus a naive
+74.43\% of the builds in the reduced data set were successful, and thus a na\"ive
 classifier that always guesses ``successful'' would succeed 74.43\% of the time.
@@
 chance. Thus, in our dataset, core team 
-members are more
-likely to have a successful build integration than non-core team developers, likely
+members 
+have a successful build integration more often than non-core team 
+developers, likely
 because core team members are naturally more familiar with the 
@@
 internal validity. We also release our scripts, data, and decision tree 
-results in the study.\footnote{https://github.com/squaresLab/MSR-challenge-2017}
+results.\footnote{https://github.com/squaresLab/MSR-challenge-2017}
 
@@
 integration build success.  We found social factors improve predictions of build 
-success; technical factors led to a 14\% increase in predictive power, and 
+success, technical factors led to a 14\% increase in predictive power, and 
 adding social factors led to another 12\% increase.
@@
 likely to pass the build.
-Developers with 1000+ followers were more than 10\% more succesful in their
+Developers with 1000+ followers were more than 10\% more successful in their
 builds compared to
